### 2021-09-17 paper/main.tex
started paper draft

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[sort]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{authblk}

\doublespacing
\linenumbers

\title{Fitness tracking reveals task-specific memory effects of exercise}
\author[1]{Jeremy R. Manning}
\author[1,2]{Gina M. Notaro}
\author[1]{Esme Chen}
\author[1]{Paxton C. Fitzpatrick}
\affil[1]{Dartmouth College, Hanover, NH}
\affil[2]{Lockheed Martin, Bethesda, MD}

\begin{document}
\maketitle

\begin{abstract}
Physical excercise can benefit both physical and mental well-being.  Different forms of exercise (i.e., aerobic versus anaerobic; running versus walking versus swimming versus yoga; high-intensity interval trainiing versus endurance workouts; etc.) impact physical fitness in different ways.  For example, running may substantially impact leg and heart strength but only moderately impact arm strength. We hypothesized that the mental benefits of exercise might be similarly differentiated.  We focused specifically on how different forms of exercise might affect different aspects of memory.  To test our hypothesis, we collected nearly a century's woth of fitness data (in aggregate).  We then asked participants to engage in a battery of memory tasks that tested their short and long term episodic, semantic, and spatial memory.  We found that ??.
\end{abstract}

\section*{Introduction and overview}

\section*{Acknowledgements}

\section*{Data and code availability}
All analysis code and data used in the present manuscript may be found \href{https://github.com/ContextLab/brainfit-paper}{\underline{here}}.

\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
\end{document}

### 2021-09-17 paper/main.tex
added rough outline

@@
-\documentclass{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \title{Fitness tracking reveals task-specific memory effects of exercise}
-\author[1]{Jeremy R. Manning}
+\author[1, $\star$]{Jeremy R. Manning}
 \author[1,2]{Gina M. Notaro}
@@
 \affil[2]{Lockheed Martin, Bethesda, MD}
+\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}
 
@@
 
-\section*{Introduction and overview}
+\section*{Introduction}
+
+\section*{Results}
+\begin{itemize}
+  \item exploratory analysis (correlations)
+    \begin{itemize}
+    \item Memory-memory
+    \item fitness-fitness
+    \item survey-survey
+    \item (fitness + survey)-memory
+    \end{itemize}
+  \item predictive analysis (regressions)
+    \begin{itemize}
+    \item Predict memory performance on held-out task from other tasks
+    \item Predict memory performance on each task using fitness data
+      \item Predict memory performance on each task using survey data
+      \end{itemize}
+    \item Reverse correlations
+      \begin{itemize}
+      \item Fitness profile that predicts performance on each task (barplots + timelines)
+      \item Fitness profile for each survey demographic (barplots + timelines)
+        \begin{itemize}
+          \item Select out mental health demographics (based on meds, stress levels)
+          \end{itemize}
+        \end{itemize}
+  \end{itemize}
+
+  \section*{Discussion}
+  \begin{itemize}
+  \item summarize key findings
+  \item correlation versus causation
+  \item related work (exercise/memory, exercise/mental health), what this study adds
+    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
+    \end{itemize}
+
+\section*{Methods}
+\subsection*{Experiment}
+\subsubsection*{Participants}
+\subsubsection*{Tasks}
+\paragraph*{Intake survey.}
+\paragraph*{Free recall.}
+\paragraph*{Naturalistic recall.}
+\paragraph*{Foreign language flashcards.}
+\paragraph*{Spatial learning.}
+
+\subsubsection*{Fitness tracking using Fitbit devices}
+
+\subsubsection*{Processing Fitbit data}
+\paragraph*{Raw metrics.}
+\paragraph*{Comparing recent versus baseline measurements.}
+
+\subsubsection*{Exploratory correlation analyses}
+\paragraph*{Imputation and interpolation of missing data.}
+
+\subsubsection*{Regression-based prediction analyses}
+
+\subsubsection*{Reverse correlation analyses}
 
 \section*{Acknowledgements}
+We acknowledge useful discussions with David Bucci, Emily Glasser, Andrew Heusser, Avigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten Ziman.
+Our work was supported in part by the Dartmouth Young Minds and Brains initiative.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+This paper is dedicated to the memory of David Bucci, who helped to inspire the theoretical foundations of this work.
+Dave served as a mentor and colleague on the project prior to his passing.
 
@@
 
+\section*{Author contributions}
+Concept: J.R.M.  Implementation: G.M.N.  Analyses: G.M.N., E.C., and P.C.F.  Writing: J.R.M.
+
+\section*{Competing interests}
+The authors declare no competing interests.
+
 \bibliographystyle{apa}

### 2021-09-17 paper/main.tex
finished draft of introduction

@@
 
-\title{Fitness tracking reveals task-specific memory effects of exercise}
+\title{Fitness tracking reveals task-specific associations between
+  memory, mental health, and exercise}
 \author[1, $\star$]{Jeremy R. Manning}
@@
   Physical excercise can benefit both physical and mental well-being.
-Different forms of exercise (i.e., aerobic versus anaerobic; running versus walking versus swimming versus yoga; high-intensity interval trainiing versus endurance workouts; etc.) impact physical fitness in different ways.
-For example, running may substantially impact leg and heart strength but only moderately impact arm strength.
-We hypothesized that the mental benefits of exercise might be similarly differentiated.
-We focused specifically on how different forms of exercise might affect different aspects of memory.
-To test our hypothesis, we collected nearly a century's woth of fitness data (in aggregate).
-We then asked participants to engage in a battery of memory tasks that tested their short and long term episodic, semantic, and spatial memory.
-We found that ??.
+  Different forms of exercise (i.e., aerobic versus anaerobic; running
+  versus walking versus swimming versus yoga; high-intensity interval
+  trainiing versus endurance workouts; etc.) impact physical fitness
+  in different ways.  For example, running may substantially impact
+  leg and heart strength but only moderately impact arm strength. We
+  hypothesized that the mental benefits of exercise might be similarly
+  differentiated.  We focused specifically on how different forms of
+  exercise might related to different aspects of memory and mental
+  health.  To test our hypothesis, we collected nearly a century's
+  woth of fitness data (in aggregate).  We then asked participants to
+  fill out surveys asking them to self-report on different aspects of
+  their mental health.  We also asked participants to engage in a
+  battery of memory tasks that tested their short and long term
+  episodic, semantic, and spatial memory.  We found that participants
+  with similar exercise habits and fitness profiles tended to also
+  exhibit similar mental health and task performance profiles.
 \end{abstract}
@@
 \section*{Introduction}
+Engaging in physical activity (exercise) can improve our physical
+fitness by increasing muscle strength~\citep{RogeEvan93, Lind79,
+  CranEtal13, Knut07}, increasing bone density~\citep{ChilEtal12,
+  BassRams94, LaynNels99}, increasing cardiovascular
+performance~\citep{MaioEtal00, PollEtal00}, increasing lung
+capacity~\citep{LazoEtal16}~\citep[although see][]{RomaEtal16},
+increasing endurance~\citep{WilmKnut03}, and more.  Exercise can also
+improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
+  DeslEtal09, Call04, PaluSchw00} and cognitive performance~\citep{ChanEtal12b,
+  BrisEtal02, EtniEtal06}.
+
+The physical benefits of exercise can be explained by stress-responses
+of the affected body tissues. For example, skeletal muscles that are
+taxed during exercise exhibit stress responses~\citep{MortEtal09} that
+can in turn affect their growth or atrophy~\citep{SchiEtal13}.  By
+comparison, the benefits of exercise on mental health are less direct.  For
+example, one hypothesis is that exercise leads to specific
+physiological changes, such as increased aminergic synaptic
+transmission and endorphin release, which in turn act on
+neurotransmitters in the brain~\citep{PaluSchw00}.
+
+Speculatively, if different exercise regimens lead to different
+neurophysiological responses, one might be able to map out a spectrum
+of signalling and transduction pathways that are impacted by a given
+type, duration, and intensity of exercise in each brain region.  For
+example, prior work has shown that exercise increases acetylcholine
+levels, starting in the vicinity of the exercised
+muscles~\citep{ShoeEtal97}.  Acetylcholine is thought to play an
+important role in memory formation~\citep[e.g., by modulating specific
+synaptic inputs from entorhinal cortex to the hippocampus, albeit in
+rodents;]{PalaEtal21}.  Given the central role of these medial
+temporal lobe structures play in memory, changes in acetylcholine
+might lead to specific changes in memory formation and retrieval.
+
+In the present study, we hypothesize that (a) different exercise regimens will
+have different, quantifiable impacts on cognitive performance and
+mental health, and that (b) these impacts will be consistant across
+individuals.  To this end, we collected a year of fitness tracking
+data from each of 113 participants.  We then asked each participant to
+fill out a brief survey in which they self-evaluated several aspects
+of their mental health.  Finally, we ran each participant through a
+battery of memory tasks, which we used to evaluate their memory
+performance along several dimensions.  We examined the data for
+potential associations between memory, mental health, and exercise.
 
@@
       \end{itemize}
-    \item Reverse correlations
+    \item Reverse correlations: look at recent changes versus baseline trends
       \begin{itemize}
@@
   \item correlation versus causation
+         \item what can vs.
+can't we know?
+we can identify correlations, but not causal direction-- e.g.
+we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.
+that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
   \item related work (exercise/memory, exercise/mental health), what this study adds
@@
 \bibliographystyle{apa}
-\bibliography{CDL-bibliography/cdl}
+\bibliography{/Users/jmanning/CDL-bibliography/cdl}
 \end{document}

### 2021-09-17 paper/main.tex
minor tweaks to intro

@@
 improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
-  DeslEtal09, Call04, PaluSchw00} and cognitive performance~\citep{ChanEtal12b,
-  BrisEtal02, EtniEtal06}.
+  DeslEtal09, Call04, PaluSchw00, BassSuzu17} and cognitive performance~\citep{ChanEtal12b,
+  BrisEtal02, EtniEtal06, BassSuzu17}.
 

### 2021-09-18 paper/main.tex
starting to fill in methods

@@
     \section*{Methods}
+
+    We ran an online experiment using the Amazon Mechanical Turk
+    platform.  We collected data about each participant's fitness and
+    exercise habits, a variety of self-reported measures concerning their
+    mental health, and about their performance on a battery of memory
+    tasks.  We mined the dataset for potential associations between
+    memory, mental health, and exercise.
+
 \subsection*{Experiment}
 \subsubsection*{Participants}
+\begin{itemize}
+\item 160 total (recruited ``master'' workers who reported owning and
+  using a Fitbit device)
+  \item 113 completed all experiments successfully.  We excluded the
+    remaining participants who failed to log in to their Fitbit
+    accounts, encountered technical issues that prevented them from
+    participating in the study, or ended their participation before
+    finishing the study.
+  \item compensation (check this)
+  \item M/F counts
+  \item age
+    \item demographics (race, education completed, location)
+  \end{itemize}
 \subsubsection*{Tasks}

### 2021-09-18 paper/main.tex
added participant information to methods section

--- 2021-09-17 paper/main.tex
@@
 \begin{abstract}
-  Physical excercise can benefit both physical and mental well-being.
+  Physical exercise can benefit both physical and mental well-being.
   Different forms of exercise (i.e., aerobic versus anaerobic; running
   versus walking versus swimming versus yoga; high-intensity interval
-  trainiing versus endurance workouts; etc.) impact physical fitness
+  training versus endurance workouts; etc.) impact physical fitness
   in different ways.  For example, running may substantially impact
@@
   health.  To test our hypothesis, we collected nearly a century's
-  woth of fitness data (in aggregate).  We then asked participants to
+  worth of fitness data (in aggregate).  We then asked participants to
   fill out surveys asking them to self-report on different aspects of
@@
     \section*{Methods}
+
+    We ran an online experiment using the Amazon Mechanical Turk
+    platform.  We collected data about each participant's fitness and
+    exercise habits, a variety of self-reported measures concerning their
+    mental health, and about their performance on a battery of memory
+    tasks.  We mined the dataset for potential associations between
+    memory, mental health, and exercise.
+
 \subsection*{Experiment}
 \subsubsection*{Participants}
+We recruited experimental participants by posting our experiment as a
+Human Intelligence Task (HIT) on the Amazon Mechanical Turk platform.
+We limited participation to Mechanical Turk Workers who had been
+assigned a ``Masters'' designation on the platform, given to workers
+who score highly across several metrics on a large number of HITs,
+according to a proprietary algorithm managed by Amazon.  We further
+limited our participant pool to participants who self-reported that
+they were fluent in English and regularly used a Fitbit fitness
+tracker device.  A total of 160 workers accepted our
+HIT in order to participate in our experiment.  Of these, we excluded all
+participants who failed to log into their Fitbit account (giving us
+access to their anonymized fitness tracking data), encountered
+technical issues (e.g., by accessing the HIT using an incompatible browser, device, or
+operating system), or who ended their participation prematurely,
+before completing the full study.  In all, 113 participants remained
+that contributed usable data to the study.
+
+For their participation, workers received a base payment of \$5 per hour (computed in 15
+minute increments, rounded up to the nearest 15 minutes), plus an
+additional performance-based bonus of up to \$5.  Our recruitment
+procedure and study protocol
+were approved by Dartmouth's Committee for the Protection of Human Subjects.
+
+\paragraph{Gender, age, and race.}
+Of the 113 participants who contributed usable data, 77 reported their gender as female, 35 as
+male, and 1 chose not to report their gender.  Participants ranged in
+age from 19--68 years old (25\textsuperscript{th} percentile: 28.25
+years; 50\textsuperscript{th} percentile: 32 years;
+75\textsuperscript{th} percentile: 38 years).  Participants reported
+their race as White (90 participants), Black or African American (11
+participants), Asian (7 participants), Other (4 participants), and
+American Indian or Alaska Native (3 participants).  One participant
+opted not to report their race.
+
+\paragraph{Languages.}
+All participants reported that they were fluent in either 1 and 2
+languages (25\textsuperscript{th} percentile: 1;
+50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
+percentile: 1), and that they were ``familiar'' with between 1 and 11
+languages (25\textsuperscript{th} percentile: 1;
+50\textsuperscript{th} percentile: 2; 75\textsuperscript{th}
+percentile: 3).
+
+\paragraph{Reported medical conditions and medications.}
+Participants reported having and/or taking medications pertaining to the following medical conditions: anxiety or
+depression (4 participants), recent head injury (2 participants), high
+blood pressure (1 participant), bipolar (1 participant),
+hypothyroidism (1 participant), and other unspecified medications (1
+participant).  Participants reported their current and typical stress
+levels on a Likert scale as very relaxed (-2), a little relaxed (-1),
+neutral (0), a little stressed (1), or very stressed (2).  The
+``current'' stress level reflected participants' stress at the time
+they participated in the experiment.
+Their responses
+ranged from -2 to 2 (current stress: 25\textsuperscript{th} percentile: -2;
+50\textsuperscript{th} percentile: -1; 75\textsuperscript{th}
+percentile: 1; typical stress: 25\textsuperscript{th} percentile: 0;
+50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
+percentile: 1).  Participants also reported their current level of
+alertness on a Likert scale as very sluggish (-2), a little sluggish
+(-1), neutral (0), a little alert (1), or very alert (2).  Their
+responses ranged from -2 to 2 (25\textsuperscript{th} percentile: 0;
+50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
+percentile: 2).
+
+\paragraph{Residence and level of education.}
+Participants reported their residence
+as being located in the suburbs (36 participants), a large city (30
+participants), a small city (23 participants), rural (14
+participants), or a small town (10 participants).  Participants
+reported their level of education as follows: College graduate (42
+participants), Master's degree (23 participants), Some college (21
+participants), High school graduate (9 participants), Associate's
+degree (8 participants), Other graduate or professional school (5
+participants), Some graduate training (3 participants), or Doctorate
+(2 participants).
+
+\paragraph{Reported water and coffee intake.}
+Participants reported the number of cups of water and coffee they had
+consumed prior to accepting the HIT.  Water consumption ranged from
+0--6 cups (25\textsuperscript{th} percentile: 1;
+50\textsuperscript{th} percentile: 3; 75\textsuperscript{th}
+percentile: 4).  Coffee consumption ranged from 0--4 cups (25\textsuperscript{th} percentile: 0;
+50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
+percentile: 2).
+
 \subsubsection*{Tasks}
@@
 \section*{Acknowledgements}
-We acknowledge useful discussions with David Bucci, Emily Glasser, Andrew Heusser, Avigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten Ziman.
+We acknowledge useful discussions with David Bucci, Emily Glasser, Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten Ziman.
 Our work was supported in part by the Dartmouth Young Minds and Brains initiative.
@@
 \section*{Author contributions}
-Concept: J.R.M.  Implementation: G.M.N.  Analyses: G.M.N., E.C., and P.C.F.  Writing: J.R.M.
+Concept: J.R.M.  Experiment implementation and data collection: G.M.N.
+Analyses: G.M.N., E.C., P.C.F., and J.R.M.  Writing: J.R.M.
 

### 2021-09-18 paper/main.tex
added survey info to methods

@@
 50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
-percentile: 2).
+percentile: 2).  Nearly all (111 out of 113) participants reported
+that they had normal color vision, and 15 participants reported
+uncorrected visual impairments (including dyslexia and uncorrected
+near- or far-sightedness).
 
@@
 \subsubsection*{Tasks}
-\paragraph*{Intake survey.}
+Upon accepting the HIT posted on Mechanical Turk, the worker was
+directed to read and fill out a screening and consent form, and to
+share access to their anonymized Fitbit data via their Fitbit
+account.  After consenting to participant and successfully sharing
+their Fitbit data, participants filled out a survey and then engaged
+in a series of memory tasks.
+
+\paragraph*{Survey questions.}  We collected the following demographic
+information from each participant: their birth year, gender, highest
+(academic) degree achieved, race, language fluency, and language
+familiarity.  We also collected information about participants'
+health and wellness, including about their vision, alertness, stress, sleep, coffee
+and water consumption, location of their residence, activity typically
+required for their job, and exercise habits.
+
 \paragraph*{Free recall.}
+
 \paragraph*{Naturalistic recall.}

### 2021-09-20 paper/main.tex
adding task descriptions [WIP]

@@
 directed to read and fill out a screening and consent form, and to
-share access to their anonymized Fitbit data via their Fitbit
-account.  After consenting to participant and successfully sharing
-their Fitbit data, participants filled out a survey and then engaged
-in a series of memory tasks.
+share access to their anonymized Fitbit data via their Fitbit account.
+After consenting to participant and successfully sharing their Fitbit
+data, participants filled out a survey and then engaged in a series of
+memory tasks (Fig.~\ref{fig:tasks}).  All stimuli and code for running
+the full Mechanical Turk experiment may be found
+\href{https://github.com/ContextLab/brainfit-task}{\underline{here}}.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/experiment}
+\caption{\textbf{Battery of memory tasks.}  \textbf{a.  Free recall.}
+Participants study 16 words (presented one at a time), followed by an
+immediate memory test where they type
+each word they remember from the just-studied list.  In the delayed
+memory test, participants type any words they remember studying, from
+any list.  \textbf{b. Naturalistic recall.}  Participants watch a
+brief video, followed by two immediate memory tests.  The first test
+asks participants to write out what happened in the video.  The second
+test has participants answer a series of multiple choice questions
+about the conceptual content of the video.  In the delayed memory
+test, participants (again) write out what happened in the video.
+\textbf{c. Foreign language flashcards.}  Participants study a
+sequence of 10 English-Gailic word pairs, each presented with an
+illustration of the given word.  During an immediate memory test,
+participants perform a multiple choice test where they select the
+Gaelic word that corresponds to the given photograph.  During the
+delayed memory test, participants perform a second multiple choice
+test, where they select the Gaelic word that corresponds to each of a
+new set of photographs.  \textbf{d. Spatial learning.}  In each trial,
+participants
+study a set of randomly positioned shapes.  Next, the shapes'
+positions are altered, and participants are asked to drag the shapes
+back to their previous positions.  \textbf{All panels.}  The gray
+numbers denote the order in which participants experienced each task
+or test.}
+\label{fig:tasks}
+\end{figure}
 
@@
 
-\paragraph*{Free recall.}
+\paragraph*{Free recall (Fig.~\ref{fig:tasks}a).} 
+Participants studied a sequence of four word lists, each comprising 16
+words.  After studying each list, participants received an immediate
+memory test, whereby they were asked to type (one word at a time) any
+words they remembered from the just-studied list, in any order.
 
-\paragraph*{Naturalistic recall.}
-\paragraph*{Foreign language flashcards.}
-\paragraph*{Spatial learning.}
+Words were presented for 2~s each, in black text on a white
+background, followed by a 2~s blank (white) screen.  After the final
+2~s pause, participants were given 90~s to type in as many words as
+they could remember, in any order.  The memory test was constructed
+such that the participant could only see the text of the current word
+they were typing; when they pressed any non-letter key, the current
+word was submitted and the text box they were typing in was cleared.
+This was intended to prevent participants from retroactively editing
+their previous responses.
+
+The word lists participants studied were drawn from the categorized
+lists reported in \cite{ZimaEtal18}.  Each participant was assigned
+four unique randomly chosen lists (in a randomized order), selected from a full set of 16
+lists.  Each chosen list was then randomly shuffled before presenting
+the words to the participants.
+
+Participants also performed a final delayed memory test where they
+were given 180~s to type out any words they remembered from
+\textit{any} of the 4 lists they had studied.
+
+Recalled words within an edit distance of 2 (i.e., a Levenshtein Distance less
+than or equal to 2) of any word in the wordpool were ``autocorrected''
+to their nearest match.  We also manually corrected clear typos or
+mispellings by hand (e.g., we corrected ``hippoptumas'' to
+``hippopotamus'', ``zucinni'' to ``zucchini'', and so on).  Finally,
+we lemmatized each submitted word to match the plurality of the
+matching wordpool word (e.g., ``bongo'' was corrected to ``bongos'',
+and so on).  After applying these corrections, any submitted words
+that matched words presented on the just-studied list were tagged as
+``correct'' recalls, and any non-matching words were discarded as
+``errors.''  Because participants were not allowed to edit the text
+they entered, we chose not to analyze these putative ``errors,'' since
+we could not distinguish typos from true misrememberings.
+
+\paragraph*{Naturalistic recall (Fig.~\ref{fig:tasks}b).}
+Participants watched a 2.5~minute video clip entitled ``The Temple of
+Knowledge.''  The video comprises an animated story told to StoryCorps
+by Ronald Clark, who was interviewed by his daughter, Jamilah Clark.
+The narrator (Ronald) discusses growing up living in an apartment over Washington
+Heights branch of the New York Public Library, where his father worked
+as a custodian during the 1940s.
+
+After watching the video clip, participants were asked to type out
+anything they remembered about what happened in the video.  They typed
+their responses into a text box, one sentence at a time.  When the
+participant pressed the return key or typed any final punctuation mark
+(``.'', ``!'', or ``?'') the text currently entered into the box was
+``submitted'' and added to their transcript, and the text box was
+cleared to prevent further editing of any already-submitted text.
+This was intended to prevent participants from retroactively editing
+their previous responses.  Participants were given up to 10~minutes to
+enter their responses.  After 4~minutes participants were given the
+option of ending the response period early, e.g., if they felt they had finished
+entering all of the information they remembered.  Each participant's
+transcript was constructed from their submitted responses by combining
+the sentences into a single document and removing extraneous
+whitespace characters.
+
+Following this 4--10 minute free response period, participants were
+given a series of 10 multiple choice questions about the conceptual
+content of the story.  All participants received the same questions,
+in the same order.
+
+Participants also performed a final delayed memory test, where they
+carried out the free response recall task a second time, near the end
+of the testing session.  This resulted in a second transcript, for
+each participant.
+
+\paragraph*{Foreign language flashcards (Fig.~\ref{fig:tasks}c).}
+Participants studied a series of 10 English-Gaelic word pairs in a
+randomized order.  We selected the Gaelic language both for its
+relatively small number of native speakers and for its dissimilarity
+to other commonly spoken languages amongst Mechanical Turk Workers.
+We verified (via self report) that all of our participants were fluent in English and
+that they were neither fluent nor familiar with Gaelic.
+
+Each word's ``flashcard'' comprised a cartoon
+depicting the given word, the English word or phrase in lowercase text (e.g., ``the
+boy''), and the Gaelic word or phrase in uppercase text (e.g.,
+``BUACHAILL'').   Each
+flashcard was displayed for 4~s, followed by a 3~s interval (during
+which the screen was cleared) prior to the next flashcard
+presentation.
+
+After studying all 10 flashcards, participants were given a multiple
+choice memory test where they were shown a series of novel
+photographs, each depicting one of the 10 words they had learned.
+They were asked to select which (of 4 unique options) Gaelic word went with
+the given picture.  The 3 incorrect options were selected at random
+(with replacement across trials), and the order in which the choices
+appeared to the participant were also randomized.  Each of the 10
+words they had learned were tested exactly once.
+
+Participants also performed a final delayed memory test, where they
+were given a second set of 10 questions (again, one per word they had
+studied).  For this second set of questions participants were prompted
+with a new set of novel photographs, and new randomly chosen incorrect
+choices for each question.  Each of the 10 original words they had
+learned were (again) tested exactly once during this final memory test.
+
+\paragraph*{Spatial learning (Fig.~\ref{fig:tasks}d).}
 

### 2021-09-20 paper/main.tex
finished adding (draft) descriptions of all tasks

@@
 \paragraph*{Spatial learning (Fig.~\ref{fig:tasks}d).}
+Participants performed a series of study-test trials where they
+memorized the onscreen spatial locations of two or more shapes.
+During the study phrase of each trial, a set of shapes appeared on the screen for
+10~s, followed by 2~s of blank (white) screen.  During the test phase
+of each trial, the same shapes appeared onscreen again, but this time
+they were vertically aligned and sorted horizontally in a random
+order.  Participants were instructed to drag (using the mouse) each
+shape to its studied position, and then to click a button to indicate
+that the placements were complete.
+
+In different study-test trials, participants learned the locations of
+different numbers of shapes (always drawn from the same pool of 7
+unique shapes, where each shape appeared at most one time per trial).
+They first performed three trials where they learned the locations of
+2 shapes; next three trials where they learned the locations of 3
+shapes; and so on until their last three trials, where (during each trial) they learned
+the locations of 7 shapes.  All told, each participant performed 18
+study-test trials of this spatial learning task (3 trials for each of 2, 3,
+4, 5, 6, and 7 shapes).
 

### 2021-09-21 paper/main.tex
added some notes to the results section

@@
 \begin{itemize}
+\item characterizing behaviors (potentially broken down by 3--4
+  fitness-defined categories, like activity level quartile; may also
+  want to have separate figures: one for characterizing behaviors on
+  average, and a second breaking down by fitness variable, e.g. after
+  the correlation analyses are presented)
+  \begin{itemize}
+  \item Free recall: pfr, lag-CRP, spc
+    \item Naturalistic recall: reproduce a version of the sherlock
+      movie/recall trajectories
+    \item Foreign language flashcards: p(correct) by activity level
+      \item Spatial learning: mean error by number of shapes
+      \end{itemize}
+    \item Fitness info (break down by task performance, potentiall
+      separately for each task); also separate out recent (raw) and recent versus baseline
+      \begin{itemize}
+      \item activity (steps, zone minutes, floors/elevation)
+      \item resting heart rate
+        \item sleep
+        \end{itemize}
   \item exploratory analysis (correlations)

### 2021-09-21 paper/main.tex
added figure reporting which devices participants used

@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/devices}
+\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
+  participants whose fitness tracking data came from each model of
+  Fitbit device.  ``MobileTrack'' refers to participants who used
+  smartphone accelerometer information to track their activity via the
+  Fitbit smartphone app.
+  ``Unknown''  denotes participants whose device information was not
+  available from their available Fitbit data.}
+\label{fig:devices}
+\end{figure}
+
 \subsubsection*{Processing Fitbit data}

### 2021-09-21 paper/main.tex
backing up progress

@@
 \subsubsection*{Fitness tracking using Fitbit devices}
+To gain access to our study, participants provided us with access to
+all data associated with their Fitbit account from the
+year (365 calendar days) up to and including the day they accepted the
+HIT.  We filtered out all identifiable information (e.g., participant names, GPS
+coordinates, etc.) prior to importing their data.
+
+\subsubsection*{Collecting and processing Fitbit data}
+
+The fitness
+tracking data associated with participants' Fitbit accounts varied in
+scope and duration
+according to which device the participant owned (Fig.~\ref{fig:devices}), how often the
+participant wore (and/or synced) their tracking device, and how long they had owned their
+device.  For example, while all participants' devices supported basic
+activity metrics such as daily step counts, only a subset of the
+devices with heart rate monitoring capabilities provided information
+about workout intensity, resting heart rate, and other related
+measures.
 
@@
 
-\subsubsection*{Processing Fitbit data}
-\paragraph*{Raw metrics.}
-\paragraph*{Comparing recent versus baseline measurements.}
+Across all devices, we collected the following information: heart
+rate data, sleep tracking data, logged bodyweight measurements, logged
+nutrition measurements, Fitbit account and device settings, and
+activity metrics.
+
+\paragraph{Heart rate.}  If available, we extracted all
+heart rate data collected by participants' Fitbit device(s) and associated with
+their Fitbit profile.  Depending on the specific device model(s) and
+settings, this included second-by-second, minute-by-minute, daily
+summary, weekly summary, and/or monthly summary heart rate
+information.  These summaries include information about participants' average
+heart rates, and the amount of time they were estimated to have spent in
+different ``heart rate zones'' (rest, out-of-range, fat burn, cardio, or
+peak, as defined by their Fitbit profile), as well as an estimate of the number of estimated calories
+burned while in each heart rate zone.
+
+\paragraph{Sleep.}  If available, we extracted all sleep data collected
+by participants' Fitbit device(s).  Depending on the specific device
+model(s) and settings, this included nightly estimates of the duration
+and quality of sleep, as well as the amount of time spent in each
+sleep stage (awake, REM, light, or deep).
+
+\paragraph{Weight.}  If available, we extracted any weight-related
+information affiliated with particiants' Fitbit accounts within 1 year
+prior to enrolling in our study.  Depending on their specific device model(s) and
+settings, this included their weight, body mass index, and/or body fat
+percentage.
+
+\paragraph{Nutrition.} If available, we extracted any nutrition-related
+information affiliated with particiants' Fitbit accounts within 1 year
+prior to enrolling in our study. Depending on their specific account
+settings and usage behaviors, this
+included a log of the specific foods they had eaten (and logged)
+over the past year, and the amount of water consumed each day.
+
+\paragraph{Account and device settings.}  We extracted any settings
+associated with participants' Fitbit accounts to determine (a) which
+device(s) and model(s) are associated with their Fitbit account, (b)
+time(s) when their device(s) were last synced, and (c) battery
+level(s).
+
+\paragraph{Activity metrics.}  If available, we extracted any
+activity-related information affiliated with particiants' Fitbit
+accounts within 1 year prior to enrolling in our study.  Depending on
+their specific device model(s) and settings, this included: daily step
+counts; daily amount of time spent in each activity level (sedentary,
+lightly active, fairly active, or very active, as defined by their
+account settings and preferences); daily number of floors climbed;
+daily elevation change; and daily total distance traveled.
+
+\subsubsection*{Comparing recent versus baseline measurements.}
+We were interested in separating out potential associations between
+\textit{absolute} fitness metrics and \textit{relative} metrics.  To
+this end, in addition to assessing potential raw
+(absolute) fitness metrics, we also defined a simple measure of recent
+changes in those metrics, relative to a baseline.  We
+
+In order to study
 

### 2021-09-21 paper/main.tex
added description of exploratory correlation analysis

@@
 (absolute) fitness metrics, we also defined a simple measure of recent
-changes in those metrics, relative to a baseline.  We
-
-In order to study
+changes in those metrics, relative to a baseline:
+\[
+  \Delta_{R, B} m = \frac{\frac{1}{R} \sum_{i = 1}^R
+  m(i)}{\frac{1}{B} \sum_{i=R + 1}^{R+B}m(i)},
+\]
+where $m(i)$ is the value of metric $m$ from $i - 1$ days prior to testing (e.g.,
+$m(1)$ represents the value of $m$ on the day the participant accepted
+the HIT, and $m(10)$ represents the value of $m$ 9 days prior to
+accepting the HIT.  Unless otherwise noted, we set $R = 7$ and $B =
+30$.  In other words, to estimate recent changes in any metric $m$, we
+divided the average value of $m$ taken over the prior week by the
+average value of $m$ taken over the 30 days before that.
 
 \subsubsection*{Exploratory correlation analyses}
-\paragraph*{Imputation and interpolation of missing data.}
+We used a bootsrap procedure to identify reliable correlations between
+different memory-related, fitness-related, and demographic-related
+variables.  For each of $N = 1000$ iterations, we selected (with
+replacement) a sample of 113 participants to include.  This yielded,
+for each iteration, a sampled ``data matrix'' with one row per sampled
+participant and one column for each measured variable.  When
+participants were sampled multiple times in a given iteration, as was
+often the case, this matrix contained duplicate rows.  We used a
+round-robin imputation procedure to estimate the values of any missing
+features~\citep{Buck60}.  Next, we computed the Pearson's correlation
+between each pair of columns.  This yielded, for each pair of columns,
+a distribution of $N$ bootstrapped correlation coefficients.  If fewer
+than $95\%$ of the coefficients for a given pair of columns had the
+same sign, we excluded the pair from further analysis and considered
+the expected correlation between those columns to be undefined.  If
+$\geq 95\%$ of the coefficients for a given pair of columns had the
+same sign, we computed the expected correlation coefficient as:
+\[
+  \mathbb{E}_{i, j}\left[ r\right] = \tanh\left(\frac{1}{N} \sum_{n=1}^N
+  \tanh^{-1}(\mathrm{corr}\left(m(i)_n, m(j)_n\right))\right),
+\]
+where $m(x)_n$ represents column $x$ of the bootstrapped data matrix
+for iteration $n$, $\tanh$ is the hyperbolic tangent, and $\tanh^{-1}$
+is the inverse hyperbolic tangent.
 

### 2021-09-22 paper/main.tex
filled in description of regression-based prediction analyses

@@
 \subsubsection*{Regression-based prediction analyses}
+Following our exploratory correlation analyses, we used an analogous
+bootstrap procedure to identify subsets of memory-related,
+fitness-related, and demographic-related variables that predicted
+(non-overlapping) subsets of other variables.  For example, we tested
+whether a combination of fitness-related variables could predict a
+combination of memory-related variables, and so on.
+
+We used the same bootstrap procedure described above (used in our
+exploratory correlation analyses) to generate $N = 1000$ bootstrapped
+data matrices whose rows reflected sampled participants and whose
+columns reflected different measured variables.
+
+We grouped variables according to whether they were memory-related,
+fitness-related, or demographic-related.  For each bootstrap
+iteration, we divided the rows of that iterations data matrix into
+training and test sets.  The assignments of rows to these two sets was
+random, subject to the constraint that any duplicated rows in the data
+matrix (i.e., reflecting a single participant who had been sampled
+multiple times) was always assigned to either the training \textit{or}
+the test set--i.e., duplicated rows could not appear in both the
+training and the test sets.  The training sets always comprised 75\%
+of the data, and the tests sets comprised the remaining 25\% of the
+data.
+
+Next, we fit a series of ridge regression models to the training
+data.  Specifically, for each pairing of memory, fitness, and
+demographic variables, we fit a single ridge regression model treating
+the first variable group as the input features and the second variable
+group as the target features.  For example, one regression model used
+memory variables to predict fitness variables, and another regression
+model used fitness variables to predict demographic variables, and so
+on.  In total we fit six regression models to each training dataset.
+We then applied the fitted models to the held-out test dataset and
+computed the root mean squared deviation (RMSD) between the predicted and
+observed values in the target features of the test dataset.  We also
+examined the regression weights assigned to each input feature.  This
+yielded, for each regression model (across $N$ bootstrap iterations) a
+distribution of RMSD values and a distribution of weights for each
+input variable.
+
+We constructed a ``null'' distribution by using the same procedure as above,
+but where the columns in the test datasets were randomly permuted with
+each iteration (thereby breaking any meaningful predictive information
+between the training and test data).  We assessed the statistical
+significance ($p$-values) of the observed RMSD values by computing the proportions
+of null RMSD values that were less than the observed value.  We also
+assessed the significance of the observed regression weights using
+$t$-tests to compare the means of the observed versus null
+distributions of weights.
 

### 2021-09-22 paper/main.tex
finished complete draft of methods section

@@
       \end{itemize}
-    \item Fitness info (break down by task performance, potentiall
+    \item Fitness info (break down by task performance, potentially
       separately for each task); also separate out recent (raw) and recent versus baseline
@@
 \textbf{c. Foreign language flashcards.}  Participants study a
-sequence of 10 English-Gailic word pairs, each presented with an
+sequence of 10 English-Gaelic word pairs, each presented with an
 illustration of the given word.  During an immediate memory test,
@@
 to their nearest match.  We also manually corrected clear typos or
-mispellings by hand (e.g., we corrected ``hippoptumas'' to
+misspellings by hand (e.g., we corrected ``hippoptumas'' to
 ``hippopotamus'', ``zucinni'' to ``zucchini'', and so on).  Finally,
@@
 \paragraph{Weight.}  If available, we extracted any weight-related
-information affiliated with particiants' Fitbit accounts within 1 year
+information affiliated with participants' Fitbit accounts within 1 year
 prior to enrolling in our study.  Depending on their specific device model(s) and
@@
 \paragraph{Nutrition.} If available, we extracted any nutrition-related
-information affiliated with particiants' Fitbit accounts within 1 year
+information affiliated with participants' Fitbit accounts within 1 year
 prior to enrolling in our study. Depending on their specific account
@@
 \paragraph{Activity metrics.}  If available, we extracted any
-activity-related information affiliated with particiants' Fitbit
+activity-related information affiliated with participants' Fitbit
 accounts within 1 year prior to enrolling in our study.  Depending on
@@
 \[
-  \Delta_{R, B} m = \frac{\frac{1}{R} \sum_{i = 1}^R
-  m(i)}{\frac{1}{B} \sum_{i=R + 1}^{R+B}m(i)},
+  \Delta_{R, B} m = \frac{B \sum_{i = 1}^R
+  m(i)}{R \sum_{i=R + 1}^{R+B}m(i)},
 \]
@@
 \subsubsection*{Exploratory correlation analyses}
-We used a bootsrap procedure to identify reliable correlations between
+We used a bootstrap procedure to identify reliable correlations between
 different memory-related, fitness-related, and demographic-related
@@
 \subsubsection*{Reverse correlation analyses}
+We sought to characterize potential associations between the history
+of participants' fitness-related activities leading up to the time
+they participated in a memory task and their performance on the given
+task.  For each fitness-related variable, we constructed a timeseries
+matrix whose rows corresponded to timepoints (sampled once per day)
+leading up to the day the participant accepted the HIT for our study,
+and whose columns corresponded to different participants.  These
+matrices often contained missing entries, since different
+participants' Fitbit devices tracked fitness-related activities
+differently.  For example, participants whose Fitbit devices lacked
+heart rate sensors would have missing entries for any heart
+rate-related variables.  Or, if a given participant neglected to wear
+their fitness tracker on a particular day, the column corresponding to
+that participant would have missing entries for that day.
+
+In addition to this set of matrices storing timeseries data for each
+fitness-related variable, we also constructed a memory performance
+matrix, $M$, whose rows corresponded to different memory-related variables,
+and whose columns corresponded to different participants.  For
+example, one row of the memory performance matrix reflected the
+average proportion of words (across lists) that each
+participant remembered during the immediate free recall test, and so
+on.
+
+Given a fitness timeseries matrix, $F$, we computed the weighted
+average and weighted standard error of the mean of each row of $F$,
+where the weights were given by a particular memory-related variable
+(row of $M$).  For example, if $F$ contained participants' daily step
+counts, we could use any row of $M$ to compute a weighted average
+across any participants who contributed step count data on each day.
+Choosing a row of $M$ that corresponded to participants' performance
+on the naturalistic recall task would mean that participants who
+performed better on the naturalistic recall task would contribute more
+to the weighted average timeseries of daily step counts.
+Specifically, for each row, $t$, of $F$, we computed the weighted
+average (across the $S$ participants)  as:
+\[
+\bar{f}(t) = \sum_{s=1}^S \dot{m}(s) F(t, s),
+\]
+where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row of $M$
+corresponding to the chosen memory-related variable):
+\[
+  \dot{m} = \frac{m}{\sum_{s=1}^S \hat{m}(s)},
+\]
+where
+\[
+  \hat{m} = \frac{m - \min(m)}{\max(m) - \min(m)}
+\]
+
+We computed the weighted standard error of the mean as:
+\[
+\mathrm{SEM}_m\left(f(t)\right) = \frac{\left| \sum_{s=1}^S \left( F(t, s) -
+    \bar{f}(t)\right) \right|}{\sqrt{S}}.
+\]
+
+When a given row of $F$ was missing data from one or more
+participants, those participants were excluded from the weighted
+average for the corresponding timepoint and the weights (across all
+remaining participants) were re-normalized to sum to 1.
+The above procedure yielded, for each memory
+variable, a timeseries of average (and standard error of the mean)
+fitness tracking values leading up to the day of the experiment.
 

### 2021-09-22 paper/main.tex
updated descriptions of figures/analyses prior to implementing them

@@
 \section*{Results}
+Before testing our main hypothesis, we first examined the behavioral
+data from each memory task.  We expected that the general trends and
+tendancies in the behavioral data would follow previously reported
+behaviors from similar tasks that had been utilized in prior work.  We
+were also interested in characterizing the variability in task
+performance across participants.  For example, if all participants
+exhibited near-identical behaviors or performance on a given task, we
+would be unable to identify how memory performance varied with
+mental health or exercise.
+
 \begin{itemize}
-\item characterizing behaviors (potentially broken down by 3--4
-  fitness-defined categories, like activity level quartile; may also
-  want to have separate figures: one for characterizing behaviors on
-  average, and a second breaking down by fitness variable, e.g. after
-  the correlation analyses are presented)
+\item characterizing behaviors (color by quartile and continue the
+  color scheme in later figures-- hue reflects task, shading reflects
+  performance.  white outline means immediate, black outline means delayed)
   \begin{itemize}
-  \item Free recall: pfr, lag-CRP, spc
-    \item Naturalistic recall: reproduce a version of the sherlock
-      movie/recall trajectories
-    \item Foreign language flashcards: p(correct) by activity level
-      \item Spatial learning: mean error by number of shapes
+  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color: recall performance)
+    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
+      movie/recall trajectories (color: mean precision)
+    \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))
+      \item Spatial learning: mean error by number of shapes (color:
+        slope of line fit to errors as a function of the number of shapes)
       \end{itemize}
     \item Fitness info (break down by task performance, potentially
-      separately for each task); also separate out recent (raw) and recent versus baseline
+      separately for each task); also separate out recent (raw) and
+      recent versus baseline -- color using same color scheme as
+      behavior figure
       \begin{itemize}
@@
       \end{itemize}
-    \item Reverse correlations: look at recent changes versus baseline trends
+    \item Reverse correlations: look at recent changes versus baseline
+      trends (color using same scheme as behavior figure)
       \begin{itemize}
@@
 lists reported in \cite{ZimaEtal18}.  Each participant was assigned
-four unique randomly chosen lists (in a randomized order), selected from a full set of 16
-lists.  Each chosen list was then randomly shuffled before presenting
-the words to the participants.
+four unique randomly chosen lists (in a randomized order), selected
+from a full set of 16 lists.  Each chosen list was then randomly
+shuffled before presenting the words to the participants.
 
@@
 by Ronald Clark, who was interviewed by his daughter, Jamilah Clark.
-The narrator (Ronald) discusses growing up living in an apartment over Washington
-Heights branch of the New York Public Library, where his father worked
-as a custodian during the 1940s.
+The narrator (Ronald) discusses growing up living in an apartment over
+Washington Heights branch of the New York Public Library, where his
+father worked as a custodian during the 1940s.
 
@@
 enter their responses.  After 4~minutes participants were given the
-option of ending the response period early, e.g., if they felt they had finished
-entering all of the information they remembered.  Each participant's
-transcript was constructed from their submitted responses by combining
-the sentences into a single document and removing extraneous
-whitespace characters.
+option of ending the response period early, e.g., if they felt they
+had finished entering all of the information they remembered.  Each
+participant's transcript was constructed from their submitted
+responses by combining the sentences into a single document and
+removing extraneous whitespace characters.
 
@@
 to other commonly spoken languages amongst Mechanical Turk Workers.
-We verified (via self report) that all of our participants were fluent in English and
-that they were neither fluent nor familiar with Gaelic.
+We verified (via self report) that all of our participants were fluent
+in English and that they were neither fluent nor familiar with Gaelic.
 
-Each word's ``flashcard'' comprised a cartoon
-depicting the given word, the English word or phrase in lowercase text (e.g., ``the
+Each word's ``flashcard'' comprised a cartoon depicting the given
+word, the English word or phrase in lowercase text (e.g., ``the
 boy''), and the Gaelic word or phrase in uppercase text (e.g.,
-``BUACHAILL'').   Each
-flashcard was displayed for 4~s, followed by a 3~s interval (during
-which the screen was cleared) prior to the next flashcard
-presentation.
+``BUACHAILL'').  Each flashcard was displayed for 4~s, followed by a
+3~s interval (during which the screen was cleared) prior to the next
+flashcard presentation.
 
@@
 photographs, each depicting one of the 10 words they had learned.
-They were asked to select which (of 4 unique options) Gaelic word went with
-the given picture.  The 3 incorrect options were selected at random
-(with replacement across trials), and the order in which the choices
-appeared to the participant were also randomized.  Each of the 10
-words they had learned were tested exactly once.
+They were asked to select which (of 4 unique options) Gaelic word went
+with the given picture.  The 3 incorrect options were selected at
+random (with replacement across trials), and the order in which the
+choices appeared to the participant were also randomized.  Each of the
+10 words they had learned were tested exactly once.
 
@@
 choices for each question.  Each of the 10 original words they had
-learned were (again) tested exactly once during this final memory test.
+learned were (again) tested exactly once during this final memory
+test.
 
@@
 memorized the onscreen spatial locations of two or more shapes.
-During the study phrase of each trial, a set of shapes appeared on the screen for
-10~s, followed by 2~s of blank (white) screen.  During the test phase
-of each trial, the same shapes appeared onscreen again, but this time
-they were vertically aligned and sorted horizontally in a random
-order.  Participants were instructed to drag (using the mouse) each
-shape to its studied position, and then to click a button to indicate
-that the placements were complete.
+During the study phrase of each trial, a set of shapes appeared on the
+screen for 10~s, followed by 2~s of blank (white) screen.  During the
+test phase of each trial, the same shapes appeared onscreen again, but
+this time they were vertically aligned and sorted horizontally in a
+random order.  Participants were instructed to drag (using the mouse)
+each shape to its studied position, and then to click a button to
+indicate that the placements were complete.
 
@@
 2 shapes; next three trials where they learned the locations of 3
-shapes; and so on until their last three trials, where (during each trial) they learned
-the locations of 7 shapes.  All told, each participant performed 18
-study-test trials of this spatial learning task (3 trials for each of 2, 3,
-4, 5, 6, and 7 shapes).
+shapes; and so on until their last three trials, where (during each
+trial) they learned the locations of 7 shapes.  All told, each
+participant performed 18 study-test trials of this spatial learning
+task (3 trials for each of 2, 3, 4, 5, 6, and 7 shapes).
 
@@
 To gain access to our study, participants provided us with access to
-all data associated with their Fitbit account from the
-year (365 calendar days) up to and including the day they accepted the
-HIT.  We filtered out all identifiable information (e.g., participant names, GPS
-coordinates, etc.) prior to importing their data.
+all data associated with their Fitbit account from the year (365
+calendar days) up to and including the day they accepted the HIT.  We
+filtered out all identifiable information (e.g., participant names,
+GPS coordinates, etc.) prior to importing their data.
 
@@
 
-The fitness
-tracking data associated with participants' Fitbit accounts varied in
-scope and duration
-according to which device the participant owned (Fig.~\ref{fig:devices}), how often the
-participant wore (and/or synced) their tracking device, and how long they had owned their
-device.  For example, while all participants' devices supported basic
-activity metrics such as daily step counts, only a subset of the
-devices with heart rate monitoring capabilities provided information
-about workout intensity, resting heart rate, and other related
-measures.
+The fitness tracking data associated with participants' Fitbit
+accounts varied in scope and duration according to which device the
+participant owned (Fig.~\ref{fig:devices}), how often the participant
+wore (and/or synced) their tracking device, and how long they had
+owned their device.  For example, while all participants' devices
+supported basic activity metrics such as daily step counts, only a
+subset of the devices with heart rate monitoring capabilities provided
+information about workout intensity, resting heart rate, and other
+related measures.
 
@@
 
-Across all devices, we collected the following information: heart
-rate data, sleep tracking data, logged bodyweight measurements, logged
+Across all devices, we collected the following information: heart rate
+data, sleep tracking data, logged bodyweight measurements, logged
 nutrition measurements, Fitbit account and device settings, and
@@
 
-\paragraph{Heart rate.}  If available, we extracted all
-heart rate data collected by participants' Fitbit device(s) and associated with
+\paragraph{Heart rate.}  If available, we extracted all heart rate
+data collected by participants' Fitbit device(s) and associated with
 their Fitbit profile.  Depending on the specific device model(s) and
@@
 summary, weekly summary, and/or monthly summary heart rate
-information.  These summaries include information about participants' average
-heart rates, and the amount of time they were estimated to have spent in
-different ``heart rate zones'' (rest, out-of-range, fat burn, cardio, or
-peak, as defined by their Fitbit profile), as well as an estimate of the number of estimated calories
-burned while in each heart rate zone.
+information.  These summaries include information about participants'
+average heart rates, and the amount of time they were estimated to
+have spent in different ``heart rate zones'' (rest, out-of-range, fat
+burn, cardio, or peak, as defined by their Fitbit profile), as well as
+an estimate of the number of estimated calories burned while in each
+heart rate zone.
 
-\paragraph{Sleep.}  If available, we extracted all sleep data collected
-by participants' Fitbit device(s).  Depending on the specific device
-model(s) and settings, this included nightly estimates of the duration
-and quality of sleep, as well as the amount of time spent in each
-sleep stage (awake, REM, light, or deep).
+\paragraph{Sleep.}  If available, we extracted all sleep data
+collected by participants' Fitbit device(s).  Depending on the
+specific device model(s) and settings, this included nightly estimates
+of the duration and quality of sleep, as well as the amount of time
+spent in each sleep stage (awake, REM, light, or deep).
 
 \paragraph{Weight.}  If available, we extracted any weight-related
-information affiliated with participants' Fitbit accounts within 1 year
-prior to enrolling in our study.  Depending on their specific device model(s) and
-settings, this included their weight, body mass index, and/or body fat
-percentage.
+information affiliated with participants' Fitbit accounts within 1
+year prior to enrolling in our study.  Depending on their specific
+device model(s) and settings, this included their weight, body mass
+index, and/or body fat percentage.
 
-\paragraph{Nutrition.} If available, we extracted any nutrition-related
-information affiliated with participants' Fitbit accounts within 1 year
-prior to enrolling in our study. Depending on their specific account
-settings and usage behaviors, this
-included a log of the specific foods they had eaten (and logged)
-over the past year, and the amount of water consumed each day.
+\paragraph{Nutrition.} If available, we extracted any
+nutrition-related information affiliated with participants' Fitbit
+accounts within 1 year prior to enrolling in our study. Depending on
+their specific account settings and usage behaviors, this included a
+log of the specific foods they had eaten (and logged) over the past
+year, and the amount of water consumed each day.
 
@@
 \textit{absolute} fitness metrics and \textit{relative} metrics.  To
-this end, in addition to assessing potential raw
-(absolute) fitness metrics, we also defined a simple measure of recent
-changes in those metrics, relative to a baseline:
+this end, in addition to assessing potential raw (absolute) fitness
+metrics, we also defined a simple measure of recent changes in those
+metrics, relative to a baseline:
 \[
@@
 \]
-where $m(i)$ is the value of metric $m$ from $i - 1$ days prior to testing (e.g.,
-$m(1)$ represents the value of $m$ on the day the participant accepted
-the HIT, and $m(10)$ represents the value of $m$ 9 days prior to
-accepting the HIT.  Unless otherwise noted, we set $R = 7$ and $B =
-30$.  In other words, to estimate recent changes in any metric $m$, we
-divided the average value of $m$ taken over the prior week by the
-average value of $m$ taken over the 30 days before that.
+where $m(i)$ is the value of metric $m$ from $i - 1$ days prior to
+testing (e.g., $m(1)$ represents the value of $m$ on the day the
+participant accepted the HIT, and $m(10)$ represents the value of $m$
+9 days prior to accepting the HIT.  Unless otherwise noted, we set
+$R = 7$ and $B = 30$.  In other words, to estimate recent changes in
+any metric $m$, we divided the average value of $m$ taken over the
+prior week by the average value of $m$ taken over the 30 days before
+that.
 
 \subsubsection*{Exploratory correlation analyses}
-We used a bootstrap procedure to identify reliable correlations between
-different memory-related, fitness-related, and demographic-related
-variables.  For each of $N = 1000$ iterations, we selected (with
-replacement) a sample of 113 participants to include.  This yielded,
-for each iteration, a sampled ``data matrix'' with one row per sampled
-participant and one column for each measured variable.  When
-participants were sampled multiple times in a given iteration, as was
-often the case, this matrix contained duplicate rows.  We used a
+We used a bootstrap procedure to identify reliable correlations
+between different memory-related, fitness-related, and
+demographic-related variables.  For each of $N = 1000$ iterations, we
+selected (with replacement) a sample of 113 participants to include.
+This yielded, for each iteration, a sampled ``data matrix'' with one
+row per sampled participant and one column for each measured variable.
+When participants were sampled multiple times in a given iteration, as
+was often the case, this matrix contained duplicate rows.  We used a
 round-robin imputation procedure to estimate the values of any missing
@@
 
-Next, we fit a series of ridge regression models to the training
-data.  Specifically, for each pairing of memory, fitness, and
-demographic variables, we fit a single ridge regression model treating
-the first variable group as the input features and the second variable
-group as the target features.  For example, one regression model used
-memory variables to predict fitness variables, and another regression
-model used fitness variables to predict demographic variables, and so
-on.  In total we fit six regression models to each training dataset.
-We then applied the fitted models to the held-out test dataset and
-computed the root mean squared deviation (RMSD) between the predicted and
-observed values in the target features of the test dataset.  We also
-examined the regression weights assigned to each input feature.  This
-yielded, for each regression model (across $N$ bootstrap iterations) a
-distribution of RMSD values and a distribution of weights for each
-input variable.
+Next, we fit a series of ridge regression models to the training data.
+Specifically, for each pairing of memory, fitness, and demographic
+variables, we fit a single ridge regression model treating the first
+variable group as the input features and the second variable group as
+the target features.  For example, one regression model used memory
+variables to predict fitness variables, and another regression model
+used fitness variables to predict demographic variables, and so on.
+In total we fit six regression models to each training dataset.  We
+then applied the fitted models to the held-out test dataset and
+computed the root mean squared deviation (RMSD) between the predicted
+and observed values in the target features of the test dataset.  We
+also examined the regression weights assigned to each input feature.
+This yielded, for each regression model (across $N$ bootstrap
+iterations) a distribution of RMSD values and a distribution of
+weights for each input variable.
 
-We constructed a ``null'' distribution by using the same procedure as above,
-but where the columns in the test datasets were randomly permuted with
-each iteration (thereby breaking any meaningful predictive information
-between the training and test data).  We assessed the statistical
-significance ($p$-values) of the observed RMSD values by computing the proportions
-of null RMSD values that were less than the observed value.  We also
-assessed the significance of the observed regression weights using
-$t$-tests to compare the means of the observed versus null
-distributions of weights.
+We constructed a ``null'' distribution by using the same procedure as
+above, but where the columns in the test datasets were randomly
+permuted with each iteration (thereby breaking any meaningful
+predictive information between the training and test data).  We
+assessed the statistical significance ($p$-values) of the observed
+RMSD values by computing the proportions of null RMSD values that were
+less than the observed value.  We also assessed the significance of
+the observed regression weights using $t$-tests to compare the means
+of the observed versus null distributions of weights.
 
@@
 fitness-related variable, we also constructed a memory performance
-matrix, $M$, whose rows corresponded to different memory-related variables,
-and whose columns corresponded to different participants.  For
-example, one row of the memory performance matrix reflected the
-average proportion of words (across lists) that each
-participant remembered during the immediate free recall test, and so
-on.
+matrix, $M$, whose rows corresponded to different memory-related
+variables, and whose columns corresponded to different participants.
+For example, one row of the memory performance matrix reflected the
+average proportion of words (across lists) that each participant
+remembered during the immediate free recall test, and so on.
 
@@
 \]
-where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row of $M$
-corresponding to the chosen memory-related variable):
+where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row
+of $M$ corresponding to the chosen memory-related variable):
 \[
@@
 average for the corresponding timepoint and the weights (across all
-remaining participants) were re-normalized to sum to 1.
-The above procedure yielded, for each memory
-variable, a timeseries of average (and standard error of the mean)
-fitness tracking values leading up to the day of the experiment.
+remaining participants) were re-normalized to sum to 1.  The above
+procedure yielded, for each memory variable, a timeseries of average
+(and standard error of the mean) fitness tracking values leading up to
+the day of the experiment.
 
 \section*{Acknowledgements}
-We acknowledge useful discussions with David Bucci, Emily Glasser, Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten Ziman.
-Our work was supported in part by the Dartmouth Young Minds and Brains initiative.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
-This paper is dedicated to the memory of David Bucci, who helped to inspire the theoretical foundations of this work.
-Dave served as a mentor and colleague on the project prior to his passing.
+We acknowledge useful discussions with David Bucci, Emily Glasser,
+Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten
+Ziman.  Our work was supported in part by the Dartmouth Young Minds
+and Brains initiative.  The content is solely the responsibility of
+the authors and does not necessarily represent the official views of
+our supporting organizations.  This paper is dedicated to the memory
+of David Bucci, who helped to inspire the theoretical foundations of
+this work.  Dave served as a mentor and colleague on the project prior
+to his passing.
 
 \section*{Data and code availability}
-All analysis code and data used in the present manuscript may be found \href{https://github.com/ContextLab/brainfit-paper}{\underline{here}}.
+All analysis code and data used in the present manuscript may be found
+\href{https://github.com/ContextLab/brainfit-paper}{\underline{here}}.
 

### 2021-09-22 paper/main.tex
working on FR analyses

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/free_recall_behavior}
+\caption{\textbf{Free recall behavioral results.}}
+\label{fig:fr_behavioral}
+\end{figure}
+
 \begin{itemize}
@@
   \begin{itemize}
-  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color: recall performance)
+  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
+    recall performance).  Note: for delayed pfr and spc, need to collapse
+    across lists (current figure doesn't do this...).
+    Figure~\ref{fig:fr_behavioral}.  Also collapse across lists for
+    delayed analysis...
     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock

### 2021-09-24 paper/main.tex
added some notes

@@
       \item Spatial learning: mean error by number of shapes (color:
-        slope of line fit to errors as a function of the number of shapes)
+        slope of line fit to errors as a function of the number of
+        shapes)
       \end{itemize}
@@
         \end{itemize}
-  \item exploratory analysis (correlations)
+  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
+          tasks.  Diagonal: histogram of performance metric for that
+          task.  Above-diagonal entries: compare performance across
+          tasks (by subject).  Below-diagonal entries: empty?
+          density/2d histograms?
     \begin{itemize}
@@
     \item Reverse correlations: look at recent changes versus baseline
-      trends (color using same scheme as behavior figure)
+      trends (color using same scheme as behavior figures).  Possibly 
       \begin{itemize}

### 2021-10-04 paper/main.tex
added naturalistic recall figure

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
+\caption{\textbf{Naturalistic recall behavioral results.}}
+\label{fig:nat_behavioral}
+\end{figure}
+
 \begin{itemize}
@@
   \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
-    recall performance).  Note: for delayed pfr and spc, need to collapse
-    across lists (current figure doesn't do this...).
-    Figure~\ref{fig:fr_behavioral}.  Also collapse across lists for
-    delayed analysis...
+    recall performance).  
+    Figure~\ref{fig:fr_behavioral}.
     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
-      movie/recall trajectories (color: mean precision)
+      movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
     \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))

### 2021-10-06 paper/main.tex
added vocab learning figs
added summary figures for immediate and delayed memory behaviors-- todo: move detailed figs to supplement

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
+\caption{\textbf{Foreign language vocabulary learning behavioral results.}}
+\label{fig:vocab_behavioral}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
+\caption{\textbf{Spatial learning behavioral results.}}
+\label{fig:spatial_behavioral}
+\end{figure}
+
 \begin{itemize}
@@
       movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
-    \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))
+    \item Foreign language flashcards (immediate + delayed):
+      p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
       \item Spatial learning: mean error by number of shapes (color:
-        slope of line fit to errors as a function of the number of
-        shapes)
+        intercept and slope of line fit to errors as a function of the number of
+        shapes).  Figure~\ref{fig:spatial_behavioral}.
       \end{itemize}

### 2021-10-07 paper/supplement.tex
moved detailed behavioral results to supplement; added summary behavioral figures to main text

--- 2021-10-06 paper/main.tex
@@
 
-\title{Fitness tracking reveals task-specific associations between
+\title{\textit{Supplementary materials for} Fitness tracking reveals task-specific associations between
   memory, mental health, and exercise}
@@
 
-\begin{abstract}
-  Physical exercise can benefit both physical and mental well-being.
-  Different forms of exercise (i.e., aerobic versus anaerobic; running
-  versus walking versus swimming versus yoga; high-intensity interval
-  training versus endurance workouts; etc.) impact physical fitness
-  in different ways.  For example, running may substantially impact
-  leg and heart strength but only moderately impact arm strength. We
-  hypothesized that the mental benefits of exercise might be similarly
-  differentiated.  We focused specifically on how different forms of
-  exercise might related to different aspects of memory and mental
-  health.  To test our hypothesis, we collected nearly a century's
-  worth of fitness data (in aggregate).  We then asked participants to
-  fill out surveys asking them to self-report on different aspects of
-  their mental health.  We also asked participants to engage in a
-  battery of memory tasks that tested their short and long term
-  episodic, semantic, and spatial memory.  We found that participants
-  with similar exercise habits and fitness profiles tended to also
-  exhibit similar mental health and task performance profiles.
-\end{abstract}
-
-\section*{Introduction}
-Engaging in physical activity (exercise) can improve our physical
-fitness by increasing muscle strength~\citep{RogeEvan93, Lind79,
-  CranEtal13, Knut07}, increasing bone density~\citep{ChilEtal12,
-  BassRams94, LaynNels99}, increasing cardiovascular
-performance~\citep{MaioEtal00, PollEtal00}, increasing lung
-capacity~\citep{LazoEtal16}~\citep[although see][]{RomaEtal16},
-increasing endurance~\citep{WilmKnut03}, and more.  Exercise can also
-improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
-  DeslEtal09, Call04, PaluSchw00, BassSuzu17} and cognitive performance~\citep{ChanEtal12b,
-  BrisEtal02, EtniEtal06, BassSuzu17}.
-
-The physical benefits of exercise can be explained by stress-responses
-of the affected body tissues. For example, skeletal muscles that are
-taxed during exercise exhibit stress responses~\citep{MortEtal09} that
-can in turn affect their growth or atrophy~\citep{SchiEtal13}.  By
-comparison, the benefits of exercise on mental health are less direct.  For
-example, one hypothesis is that exercise leads to specific
-physiological changes, such as increased aminergic synaptic
-transmission and endorphin release, which in turn act on
-neurotransmitters in the brain~\citep{PaluSchw00}.
-
-Speculatively, if different exercise regimens lead to different
-neurophysiological responses, one might be able to map out a spectrum
-of signalling and transduction pathways that are impacted by a given
-type, duration, and intensity of exercise in each brain region.  For
-example, prior work has shown that exercise increases acetylcholine
-levels, starting in the vicinity of the exercised
-muscles~\citep{ShoeEtal97}.  Acetylcholine is thought to play an
-important role in memory formation~\citep[e.g., by modulating specific
-synaptic inputs from entorhinal cortex to the hippocampus, albeit in
-rodents;]{PalaEtal21}.  Given the central role of these medial
-temporal lobe structures play in memory, changes in acetylcholine
-might lead to specific changes in memory formation and retrieval.
-
-In the present study, we hypothesize that (a) different exercise regimens will
-have different, quantifiable impacts on cognitive performance and
-mental health, and that (b) these impacts will be consistant across
-individuals.  To this end, we collected a year of fitness tracking
-data from each of 113 participants.  We then asked each participant to
-fill out a brief survey in which they self-evaluated several aspects
-of their mental health.  Finally, we ran each participant through a
-battery of memory tasks, which we used to evaluate their memory
-performance along several dimensions.  We examined the data for
-potential associations between memory, mental health, and exercise.
-
-\section*{Results}
-Before testing our main hypothesis, we first examined the behavioral
-data from each memory task.  We expected that the general trends and
-tendancies in the behavioral data would follow previously reported
-behaviors from similar tasks that had been utilized in prior work.  We
-were also interested in characterizing the variability in task
-performance across participants.  For example, if all participants
-exhibited near-identical behaviors or performance on a given task, we
-would be unable to identify how memory performance varied with
-mental health or exercise.
-
-\begin{figure}[tp]
+\begin{figure}[p]
 \centering
@@
 
-\begin{figure}[tp]
+\begin{figure}[p]
 \centering
@@
 
-\begin{itemize}
-\item characterizing behaviors (color by quartile and continue the
-  color scheme in later figures-- hue reflects task, shading reflects
-  performance.  white outline means immediate, black outline means delayed)
-  \begin{itemize}
-  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
-    recall performance).  
-    Figure~\ref{fig:fr_behavioral}.
-    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
-      movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
-    \item Foreign language flashcards (immediate + delayed):
-      p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
-      \item Spatial learning: mean error by number of shapes (color:
-        intercept and slope of line fit to errors as a function of the number of
-        shapes).  Figure~\ref{fig:spatial_behavioral}.
-      \end{itemize}
-    \item Fitness info (break down by task performance, potentially
-      separately for each task); also separate out recent (raw) and
-      recent versus baseline -- color using same color scheme as
-      behavior figure
-      \begin{itemize}
-      \item activity (steps, zone minutes, floors/elevation)
-      \item resting heart rate
-        \item sleep
-        \end{itemize}
-  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
-          tasks.  Diagonal: histogram of performance metric for that
-          task.  Above-diagonal entries: compare performance across
-          tasks (by subject).  Below-diagonal entries: empty?
-          density/2d histograms?
-    \begin{itemize}
-    \item Memory-memory
-    \item fitness-fitness
-    \item survey-survey
-    \item (fitness + survey)-memory
-    \end{itemize}
-  \item predictive analysis (regressions)
-    \begin{itemize}
-    \item Predict memory performance on held-out task from other tasks
-    \item Predict memory performance on each task using fitness data
-      \item Predict memory performance on each task using survey data
-      \end{itemize}
-    \item Reverse correlations: look at recent changes versus baseline
-      trends (color using same scheme as behavior figures).  Possibly 
-      \begin{itemize}
-      \item Fitness profile that predicts performance on each task (barplots + timelines)
-      \item Fitness profile for each survey demographic (barplots + timelines)
-        \begin{itemize}
-          \item Select out mental health demographics (based on meds, stress levels)
-          \end{itemize}
-        \end{itemize}
-  \end{itemize}
-
-  \section*{Discussion}
-  \begin{itemize}
-  \item summarize key findings
-  \item correlation versus causation
-         \item what can vs.
-can't we know?
-we can identify correlations, but not causal direction-- e.g.
-we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.
-that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
-  \item related work (exercise/memory, exercise/mental health), what this study adds
-    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
-    \end{itemize}
-
-    \section*{Methods}
-
-    We ran an online experiment using the Amazon Mechanical Turk
-    platform.  We collected data about each participant's fitness and
-    exercise habits, a variety of self-reported measures concerning their
-    mental health, and about their performance on a battery of memory
-    tasks.  We mined the dataset for potential associations between
-    memory, mental health, and exercise.
-
-\subsection*{Experiment}
-\subsubsection*{Participants}
-We recruited experimental participants by posting our experiment as a
-Human Intelligence Task (HIT) on the Amazon Mechanical Turk platform.
-We limited participation to Mechanical Turk Workers who had been
-assigned a ``Masters'' designation on the platform, given to workers
-who score highly across several metrics on a large number of HITs,
-according to a proprietary algorithm managed by Amazon.  We further
-limited our participant pool to participants who self-reported that
-they were fluent in English and regularly used a Fitbit fitness
-tracker device.  A total of 160 workers accepted our
-HIT in order to participate in our experiment.  Of these, we excluded all
-participants who failed to log into their Fitbit account (giving us
-access to their anonymized fitness tracking data), encountered
-technical issues (e.g., by accessing the HIT using an incompatible browser, device, or
-operating system), or who ended their participation prematurely,
-before completing the full study.  In all, 113 participants remained
-that contributed usable data to the study.
-
-For their participation, workers received a base payment of \$5 per hour (computed in 15
-minute increments, rounded up to the nearest 15 minutes), plus an
-additional performance-based bonus of up to \$5.  Our recruitment
-procedure and study protocol
-were approved by Dartmouth's Committee for the Protection of Human Subjects.
-
-\paragraph{Gender, age, and race.}
-Of the 113 participants who contributed usable data, 77 reported their gender as female, 35 as
-male, and 1 chose not to report their gender.  Participants ranged in
-age from 19--68 years old (25\textsuperscript{th} percentile: 28.25
-years; 50\textsuperscript{th} percentile: 32 years;
-75\textsuperscript{th} percentile: 38 years).  Participants reported
-their race as White (90 participants), Black or African American (11
-participants), Asian (7 participants), Other (4 participants), and
-American Indian or Alaska Native (3 participants).  One participant
-opted not to report their race.
-
-\paragraph{Languages.}
-All participants reported that they were fluent in either 1 and 2
-languages (25\textsuperscript{th} percentile: 1;
-50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
-percentile: 1), and that they were ``familiar'' with between 1 and 11
-languages (25\textsuperscript{th} percentile: 1;
-50\textsuperscript{th} percentile: 2; 75\textsuperscript{th}
-percentile: 3).
-
-\paragraph{Reported medical conditions and medications.}
-Participants reported having and/or taking medications pertaining to the following medical conditions: anxiety or
-depression (4 participants), recent head injury (2 participants), high
-blood pressure (1 participant), bipolar (1 participant),
-hypothyroidism (1 participant), and other unspecified medications (1
-participant).  Participants reported their current and typical stress
-levels on a Likert scale as very relaxed (-2), a little relaxed (-1),
-neutral (0), a little stressed (1), or very stressed (2).  The
-``current'' stress level reflected participants' stress at the time
-they participated in the experiment.
-Their responses
-ranged from -2 to 2 (current stress: 25\textsuperscript{th} percentile: -2;
-50\textsuperscript{th} percentile: -1; 75\textsuperscript{th}
-percentile: 1; typical stress: 25\textsuperscript{th} percentile: 0;
-50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
-percentile: 1).  Participants also reported their current level of
-alertness on a Likert scale as very sluggish (-2), a little sluggish
-(-1), neutral (0), a little alert (1), or very alert (2).  Their
-responses ranged from -2 to 2 (25\textsuperscript{th} percentile: 0;
-50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
-percentile: 2).  Nearly all (111 out of 113) participants reported
-that they had normal color vision, and 15 participants reported
-uncorrected visual impairments (including dyslexia and uncorrected
-near- or far-sightedness).
-
-\paragraph{Residence and level of education.}
-Participants reported their residence
-as being located in the suburbs (36 participants), a large city (30
-participants), a small city (23 participants), rural (14
-participants), or a small town (10 participants).  Participants
-reported their level of education as follows: College graduate (42
-participants), Master's degree (23 participants), Some college (21
-participants), High school graduate (9 participants), Associate's
-degree (8 participants), Other graduate or professional school (5
-participants), Some graduate training (3 participants), or Doctorate
-(2 participants).
-
-\paragraph{Reported water and coffee intake.}
-Participants reported the number of cups of water and coffee they had
-consumed prior to accepting the HIT.  Water consumption ranged from
-0--6 cups (25\textsuperscript{th} percentile: 1;
-50\textsuperscript{th} percentile: 3; 75\textsuperscript{th}
-percentile: 4).  Coffee consumption ranged from 0--4 cups (25\textsuperscript{th} percentile: 0;
-50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
-percentile: 2).
-
-\subsubsection*{Tasks}
-Upon accepting the HIT posted on Mechanical Turk, the worker was
-directed to read and fill out a screening and consent form, and to
-share access to their anonymized Fitbit data via their Fitbit account.
-After consenting to participant and successfully sharing their Fitbit
-data, participants filled out a survey and then engaged in a series of
-memory tasks (Fig.~\ref{fig:tasks}).  All stimuli and code for running
-the full Mechanical Turk experiment may be found
-\href{https://github.com/ContextLab/brainfit-task}{\underline{here}}.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/experiment}
-\caption{\textbf{Battery of memory tasks.}  \textbf{a.  Free recall.}
-Participants study 16 words (presented one at a time), followed by an
-immediate memory test where they type
-each word they remember from the just-studied list.  In the delayed
-memory test, participants type any words they remember studying, from
-any list.  \textbf{b. Naturalistic recall.}  Participants watch a
-brief video, followed by two immediate memory tests.  The first test
-asks participants to write out what happened in the video.  The second
-test has participants answer a series of multiple choice questions
-about the conceptual content of the video.  In the delayed memory
-test, participants (again) write out what happened in the video.
-\textbf{c. Foreign language flashcards.}  Participants study a
-sequence of 10 English-Gaelic word pairs, each presented with an
-illustration of the given word.  During an immediate memory test,
-participants perform a multiple choice test where they select the
-Gaelic word that corresponds to the given photograph.  During the
-delayed memory test, participants perform a second multiple choice
-test, where they select the Gaelic word that corresponds to each of a
-new set of photographs.  \textbf{d. Spatial learning.}  In each trial,
-participants
-study a set of randomly positioned shapes.  Next, the shapes'
-positions are altered, and participants are asked to drag the shapes
-back to their previous positions.  \textbf{All panels.}  The gray
-numbers denote the order in which participants experienced each task
-or test.}
-\label{fig:tasks}
-\end{figure}
-
-\paragraph*{Survey questions.}  We collected the following demographic
-information from each participant: their birth year, gender, highest
-(academic) degree achieved, race, language fluency, and language
-familiarity.  We also collected information about participants'
-health and wellness, including about their vision, alertness, stress, sleep, coffee
-and water consumption, location of their residence, activity typically
-required for their job, and exercise habits.
-
-\paragraph*{Free recall (Fig.~\ref{fig:tasks}a).} 
-Participants studied a sequence of four word lists, each comprising 16
-words.  After studying each list, participants received an immediate
-memory test, whereby they were asked to type (one word at a time) any
-words they remembered from the just-studied list, in any order.
-
-Words were presented for 2~s each, in black text on a white
-background, followed by a 2~s blank (white) screen.  After the final
-2~s pause, participants were given 90~s to type in as many words as
-they could remember, in any order.  The memory test was constructed
-such that the participant could only see the text of the current word
-they were typing; when they pressed any non-letter key, the current
-word was submitted and the text box they were typing in was cleared.
-This was intended to prevent participants from retroactively editing
-their previous responses.
-
-The word lists participants studied were drawn from the categorized
-lists reported in \cite{ZimaEtal18}.  Each participant was assigned
-four unique randomly chosen lists (in a randomized order), selected
-from a full set of 16 lists.  Each chosen list was then randomly
-shuffled before presenting the words to the participants.
-
-Participants also performed a final delayed memory test where they
-were given 180~s to type out any words they remembered from
-\textit{any} of the 4 lists they had studied.
-
-Recalled words within an edit distance of 2 (i.e., a Levenshtein Distance less
-than or equal to 2) of any word in the wordpool were ``autocorrected''
-to their nearest match.  We also manually corrected clear typos or
-misspellings by hand (e.g., we corrected ``hippoptumas'' to
-``hippopotamus'', ``zucinni'' to ``zucchini'', and so on).  Finally,
-we lemmatized each submitted word to match the plurality of the
-matching wordpool word (e.g., ``bongo'' was corrected to ``bongos'',
-and so on).  After applying these corrections, any submitted words
-that matched words presented on the just-studied list were tagged as
-``correct'' recalls, and any non-matching words were discarded as
-``errors.''  Because participants were not allowed to edit the text
-they entered, we chose not to analyze these putative ``errors,'' since
-we could not distinguish typos from true misrememberings.
-
-\paragraph*{Naturalistic recall (Fig.~\ref{fig:tasks}b).}
-Participants watched a 2.5~minute video clip entitled ``The Temple of
-Knowledge.''  The video comprises an animated story told to StoryCorps
-by Ronald Clark, who was interviewed by his daughter, Jamilah Clark.
-The narrator (Ronald) discusses growing up living in an apartment over
-Washington Heights branch of the New York Public Library, where his
-father worked as a custodian during the 1940s.
-
-After watching the video clip, participants were asked to type out
-anything they remembered about what happened in the video.  They typed
-their responses into a text box, one sentence at a time.  When the
-participant pressed the return key or typed any final punctuation mark
-(``.'', ``!'', or ``?'') the text currently entered into the box was
-``submitted'' and added to their transcript, and the text box was
-cleared to prevent further editing of any already-submitted text.
-This was intended to prevent participants from retroactively editing
-their previous responses.  Participants were given up to 10~minutes to
-enter their responses.  After 4~minutes participants were given the
-option of ending the response period early, e.g., if they felt they
-had finished entering all of the information they remembered.  Each
-participant's transcript was constructed from their submitted
-responses by combining the sentences into a single document and
-removing extraneous whitespace characters.
-
-Following this 4--10 minute free response period, participants were
-given a series of 10 multiple choice questions about the conceptual
-content of the story.  All participants received the same questions,
-in the same order.
-
-Participants also performed a final delayed memory test, where they
-carried out the free response recall task a second time, near the end
-of the testing session.  This resulted in a second transcript, for
-each participant.
-
-\paragraph*{Foreign language flashcards (Fig.~\ref{fig:tasks}c).}
-Participants studied a series of 10 English-Gaelic word pairs in a
-randomized order.  We selected the Gaelic language both for its
-relatively small number of native speakers and for its dissimilarity
-to other commonly spoken languages amongst Mechanical Turk Workers.
-We verified (via self report) that all of our participants were fluent
-in English and that they were neither fluent nor familiar with Gaelic.
-
-Each word's ``flashcard'' comprised a cartoon depicting the given
-word, the English word or phrase in lowercase text (e.g., ``the
-boy''), and the Gaelic word or phrase in uppercase text (e.g.,
-``BUACHAILL'').  Each flashcard was displayed for 4~s, followed by a
-3~s interval (during which the screen was cleared) prior to the next
-flashcard presentation.
-
-After studying all 10 flashcards, participants were given a multiple
-choice memory test where they were shown a series of novel
-photographs, each depicting one of the 10 words they had learned.
-They were asked to select which (of 4 unique options) Gaelic word went
-with the given picture.  The 3 incorrect options were selected at
-random (with replacement across trials), and the order in which the
-choices appeared to the participant were also randomized.  Each of the
-10 words they had learned were tested exactly once.
-
-Participants also performed a final delayed memory test, where they
-were given a second set of 10 questions (again, one per word they had
-studied).  For this second set of questions participants were prompted
-with a new set of novel photographs, and new randomly chosen incorrect
-choices for each question.  Each of the 10 original words they had
-learned were (again) tested exactly once during this final memory
-test.
-
-\paragraph*{Spatial learning (Fig.~\ref{fig:tasks}d).}
-Participants performed a series of study-test trials where they
-memorized the onscreen spatial locations of two or more shapes.
-During the study phrase of each trial, a set of shapes appeared on the
-screen for 10~s, followed by 2~s of blank (white) screen.  During the
-test phase of each trial, the same shapes appeared onscreen again, but
-this time they were vertically aligned and sorted horizontally in a
-random order.  Participants were instructed to drag (using the mouse)
-each shape to its studied position, and then to click a button to
-indicate that the placements were complete.
-
-In different study-test trials, participants learned the locations of
-different numbers of shapes (always drawn from the same pool of 7
-unique shapes, where each shape appeared at most one time per trial).
-They first performed three trials where they learned the locations of
-2 shapes; next three trials where they learned the locations of 3
-shapes; and so on until their last three trials, where (during each
-trial) they learned the locations of 7 shapes.  All told, each
-participant performed 18 study-test trials of this spatial learning
-task (3 trials for each of 2, 3, 4, 5, 6, and 7 shapes).
-
-\subsubsection*{Fitness tracking using Fitbit devices}
-To gain access to our study, participants provided us with access to
-all data associated with their Fitbit account from the year (365
-calendar days) up to and including the day they accepted the HIT.  We
-filtered out all identifiable information (e.g., participant names,
-GPS coordinates, etc.) prior to importing their data.
-
-\subsubsection*{Collecting and processing Fitbit data}
-
-The fitness tracking data associated with participants' Fitbit
-accounts varied in scope and duration according to which device the
-participant owned (Fig.~\ref{fig:devices}), how often the participant
-wore (and/or synced) their tracking device, and how long they had
-owned their device.  For example, while all participants' devices
-supported basic activity metrics such as daily step counts, only a
-subset of the devices with heart rate monitoring capabilities provided
-information about workout intensity, resting heart rate, and other
-related measures.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/devices}
-\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
-  participants whose fitness tracking data came from each model of
-  Fitbit device.  ``MobileTrack'' refers to participants who used
-  smartphone accelerometer information to track their activity via the
-  Fitbit smartphone app.
-  ``Unknown''  denotes participants whose device information was not
-  available from their available Fitbit data.}
-\label{fig:devices}
-\end{figure}
-
-Across all devices, we collected the following information: heart rate
-data, sleep tracking data, logged bodyweight measurements, logged
-nutrition measurements, Fitbit account and device settings, and
-activity metrics.
-
-\paragraph{Heart rate.}  If available, we extracted all heart rate
-data collected by participants' Fitbit device(s) and associated with
-their Fitbit profile.  Depending on the specific device model(s) and
-settings, this included second-by-second, minute-by-minute, daily
-summary, weekly summary, and/or monthly summary heart rate
-information.  These summaries include information about participants'
-average heart rates, and the amount of time they were estimated to
-have spent in different ``heart rate zones'' (rest, out-of-range, fat
-burn, cardio, or peak, as defined by their Fitbit profile), as well as
-an estimate of the number of estimated calories burned while in each
-heart rate zone.
-
-\paragraph{Sleep.}  If available, we extracted all sleep data
-collected by participants' Fitbit device(s).  Depending on the
-specific device model(s) and settings, this included nightly estimates
-of the duration and quality of sleep, as well as the amount of time
-spent in each sleep stage (awake, REM, light, or deep).
-
-\paragraph{Weight.}  If available, we extracted any weight-related
-information affiliated with participants' Fitbit accounts within 1
-year prior to enrolling in our study.  Depending on their specific
-device model(s) and settings, this included their weight, body mass
-index, and/or body fat percentage.
-
-\paragraph{Nutrition.} If available, we extracted any
-nutrition-related information affiliated with participants' Fitbit
-accounts within 1 year prior to enrolling in our study. Depending on
-their specific account settings and usage behaviors, this included a
-log of the specific foods they had eaten (and logged) over the past
-year, and the amount of water consumed each day.
-
-\paragraph{Account and device settings.}  We extracted any settings
-associated with participants' Fitbit accounts to determine (a) which
-device(s) and model(s) are associated with their Fitbit account, (b)
-time(s) when their device(s) were last synced, and (c) battery
-level(s).
-
-\paragraph{Activity metrics.}  If available, we extracted any
-activity-related information affiliated with participants' Fitbit
-accounts within 1 year prior to enrolling in our study.  Depending on
-their specific device model(s) and settings, this included: daily step
-counts; daily amount of time spent in each activity level (sedentary,
-lightly active, fairly active, or very active, as defined by their
-account settings and preferences); daily number of floors climbed;
-daily elevation change; and daily total distance traveled.
-
-\subsubsection*{Comparing recent versus baseline measurements.}
-We were interested in separating out potential associations between
-\textit{absolute} fitness metrics and \textit{relative} metrics.  To
-this end, in addition to assessing potential raw (absolute) fitness
-metrics, we also defined a simple measure of recent changes in those
-metrics, relative to a baseline:
-\[
-  \Delta_{R, B} m = \frac{B \sum_{i = 1}^R
-  m(i)}{R \sum_{i=R + 1}^{R+B}m(i)},
-\]
-where $m(i)$ is the value of metric $m$ from $i - 1$ days prior to
-testing (e.g., $m(1)$ represents the value of $m$ on the day the
-participant accepted the HIT, and $m(10)$ represents the value of $m$
-9 days prior to accepting the HIT.  Unless otherwise noted, we set
-$R = 7$ and $B = 30$.  In other words, to estimate recent changes in
-any metric $m$, we divided the average value of $m$ taken over the
-prior week by the average value of $m$ taken over the 30 days before
-that.
-
-\subsubsection*{Exploratory correlation analyses}
-We used a bootstrap procedure to identify reliable correlations
-between different memory-related, fitness-related, and
-demographic-related variables.  For each of $N = 1000$ iterations, we
-selected (with replacement) a sample of 113 participants to include.
-This yielded, for each iteration, a sampled ``data matrix'' with one
-row per sampled participant and one column for each measured variable.
-When participants were sampled multiple times in a given iteration, as
-was often the case, this matrix contained duplicate rows.  We used a
-round-robin imputation procedure to estimate the values of any missing
-features~\citep{Buck60}.  Next, we computed the Pearson's correlation
-between each pair of columns.  This yielded, for each pair of columns,
-a distribution of $N$ bootstrapped correlation coefficients.  If fewer
-than $95\%$ of the coefficients for a given pair of columns had the
-same sign, we excluded the pair from further analysis and considered
-the expected correlation between those columns to be undefined.  If
-$\geq 95\%$ of the coefficients for a given pair of columns had the
-same sign, we computed the expected correlation coefficient as:
-\[
-  \mathbb{E}_{i, j}\left[ r\right] = \tanh\left(\frac{1}{N} \sum_{n=1}^N
-  \tanh^{-1}(\mathrm{corr}\left(m(i)_n, m(j)_n\right))\right),
-\]
-where $m(x)_n$ represents column $x$ of the bootstrapped data matrix
-for iteration $n$, $\tanh$ is the hyperbolic tangent, and $\tanh^{-1}$
-is the inverse hyperbolic tangent.
-
-\subsubsection*{Regression-based prediction analyses}
-Following our exploratory correlation analyses, we used an analogous
-bootstrap procedure to identify subsets of memory-related,
-fitness-related, and demographic-related variables that predicted
-(non-overlapping) subsets of other variables.  For example, we tested
-whether a combination of fitness-related variables could predict a
-combination of memory-related variables, and so on.
-
-We used the same bootstrap procedure described above (used in our
-exploratory correlation analyses) to generate $N = 1000$ bootstrapped
-data matrices whose rows reflected sampled participants and whose
-columns reflected different measured variables.
-
-We grouped variables according to whether they were memory-related,
-fitness-related, or demographic-related.  For each bootstrap
-iteration, we divided the rows of that iterations data matrix into
-training and test sets.  The assignments of rows to these two sets was
-random, subject to the constraint that any duplicated rows in the data
-matrix (i.e., reflecting a single participant who had been sampled
-multiple times) was always assigned to either the training \textit{or}
-the test set--i.e., duplicated rows could not appear in both the
-training and the test sets.  The training sets always comprised 75\%
-of the data, and the tests sets comprised the remaining 25\% of the
-data.
-
-Next, we fit a series of ridge regression models to the training data.
-Specifically, for each pairing of memory, fitness, and demographic
-variables, we fit a single ridge regression model treating the first
-variable group as the input features and the second variable group as
-the target features.  For example, one regression model used memory
-variables to predict fitness variables, and another regression model
-used fitness variables to predict demographic variables, and so on.
-In total we fit six regression models to each training dataset.  We
-then applied the fitted models to the held-out test dataset and
-computed the root mean squared deviation (RMSD) between the predicted
-and observed values in the target features of the test dataset.  We
-also examined the regression weights assigned to each input feature.
-This yielded, for each regression model (across $N$ bootstrap
-iterations) a distribution of RMSD values and a distribution of
-weights for each input variable.
-
-We constructed a ``null'' distribution by using the same procedure as
-above, but where the columns in the test datasets were randomly
-permuted with each iteration (thereby breaking any meaningful
-predictive information between the training and test data).  We
-assessed the statistical significance ($p$-values) of the observed
-RMSD values by computing the proportions of null RMSD values that were
-less than the observed value.  We also assessed the significance of
-the observed regression weights using $t$-tests to compare the means
-of the observed versus null distributions of weights.
-
-\subsubsection*{Reverse correlation analyses}
-We sought to characterize potential associations between the history
-of participants' fitness-related activities leading up to the time
-they participated in a memory task and their performance on the given
-task.  For each fitness-related variable, we constructed a timeseries
-matrix whose rows corresponded to timepoints (sampled once per day)
-leading up to the day the participant accepted the HIT for our study,
-and whose columns corresponded to different participants.  These
-matrices often contained missing entries, since different
-participants' Fitbit devices tracked fitness-related activities
-differently.  For example, participants whose Fitbit devices lacked
-heart rate sensors would have missing entries for any heart
-rate-related variables.  Or, if a given participant neglected to wear
-their fitness tracker on a particular day, the column corresponding to
-that participant would have missing entries for that day.
-
-In addition to this set of matrices storing timeseries data for each
-fitness-related variable, we also constructed a memory performance
-matrix, $M$, whose rows corresponded to different memory-related
-variables, and whose columns corresponded to different participants.
-For example, one row of the memory performance matrix reflected the
-average proportion of words (across lists) that each participant
-remembered during the immediate free recall test, and so on.
-
-Given a fitness timeseries matrix, $F$, we computed the weighted
-average and weighted standard error of the mean of each row of $F$,
-where the weights were given by a particular memory-related variable
-(row of $M$).  For example, if $F$ contained participants' daily step
-counts, we could use any row of $M$ to compute a weighted average
-across any participants who contributed step count data on each day.
-Choosing a row of $M$ that corresponded to participants' performance
-on the naturalistic recall task would mean that participants who
-performed better on the naturalistic recall task would contribute more
-to the weighted average timeseries of daily step counts.
-Specifically, for each row, $t$, of $F$, we computed the weighted
-average (across the $S$ participants) as:
-\[
-\bar{f}(t) = \sum_{s=1}^S \dot{m}(s) F(t, s),
-\]
-where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row
-of $M$ corresponding to the chosen memory-related variable):
-\[
-  \dot{m} = \frac{m}{\sum_{s=1}^S \hat{m}(s)},
-\]
-where
-\[
-  \hat{m} = \frac{m - \min(m)}{\max(m) - \min(m)}
-\]
-
-We computed the weighted standard error of the mean as:
-\[
-\mathrm{SEM}_m\left(f(t)\right) = \frac{\left| \sum_{s=1}^S \left( F(t, s) -
-    \bar{f}(t)\right) \right|}{\sqrt{S}}.
-\]
-
-When a given row of $F$ was missing data from one or more
-participants, those participants were excluded from the weighted
-average for the corresponding timepoint and the weights (across all
-remaining participants) were re-normalized to sum to 1.  The above
-procedure yielded, for each memory variable, a timeseries of average
-(and standard error of the mean) fitness tracking values leading up to
-the day of the experiment.
-
-\section*{Acknowledgements}
-We acknowledge useful discussions with David Bucci, Emily Glasser,
-Andrew Heusser, Abigail Bartolome, Lorie Loeb, Lucy Owen, and Kirsten
-Ziman.  Our work was supported in part by the Dartmouth Young Minds
-and Brains initiative.  The content is solely the responsibility of
-the authors and does not necessarily represent the official views of
-our supporting organizations.  This paper is dedicated to the memory
-of David Bucci, who helped to inspire the theoretical foundations of
-this work.  Dave served as a mentor and colleague on the project prior
-to his passing.
-
-\section*{Data and code availability}
-All analysis code and data used in the present manuscript may be found
-\href{https://github.com/ContextLab/brainfit-paper}{\underline{here}}.
-
-\section*{Author contributions}
-Concept: J.R.M.  Experiment implementation and data collection: G.M.N.
-Analyses: G.M.N., E.C., P.C.F., and J.R.M.  Writing: J.R.M.
-
-\section*{Competing interests}
-The authors declare no competing interests.
-
 \bibliographystyle{apa}

### 2021-10-07 paper/main.tex
moved detailed behavioral results to supplement; added summary behavioral figures to main text
writing up behavioral results [WIP]

@@
 \affil[2]{Lockheed Martin, Bethesda, MD}
-\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}
+\affil[$\star$]{Address correspondence to
+  jeremy.r.manning@dartmouth.edu}
+
+\newcommand{\frDetail}{S1}
+\newcommand{\natDetail}{S2}
+\newcommand{\vocabDetail}{S3}
+\newcommand{\spatialDetail}{S4}
 
@@
 \section*{Results}
-Before testing our main hypothesis, we first examined the behavioral
-data from each memory task.  We expected that the general trends and
-tendancies in the behavioral data would follow previously reported
-behaviors from similar tasks that had been utilized in prior work.  We
-were also interested in characterizing the variability in task
-performance across participants.  For example, if all participants
-exhibited near-identical behaviors or performance on a given task, we
-would be unable to identify how memory performance varied with
-mental health or exercise.
+Before testing our main hypothesis we examined the behavioral data
+from each of four memory tasks: a random word list learning ``free
+recall'' task; a naturalistic recall task whereby participants watched
+a short video and then recounted the narrative; a foreign language
+``flashcards'' task; and a spatial learning task.  Each of the first
+three tasks (free recall, naturalistic recall, and the flashcards
+task) included both an immediate (short term) memory test and a
+delayed (long term) memory test.  The spatial learning task included
+only an immediate test. Participants in all four tasks exhibited
+general trends and tendancies that have been previously reported in
+prior work.  We were also interested in characterizing the variability
+in task performance across participants.  For example, if all
+participants exhibited near-identical behaviors or performance on a
+given task, we would be unable to identify how memory performance on
+that task varied with mental health or exercise.
+
+When participants engaged in free recall of random word lists, they
+displayed strong primacy and recency effects~\citep{Murd62a} on the
+immediate memory tests (as reflected by improved memory for early and
+late list items; Fig.~\ref{fig:immediate_behavior}a, left and right
+panels).  On the delayed memory test, the recency effect was
+substantially diminished (Fig.~\ref{fig:delayed_behavior}a, left and
+right panels), consistent with myriad previous studies~\citep[for
+review see][]{Kaha12}.  Participants also tended to cluster their
+recalls according to the words' study positions~\citep{Kaha96} on both
+the immediate (Fig.~\ref{fig:immediate_behavior}a, middle panel) and
+delayed (Fig.~\ref{fig:delayed_behavior}a, middle panel) memory tests.
+
+When participants engaged in naturalistic recall by recounting the
+narrative of a short story video, they reliably and accurately
+remembered the major narrative events on both the immediate
+(Fig.~\ref{fig:immediate_behavior}b) and delayed
+(Fig.~\ref{fig:delayed_behavior}b) tests.  This is consistent with
+prior work showing that memory for rich narratives is both detailed
+and accurate~\citep{HeusEtal21, ChenEtal17}.
+
+We expected (and found) that the general trends and
+tendancies in the behavioral data followed previously reported
+behaviors from similar tasks that had been utilized in prior work.
+
+In Figure~\ref{fig:immediate_behavior}, we summarize participants'
+behaviors on four immediate (short term) memory tests: free recall
+(Fig.~\ref{fig:immediate_behavior}a), a naturalistic recall task
+(Fig.~\ref{fig:immediate_behavior}b), a foreign language vocabularly
+learning task (Fig.~\ref{fig:immediate_behavior}c), and a spatial
+learning task (Fig.~\ref{fig:immediate_behavior}d).
 
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/free_recall_behavior}
-\caption{\textbf{Free recall behavioral results.}}
-\label{fig:fr_behavioral}
+\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
+\caption{\textbf{Immediate memory tests.}}
+\label{fig:immediate_behavior}
 \end{figure}
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
-\caption{\textbf{Naturalistic recall behavioral results.}}
-\label{fig:nat_behavioral}
-\end{figure}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
-\caption{\textbf{Foreign language vocabulary learning behavioral results.}}
-\label{fig:vocab_behavioral}
-\end{figure}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
-\caption{\textbf{Spatial learning behavioral results.}}
-\label{fig:spatial_behavioral}
+\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
+\caption{\textbf{Delayed memory tests.}}
+\label{fig:delayed_behavior}
 \end{figure}

### 2021-10-08 paper/main.tex
working on results section (writing up behavioral results) [WIP]

@@
 
-We expected (and found) that the general trends and
-tendancies in the behavioral data followed previously reported
-behaviors from similar tasks that had been utilized in prior work.
-
-In Figure~\ref{fig:immediate_behavior}, we summarize participants'
-behaviors on four immediate (short term) memory tests: free recall
-(Fig.~\ref{fig:immediate_behavior}a), a naturalistic recall task
-(Fig.~\ref{fig:immediate_behavior}b), a foreign language vocabularly
-learning task (Fig.~\ref{fig:immediate_behavior}c), and a spatial
-learning task (Fig.~\ref{fig:immediate_behavior}d).
+Performance on the foreign language flashcards task (immediate:
+Fig.~\ref{fig:immediate_behavior}c; delayed:
+Fig.~\ref{fig:delayed_behavior}c) varied substantially across
+participants, and did not show any clear serial position effects.
+Participants also displayed substantial variation in performance on
+the spatial learning task (Fig.~\ref{fig:immediate_behavior}d).  In
+general, participants reported the shape's positions more accurately
+when there were fewer shapes.  However, both the baseline estimation accuracy and
+the rate of decrease in accuracy as a function of increasing number of
+memorized locations varied substantially across participants.
 

### 2021-10-11 paper/main.tex
moved methods after intro, finished draft of results section up to (before) exploratory analyses

@@
 
-\newcommand{\frDetail}{S1}
-\newcommand{\natDetail}{S2}
-\newcommand{\vocabDetail}{S3}
-\newcommand{\spatialDetail}{S4}
+\newcommand{\devices}{S1}
+\newcommand{\frDetail}{S2}
+\newcommand{\natDetail}{S3}
+\newcommand{\vocabDetail}{S4}
+\newcommand{\spatialDetail}{S5}
+\newcommand{\fitDists}{S6}
+\newcommand{\fitDistgridImmediate}{S7}
+\newcommand{\fitScatterImmediate}{S8}
+\newcommand{\fitDistgridDelayed}{S9}
+\newcommand{\fitScatterDelayed}{S10}
 
@@
 potential associations between memory, mental health, and exercise.
-
-\section*{Results}
-Before testing our main hypothesis we examined the behavioral data
-from each of four memory tasks: a random word list learning ``free
-recall'' task; a naturalistic recall task whereby participants watched
-a short video and then recounted the narrative; a foreign language
-``flashcards'' task; and a spatial learning task.  Each of the first
-three tasks (free recall, naturalistic recall, and the flashcards
-task) included both an immediate (short term) memory test and a
-delayed (long term) memory test.  The spatial learning task included
-only an immediate test. Participants in all four tasks exhibited
-general trends and tendancies that have been previously reported in
-prior work.  We were also interested in characterizing the variability
-in task performance across participants.  For example, if all
-participants exhibited near-identical behaviors or performance on a
-given task, we would be unable to identify how memory performance on
-that task varied with mental health or exercise.
-
-When participants engaged in free recall of random word lists, they
-displayed strong primacy and recency effects~\citep{Murd62a} on the
-immediate memory tests (as reflected by improved memory for early and
-late list items; Fig.~\ref{fig:immediate_behavior}a, left and right
-panels).  On the delayed memory test, the recency effect was
-substantially diminished (Fig.~\ref{fig:delayed_behavior}a, left and
-right panels), consistent with myriad previous studies~\citep[for
-review see][]{Kaha12}.  Participants also tended to cluster their
-recalls according to the words' study positions~\citep{Kaha96} on both
-the immediate (Fig.~\ref{fig:immediate_behavior}a, middle panel) and
-delayed (Fig.~\ref{fig:delayed_behavior}a, middle panel) memory tests.
-
-When participants engaged in naturalistic recall by recounting the
-narrative of a short story video, they reliably and accurately
-remembered the major narrative events on both the immediate
-(Fig.~\ref{fig:immediate_behavior}b) and delayed
-(Fig.~\ref{fig:delayed_behavior}b) tests.  This is consistent with
-prior work showing that memory for rich narratives is both detailed
-and accurate~\citep{HeusEtal21, ChenEtal17}.
-
-Performance on the foreign language flashcards task (immediate:
-Fig.~\ref{fig:immediate_behavior}c; delayed:
-Fig.~\ref{fig:delayed_behavior}c) varied substantially across
-participants, and did not show any clear serial position effects.
-Participants also displayed substantial variation in performance on
-the spatial learning task (Fig.~\ref{fig:immediate_behavior}d).  In
-general, participants reported the shape's positions more accurately
-when there were fewer shapes.  However, both the baseline estimation accuracy and
-the rate of decrease in accuracy as a function of increasing number of
-memorized locations varied substantially across participants.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
-\caption{\textbf{Immediate memory tests.}}
-\label{fig:immediate_behavior}
-\end{figure}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
-\caption{\textbf{Delayed memory tests.}}
-\label{fig:delayed_behavior}
-\end{figure}
-
-\begin{itemize}
-\item characterizing behaviors (color by quartile and continue the
-  color scheme in later figures-- hue reflects task, shading reflects
-  performance.  white outline means immediate, black outline means delayed)
-  \begin{itemize}
-  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
-    recall performance).  
-    Figure~\ref{fig:fr_behavioral}.
-    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
-      movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
-    \item Foreign language flashcards (immediate + delayed):
-      p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
-      \item Spatial learning: mean error by number of shapes (color:
-        intercept and slope of line fit to errors as a function of the number of
-        shapes).  Figure~\ref{fig:spatial_behavioral}.
-      \end{itemize}
-    \item Fitness info (break down by task performance, potentially
-      separately for each task); also separate out recent (raw) and
-      recent versus baseline -- color using same color scheme as
-      behavior figure
-      \begin{itemize}
-      \item activity (steps, zone minutes, floors/elevation)
-      \item resting heart rate
-        \item sleep
-        \end{itemize}
-  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
-          tasks.  Diagonal: histogram of performance metric for that
-          task.  Above-diagonal entries: compare performance across
-          tasks (by subject).  Below-diagonal entries: empty?
-          density/2d histograms?
-    \begin{itemize}
-    \item Memory-memory
-    \item fitness-fitness
-    \item survey-survey
-    \item (fitness + survey)-memory
-    \end{itemize}
-  \item predictive analysis (regressions)
-    \begin{itemize}
-    \item Predict memory performance on held-out task from other tasks
-    \item Predict memory performance on each task using fitness data
-      \item Predict memory performance on each task using survey data
-      \end{itemize}
-    \item Reverse correlations: look at recent changes versus baseline
-      trends (color using same scheme as behavior figures).  Possibly 
-      \begin{itemize}
-      \item Fitness profile that predicts performance on each task (barplots + timelines)
-      \item Fitness profile for each survey demographic (barplots + timelines)
-        \begin{itemize}
-          \item Select out mental health demographics (based on meds, stress levels)
-          \end{itemize}
-        \end{itemize}
-  \end{itemize}
-
-  \section*{Discussion}
-  \begin{itemize}
-  \item summarize key findings
-  \item correlation versus causation
-         \item what can vs.
-can't we know?
-we can identify correlations, but not causal direction-- e.g.
-we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.
-that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
-  \item related work (exercise/memory, exercise/mental health), what this study adds
-    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
-    \end{itemize}
 
@@
 accounts varied in scope and duration according to which device the
-participant owned (Fig.~\ref{fig:devices}), how often the participant
+participant owned (Fig.~\devices), how often the participant
 wore (and/or synced) their tracking device, and how long they had
@@
 related measures.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/devices}
-\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
-  participants whose fitness tracking data came from each model of
-  Fitbit device.  ``MobileTrack'' refers to participants who used
-  smartphone accelerometer information to track their activity via the
-  Fitbit smartphone app.
-  ``Unknown''  denotes participants whose device information was not
-  available from their available Fitbit data.}
-\label{fig:devices}
-\end{figure}
 
@@
 
+\section*{Results}
+Before testing our main hypothesis we examined the behavioral data
+from each of four memory tasks: a random word list learning ``free
+recall'' task; a naturalistic recall task whereby participants watched
+a short video and then recounted the narrative; a foreign language
+``flashcards'' task; and a spatial learning task.  Each of the first
+three tasks (free recall, naturalistic recall, and the flashcards
+task) included both an immediate (short term) memory test and a
+delayed (long term) memory test.  The spatial learning task included
+only an immediate test. Participants in all four tasks exhibited
+general trends and tendancies that have been previously reported in
+prior work.  We were also interested in characterizing the variability
+in task performance across participants.  For example, if all
+participants exhibited near-identical behaviors or performance on a
+given task, we would be unable to identify how memory performance on
+that task varied with mental health or exercise.
+
+When participants engaged in free recall of random word lists, they
+displayed strong primacy and recency effects~\citep{Murd62a} on the
+immediate memory tests (as reflected by improved memory for early and
+late list items; Fig.~\ref{fig:immediate_behavior}a, left and right
+panels).  On the delayed memory test, the recency effect was
+substantially diminished (Fig.~\ref{fig:delayed_behavior}a, left and
+right panels), consistent with myriad previous studies~\citep[for
+review see][]{Kaha12}.  Participants also tended to cluster their
+recalls according to the words' study positions~\citep{Kaha96} on both
+the immediate (Fig.~\ref{fig:immediate_behavior}a, middle panel) and
+delayed (Fig.~\ref{fig:delayed_behavior}a, middle panel) memory tests.
+
+When participants engaged in naturalistic recall by recounting the
+narrative of a short story video, they reliably and accurately
+remembered the major narrative events on both the immediate
+(Fig.~\ref{fig:immediate_behavior}b) and delayed
+(Fig.~\ref{fig:delayed_behavior}b) tests.  This is consistent with
+prior work showing that memory for rich narratives is both detailed
+and accurate~\citep{HeusEtal21, ChenEtal17}.
+
+Performance on the foreign language flashcards task (immediate:
+Fig.~\ref{fig:immediate_behavior}c; delayed:
+Fig.~\ref{fig:delayed_behavior}c) varied substantially across
+participants, and did not show any clear serial position effects.
+Participants also displayed substantial variation in performance on
+the spatial learning task (Fig.~\ref{fig:immediate_behavior}d).  In
+general, participants reported the shape's positions more accurately
+when there were fewer shapes.  However, both the baseline estimation accuracy and
+the rate of decrease in accuracy as a function of increasing number of
+memorized locations varied substantially across participants.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
+\caption{\textbf{Immediate memory tests.}  \textbf{a. Free recall.}
+  Left: probability of recalling each word first as a function of its
+  presentation position.  Middle: probability of transitioning between
+successively recalling the word presented at position $i$, followed by
+word presented at position $i + \mathrm{Lag}$.  Right: probability of
+recalling each word as a function of its presentation position.  See
+Figure~\frDetail~for additional details.
+\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5~min video
+clip; each dot reflects a narrative event (red denotes early events
+and blue denotes later events).  Bottom: 2D embedding of the averaged
+transcripts of participants' recountings of the narrative (dots: same
+format as top panel).  The arrows denote the average trajectory
+directions through the corresponding region of text embedding space,
+for any participants whose recountings passed through that region.
+Blue arrows denote statistically reliable agreement across
+participants ($p < 0.05$, corrected).  See Figure~\natDetail~for
+additional details.  \textbf{c. Foreign language
+  flashcards.} Each bar denotes the average proportion of correctly
+recalled Gaelic-English word pairs from early (first 3), late (last
+3), or all (i.e., all 10) study positions.  See
+Figure~\vocabDetail~for additional details.\textbf{d. Spatial
+  learning.}  Average estimation error in shape locations as a
+function of the number of shapes.  See Figure~\spatialDetail~for
+additional details.  All panels: error bars and error
+ribbons denote bootstrap-estimated 95\% confidence intervals.  Shading
+(saturation) denotes results for different subsets of participants
+assigned based on their task performance (Figs.~\frDetail,
+\natDetail, \vocabDetail, and \spatialDetail~provide information about
+which performance metrics and values the shading reflects; in general
+more saturated colors denote participants who performed better on the
+given task.)  In Panel d, participants are grouped in two ways; in the
+left panel, participants are grouped according to the $y$-intercepts of regression lines (estimation error as a
+function of the number of shapes); in the right panel, participants
+are grouped according to the slopes of the same regression lines.}
+\label{fig:immediate_behavior}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
+\caption{\textbf{Delayed memory tests.}  \textbf{a.  Free recall.}
+  These panels are in the same format as
+  Figure~\ref{fig:immediate_behavior}a, but they reflect performance
+  on the delayed free recall task.  For additional details see
+  Figure~\frDetail.  \textbf{b. Naturalistic recall.}  These panels
+  are in the same format as Figure~\ref{fig:immediate_behavior}b, but
+  the right panel reflects performance on the delayed naturalistic
+  recall task.  For additional details see Figure~\natDetail.
+  \textbf{c. Foreign language flashcards.} This panel is in the same
+  format as Figure~\ref{fig:immediate_behavior}c, but it reflects
+  performance on the delayed flashcards test.  For additional details
+  see Figure~\vocabDetail.}
+\label{fig:delayed_behavior}
+\end{figure}
+
+In addition to observing substantial across-participant variability in
+memory performance, we also observed substantial variability in
+participants' fitness and activity metrics
+(Fig.~\ref{fig:fitness_summary}).  We examined recent measurements,
+averaged over the week prior to testing
+(Fig.~\ref{fig:fitness_summary}a), baselined measurements (average
+over the prior week, divided by the average over the preceding 30 day;
+Fig.~\ref{fig:fitness_summary}b), along with more gradually varying
+measures that tended to remain relatively static over timescales of
+weeks to months (Fig.~\ref{fig:fitness_summary}c).
+Figure~\fitDists~displays across-participant
+distributions for a broad selection of these measures, and Figures~\fitDistgridImmediate,
+\fitScatterImmediate, \fitDistgridDelayed, and \fitScatterDelayed~show
+different participants' fitness metrics, broken down by their
+performance on different memory tasks.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/fitness_distributions_summary}
+\caption{\textbf{Fitness measures.}  \textbf{a. Recent measures.}
+  Resting heart rate (HR) and daily step counts, averaged over the
+  week prior to testing.  \textbf{Baseline-normalized measures.}
+  Resting heart rate and daily step counts averaged over the week
+  prior to testing, divided by the average resting heart rate and step
+counts averaged over the preceding month.  \textbf{Static measures.}
+Body mass index (BMI), body fat percentage, and weight (in kg).  For
+more information see Figures~\fitDists, \fitDistgridImmediate,
+\fitScatterImmediate, \fitDistgridDelayed, and \fitScatterDelayed.}
+\label{fig:fitness_summary}
+\end{figure}
+
+\begin{itemize}
+% \item characterizing behaviors (color by quartile and continue the
+%   color scheme in later figures-- hue reflects task, shading reflects
+%   performance.  white outline means immediate, black outline means delayed)
+%   \begin{itemize}
+%   \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
+%     recall performance).  
+%     Figure~\ref{fig:fr_behavioral}.
+%     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
+%       movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
+%     \item Foreign language flashcards (immediate + delayed):
+%       p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
+%       \item Spatial learning: mean error by number of shapes (color:
+%         intercept and slope of line fit to errors as a function of the number of
+%         shapes).  Figure~\ref{fig:spatial_behavioral}.
+%       \end{itemize}
+%     \item Fitness info (break down by task performance, potentially
+%       separately for each task); also separate out recent (raw) and
+%       recent versus baseline -- color using same color scheme as
+%       behavior figure
+%       \begin{itemize}
+%       \item activity (steps, zone minutes, floors/elevation)
+%       \item resting heart rate
+%         \item sleep
+%         \end{itemize}
+  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
+          tasks.  Diagonal: histogram of performance metric for that
+          task.  Above-diagonal entries: compare performance across
+          tasks (by subject).  Below-diagonal entries: empty?
+          density/2d histograms?
+    \begin{itemize}
+    \item Memory-memory
+    \item fitness-fitness
+    \item survey-survey
+    \item (fitness + survey)-memory
+    \end{itemize}
+  \item predictive analysis (regressions)
+    \begin{itemize}
+    \item Predict memory performance on held-out task from other tasks
+    \item Predict memory performance on each task using fitness data
+      \item Predict memory performance on each task using survey data
+      \end{itemize}
+    \item Reverse correlations: look at recent changes versus baseline
+      trends (color using same scheme as behavior figures).  Possibly 
+      \begin{itemize}
+      \item Fitness profile that predicts performance on each task (barplots + timelines)
+      \item Fitness profile for each survey demographic (barplots + timelines)
+        \begin{itemize}
+          \item Select out mental health demographics (based on meds, stress levels)
+          \end{itemize}
+        \end{itemize}
+  \end{itemize}
+
+  \section*{Discussion}
+  \begin{itemize}
+  \item summarize key findings
+  \item correlation versus causation
+         \item what can vs.
+can't we know?
+we can identify correlations, but not causal direction-- e.g.
+we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.
+that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
+  \item related work (exercise/memory, exercise/mental health), what this study adds
+    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
+    \end{itemize}
+
 \section*{Acknowledgements}

### 2021-10-11 paper/supplement.tex
writing up behavioral results [WIP]
moved methods after intro, finished draft of results section up to (before) exploratory analyses

@@
 
-\title{\textit{Supplementary materials for} Fitness tracking reveals task-specific associations between
+\title{\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between
   memory, mental health, and exercise}
@@
 \maketitle
+
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.6\textwidth]{figs/devices}
+\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
+  participants whose fitness tracking data came from each model of
+  Fitbit device.  ``MobileTrack'' refers to participants who used
+  smartphone accelerometer information to track their activity via the
+  Fitbit smartphone app.
+  ``Unknown''  denotes participants whose device information was not
+  available from their available Fitbit data.}
+\label{fig:devices}
+\end{figure}
 
@@
 
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_distributions}
+\caption{\textbf{Distributions of fitness measures.}}
+\label{fig:fitness_dists}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_dists_immediate}
+\caption{\textbf{Distributions of fitness measures, broken down
+    by immediate task performance.}}
+\label{fig:fitness_dists_immediate}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
+\caption{\textbf{Scatterplots of fitness measures versus
+    immediate task performance measures.}}
+\label{fig:fitness_scatters_immediate}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_dists_delayed}
+\caption{\textbf{Distributions of fitness measures, broken down
+    by delayed task performance.}}
+\label{fig:fitness_dists_delayed}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
+\caption{\textbf{Scatterplots of fitness measures versus
+    delayed task performance measures.}}
+\label{fig:fitness_scatters_delayed}
+\end{figure}
+
 \bibliographystyle{apa}

### 2021-10-13 paper/main.tex
added exploratory correlation analysis

@@
 \newcommand{\fitScatterDelayed}{S10}
+\newcommand{\behBehCorr}{S11}
+\newcommand{\fitFitCorr}{S12}
+\newcommand{\demDemCorr}{S13}
+\newcommand{\allCorr}{S14}
 
@@
 When participants were sampled multiple times in a given iteration, as
-was often the case, this matrix contained duplicate rows.  We used a
-round-robin imputation procedure to estimate the values of any missing
-features~\citep{Buck60}.  Next, we computed the Pearson's correlation
+was often the case, this matrix contained duplicate rows.  Next, we computed the Pearson's correlation
 between each pair of columns.  This yielded, for each pair of columns,
 a distribution of $N$ bootstrapped correlation coefficients.  If fewer
-than $95\%$ of the coefficients for a given pair of columns had the
+than $97.5\%$ of the coefficients for a given pair of columns had the
 same sign, we excluded the pair from further analysis and considered
 the expected correlation between those columns to be undefined.  If
-$\geq 95\%$ of the coefficients for a given pair of columns had the
-same sign, we computed the expected correlation coefficient as:
+$\geq 97.5\%$ of the coefficients for a given pair of columns had the
+same sign (corresponding to a bootstrap-estimated two-tailed $p$
+threshold of 0.05), we computed the expected correlation coefficient as:
 \[
@@
 data matrices whose rows reflected sampled participants and whose
-columns reflected different measured variables.
+columns reflected different measured variables.  We used a
+round-robin imputation procedure to estimate the values of any missing
+features~\citep{Buck60}.  This imputation procedure was applied
+independently for input features and output features to prevent data contamination.
 
@@
 above, but where the columns in the test datasets were randomly
-permuted with each iteration (thereby breaking any meaningful
+permuted with each of $M = 1000$ iterations (thereby breaking any meaningful
 predictive information between the training and test data).  We
@@
 
+We wondered about potential links between the different aspects of
+participants' data.  For example, if people who exercised in a
+particular way also tended to perform better on a given memory task,
+this could suggest that either (a) some property intrinsic to participants who
+exercised in a particular way might also affect their memory
+performance on the given task, and/or (b) particular exercise behaviors
+could have a causal impact on memory performance.  We carried out an
+exploratory analysis whereby we used a bootstrap-based approach (see
+\textit{Exploratory correlation analyses}) to
+identify reliable correlations between different aspects of memory
+performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
+attributes (Fig.~\demDemCorr), and correlations between memory
+performance, fitness information, and demographic attributes
+(Fig.~\allCorr).  Several patterns emerged.  First, we found that
+participants' performance on the (within-task) immediate versus delayed memory tests
+from the free recall, naturalistic recall, and foreign language
+flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.05$,
+bootstrap corrected).  This suggests that, within each of these tasks,
+similar processes or constraints may influence both short term and
+long term information retrieval.  We also found reliable across-task correlations
+between participants' (immediate and delayed) performance on the free
+recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.05$,
+bootstrap corrected).
+
+A large number of fitness-related measures displayed reliable
+correlations (for a complete report, see Fig.~\fitFitCorr).  For
+example, body mass index (BMI) and weight were correlated
+($r = 0.91, p < 0.05$, bootstrap corrected).  Resting heart rate over
+the prior week was negatively correlated with recent high-intensity
+activity levels ($r = 0.39, p < 0.05$, bootstrap corrected).
+Participants' peak heart rate (averaged over the prior week) were also
+negative correlated with recent decreases in step counts and daily
+elevation gains ($r\mathrm{s} < -0.27, p\mathrm{s} < 0.05$, boostrap
+corrected), where recent changes were defined as the average values
+over the seven days leading up to the test day divided by the average
+values over the preceding 30 days.  Although several demographic
+attributes (Fig.~\demDemCorr) displayed trivial correlations (e.g.,
+participants identifying as male never reported identifying as female,
+and so on), we also observed a negative correlation between reported
+stress and alertness ($r = -0.44, p < 0.05$, bootstrap corrected), and
+positive correlations between the reported task difficulties for all
+tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.05$, bootstrap corrected).
+
+We also found reliable correlations between participants' fitness and
+demographic measures and their behaviors in different tasks
+(for a complete report, see Fig.~\allCorr).  For example, recent
+low-intensity (``fat burn'') cardiovascular activity was positively
+correlated with immediate
+($r = 0.44, p < 0.05$, bootstrap corrected) and delayed ($r = 0.37, p
+< 0.05$, bootstrap corrected) recall on the naturalistic memory task.
+Moderate intensity (``cardio'') cardiovascular activitiy was
+positively correlated with immediate naturalistic recall ($r = 0.47, p
+< 0.05$, bootstrap corrected) and immediate recall on the foreign
+language flashcards task ($r = 0.43, p < 0.05$, bootstrap corrected).
+Recent low-intensity (``out-of-range'') cardiovascular activity was
+negatively correlated with spatial memory performance ($r = -0.31, p <
+0.05$, bootstrap corrected) whereas recent high-intensity (``peak'')
+cardiovascular activity was positively correlated with spatial memory
+performance ($r = 0.34, p < 0.05$, bootstrap corrected).  Recent
+increases in high-intensity cardiovascular activity (more activity
+over the past 7 days than during the preceding 30 days) also predicted
+spatial memory performance ($r = 0.41, p < 0.05$, bootstrap
+corrected).  Coffee consumption was (slightly) positively correlated with
+immediate free recall performance ($r = 0.17, p < 0.05$, bootstrap
+corrected) and (slightly) negatively correlated with immediate
+naturalistic recall performance ($r = -0.16, p < 0.05$, bootstrap
+corrected).
+
 \begin{itemize}
@@
 %         \end{itemize}
-  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
-          tasks.  Diagonal: histogram of performance metric for that
-          task.  Above-diagonal entries: compare performance across
-          tasks (by subject).  Below-diagonal entries: empty?
-          density/2d histograms?
-    \begin{itemize}
-    \item Memory-memory
-    \item fitness-fitness
-    \item survey-survey
-    \item (fitness + survey)-memory
-    \end{itemize}
+  % \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
+  %         tasks.  Diagonal: histogram of performance metric for that
+  %         task.  Above-diagonal entries: compare performance across
+  %         tasks (by subject).  Below-diagonal entries: empty?
+  %         density/2d histograms?
+  %   \begin{itemize}
+  %   \item Memory-memory
+  %   \item fitness-fitness
+  %   \item survey-survey
+  %   \item (fitness + survey)-memory
+  %   \end{itemize}
   \item predictive analysis (regressions)

### 2021-10-13 paper/supplement.tex
updated trajectories, added sleep stats
added exploratory correlation analysis

@@
 \usepackage{authblk}
+\usepackage{pdflscape}
+\usepackage{rotating}
 
@@
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:fr_behavioral}
-\end{figure}
+\end{sidewaysfigure}
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:nat_behavioral}
-\end{figure}
+\end{sidewaysfigure}
 
@@
 \label{fig:fitness_dists}
-\end{figure}
+\end{sidewaysfigure}
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:fitness_dists_immediate}
-\end{figure}
+\end{sidewaysfigure}
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:fitness_scatters_immediate}
-\end{figure}
+\end{sidewaysfigure}
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:fitness_dists_delayed}
-\end{figure}
+\end{sidewaysfigure}
 
-\begin{figure}[p]
+\begin{sidewaysfigure}[p]
 \centering
@@
 \label{fig:fitness_scatters_delayed}
+\end{sidewaysfigure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=0.4\textwidth]{figs/behavior_behavior_correlations}
+\caption{\textbf{Bootstrap-estimated reliable correlations between
+    behavioral measures.}}
+\label{fig:behavioral_corrs}
 \end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/fitness_fitness_correlations}
+\caption{\textbf{Bootstrap-estimated reliable correlations between
+    fitness measures.}}
+\label{fig:fitness_corrs}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/survey_survey_correlations}
+\caption{\textbf{Bootstrap-estimated reliable correlations between
+    demographic measures.}}
+\label{fig:survey_corrs}
+\end{figure}
+
+\begin{sidewaysfigure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/behavior_fitness+survey_correlations}
+\caption{\textbf{Bootstrap-estimated reliable correlations between
+    behavioral measures and fitness or demographic measures.}}
+\label{fig:survey_corrs}
+\end{sidewaysfigure}
 

### 2021-10-16 paper/main.tex
updated correlation figures and stats using 10000 bootstrap iterations

--- 2021-10-11 paper/main.tex
@@
 data matrices whose rows reflected sampled participants and whose
-columns reflected different measured variables.
+columns reflected different measured variables.  We used a round-robin
+imputation procedure to estimate the values of any missing
+features~\citep{Buck60}.  We applied this imputation procedure
+independently for each bootstrapped data matrix to prevent data
+contamination across iterations.
 
+Next, we fit a series of ridge regression models to the training data.
 We grouped variables according to whether they were memory-related,
-fitness-related, or demographic-related.  For each bootstrap
-iteration, we divided the rows of that iterations data matrix into
+fitness-related, or demographic-related.  
+We used variables from each group to predict held-out variables from
+the same group-- e.g., using performance on all but one task to
+predict performance on the held-out task.  We also examined
+predictions across groups of variables-- e.g., using fitness and
+demographic variables to predict memory-related variables.
+
+For each set of predictions, we used a bootstrap procedure to estimate
+the stability and reliability of those predictions.  For each bootstrap
+iteration, we divided the rows of that iteration's data matrix into
 training and test sets.  The assignments of rows to these two sets was
@@
 
-Next, we fit a series of ridge regression models to the training data.
-Specifically, for each pairing of memory, fitness, and demographic
-variables, we fit a single ridge regression model treating the first
-variable group as the input features and the second variable group as
-the target features.  For example, one regression model used memory
-variables to predict fitness variables, and another regression model
-used fitness variables to predict demographic variables, and so on.
-In total we fit six regression models to each training dataset.  We
-then applied the fitted models to the held-out test dataset and
-computed the root mean squared deviation (RMSD) between the predicted
-and observed values in the target features of the test dataset.  We
-also examined the regression weights assigned to each input feature.
-This yielded, for each regression model (across $N$ bootstrap
-iterations) a distribution of RMSD values and a distribution of
-weights for each input variable.
-
-We constructed a ``null'' distribution by using the same procedure as
-above, but where the columns in the test datasets were randomly
-permuted with each iteration (thereby breaking any meaningful
-predictive information between the training and test data).  We
-assessed the statistical significance ($p$-values) of the observed
-RMSD values by computing the proportions of null RMSD values that were
-less than the observed value.  We also assessed the significance of
-the observed regression weights using $t$-tests to compare the means
-of the observed versus null distributions of weights.
+For each bootstrap iteration, we computed the root mean squared
+deviation (RMSD) between the predicted and observed values in the
+target features of the test dataset.  We defined this as the
+\textit{observed} RMSD for that bootstrap iteration.  We also
+estimated a null distribution of RMSD values by re-fitting each
+iteration's data after randomly permuting the rows of the input data
+matrix 
+(thereby breaking any
+meaningful associations between the input and output features).  Taken
+together, this yielded a set of 1000 observed RMSD values and 1000
+null RMSD values.  We assessed the statistical significance
+($p$-values) of the observed RMSD values by computing the proportions
+of null RMSD values that were less than the observed value.  We also
+assessed the significance of the observed regression weights using
+$t$-tests to compare the means of the observed versus null
+distributions of weights, separately for each input and output feature.
 
@@
 
+We wondered about potential links between the different aspects of
+participants' data.  For example, if people who exercised in a
+particular way also tended to perform better on a given memory task,
+this could suggest that either (a) some property intrinsic to participants who
+exercised in a particular way might also affect their memory
+performance on the given task, and/or (b) particular exercise behaviors
+could have a causal impact on memory performance.  We carried out an
+exploratory analysis whereby we used a bootstrap-based approach (see
+\textit{Exploratory correlation analyses}) to
+identify reliable correlations between different aspects of memory
+performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
+attributes (Fig.~\demDemCorr), and correlations between memory
+performance, fitness information, and demographic attributes
+(Fig.~\allCorr).  Several patterns emerged.  First, we found that
+participants' performance on the (within-task) immediate versus delayed memory tests
+from the free recall, naturalistic recall, and foreign language
+flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$,
+bootstrap corrected).  This suggests that, within each of these tasks,
+similar processes or constraints may influence both short term and
+long term information retrieval.  We also found reliable across-task correlations
+between participants' (immediate and delayed) performance on the free
+recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$,
+bootstrap corrected).
+
+A large number of fitness-related measures displayed reliable
+correlations (for a complete report, see Fig.~\fitFitCorr).  For
+example, body mass index (BMI) and weight were correlated
+($r = 0.91, p < 0.0001$, bootstrap corrected).  Resting heart rate over
+the prior week was negatively correlated with recent
+low-to-moderate-intensity (``fat burn'') cardiovascular
+activity levels ($r = 0.70, p = 0.0004$, bootstrap corrected).
+Participants' peak heart rate (averaged over the prior week) were also
+negatively correlated with recent increases in step counts and daily
+elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, boostrap
+corrected), where recent changes were defined as the average values
+over the seven days leading up to the test day divided by the average
+values over the preceding 30 days.  Although several demographic
+attributes (Fig.~\demDemCorr) displayed trivial correlations (e.g.,
+participants identifying as male never reported identifying as female,
+and so on), we also observed a negative correlation between reported
+stress and alertness ($r = -0.44, p < 0.0001$, bootstrap corrected), and
+positive correlations between the reported clarity of the instructions for all
+tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.02$, bootstrap corrected).
+
+We also found reliable correlations between participants' fitness and
+demographic measures and their behaviors in different tasks
+(for a complete report, see Fig.~\allCorr).  For example, recent
+low-to-moderate-intensity (``fat burn'') 
+cardiovascular activity was positively
+correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
+0.38, p = 0.029$) recall on the naturalistic
+memory task.  Recent increases in moderate-intensity (``cardio'')
+activity over the prior 7 days (relative to the preceding 30 days) was
+also positively correlated with immediate naturalistic recall ($r =
+0.48, p = 0.003$) and immediate recall on the foreign language
+flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
+(``peak'') activity was positively correlated with performance on the
+spatial learning task ($r = 0.34, p < 0.0001$), as were recent increases
+in high-intensity activity (prior 7 days versus preceding 30 days; $r
+= 0.41, p = 0.01$).
+
 \begin{itemize}

### 2021-10-16 paper/main.tex
updated bootstrap methods

@@
 between different memory-related, fitness-related, and
-demographic-related variables.  For each of $N = 1000$ iterations, we
+demographic-related variables.  For each of $N = 10,000$ iterations, we
 selected (with replacement) a sample of 113 participants to include.
@@
 We used the same bootstrap procedure described above (used in our
-exploratory correlation analyses) to generate $N = 1000$ bootstrapped
+exploratory correlation analyses) to generate $N = 10,000$ bootstrapped
 data matrices whose rows reflected sampled participants and whose
@@
 We grouped variables according to whether they were memory-related,
-fitness-related, or demographic-related.  
-We used variables from each group to predict held-out variables from
-the same group-- e.g., using performance on all but one task to
-predict performance on the held-out task.  We also examined
-predictions across groups of variables-- e.g., using fitness and
-demographic variables to predict memory-related variables.
+fitness-related, or demographic-related.  We examined whether
+fitness-related and demographic-related features could be used to predict
+performance on one or more of the memory tasks.
 
@@
 meaningful associations between the input and output features).  Taken
-together, this yielded a set of 1000 observed RMSD values and 1000
+together, this yielded a set of $10,000$ observed RMSD values and $10,000$
 null RMSD values.  We assessed the statistical significance
@@
 $t$-tests to compare the means of the observed versus null
-distributions of weights, separately for each input and output feature.
+distributions of weights, for each combination of features.
 

### 2021-10-20 paper/main.tex
finished draft of results section, added timecourse figs to supplement

@@
 \newcommand{\allCorr}{S14}
+\newcommand{\activityTimecourse}{S15}
+\newcommand{\cardioTimecourse}{S16}
+\newcommand{\sleepTimecourse}{S17}
+\newcommand{\activityTimecourseMH}{S18}
+\newcommand{\cardioTimecourseMH}{S19}
+\newcommand{\sleepTimecourseMH}{S20}
 
@@
 
-\subsubsection*{Regression-based prediction analyses}
-Following our exploratory correlation analyses, we used an analogous
-bootstrap procedure to identify subsets of memory-related,
-fitness-related, and demographic-related variables that predicted
-(non-overlapping) subsets of other variables.  For example, we tested
-whether a combination of fitness-related variables could predict a
-combination of memory-related variables, and so on.
-
-We used the same bootstrap procedure described above (used in our
-exploratory correlation analyses) to generate $N = 10,000$ bootstrapped
-data matrices whose rows reflected sampled participants and whose
-columns reflected different measured variables.  We used a round-robin
-imputation procedure to estimate the values of any missing
-features~\citep{Buck60}.  We applied this imputation procedure
-independently for each bootstrapped data matrix to prevent data
-contamination across iterations.
-
-Next, we fit a series of ridge regression models to the training data.
-We grouped variables according to whether they were memory-related,
-fitness-related, or demographic-related.  We examined whether
-fitness-related and demographic-related features could be used to predict
-performance on one or more of the memory tasks.
-
-For each set of predictions, we used a bootstrap procedure to estimate
-the stability and reliability of those predictions.  For each bootstrap
-iteration, we divided the rows of that iteration's data matrix into
-training and test sets.  The assignments of rows to these two sets was
-random, subject to the constraint that any duplicated rows in the data
-matrix (i.e., reflecting a single participant who had been sampled
-multiple times) was always assigned to either the training \textit{or}
-the test set--i.e., duplicated rows could not appear in both the
-training and the test sets.  The training sets always comprised 75\%
-of the data, and the tests sets comprised the remaining 25\% of the
-data.
-
-For each bootstrap iteration, we computed the root mean squared
-deviation (RMSD) between the predicted and observed values in the
-target features of the test dataset.  We defined this as the
-\textit{observed} RMSD for that bootstrap iteration.  We also
-estimated a null distribution of RMSD values by re-fitting each
-iteration's data after randomly permuting the rows of the input data
-matrix 
-(thereby breaking any
-meaningful associations between the input and output features).  Taken
-together, this yielded a set of $10,000$ observed RMSD values and $10,000$
-null RMSD values.  We assessed the statistical significance
-($p$-values) of the observed RMSD values by computing the proportions
-of null RMSD values that were less than the observed value.  We also
-assessed the significance of the observed regression weights using
-$t$-tests to compare the means of the observed versus null
-distributions of weights, for each combination of features.
-
 \subsubsection*{Reverse correlation analyses}
@@
 their fitness tracker on a particular day, the column corresponding to
-that participant would have missing entries for that day.
+that participant would have missing entries for that day.  To create
+stable estimates, we smoothed the timeseries of each fitness measure
+using a sliding window of 1 week.  In other words, for each fitness
+measure, we replaced the ``observed
+value'' for each day with the average values of that measure (when
+available) over the 7 day interval ending on the given day.
 
@@
 \[
-  \hat{m} = \frac{m - \min(m)}{\max(m) - \min(m)}
+  \hat{m} = (1 - \epsilon)\frac{m - \min(m)}{\max(m) - \min(m)} + \epsilon.
 \]
+Here, $\epsilon$ provides a lower bound on the influence of the
+lowest-weighted participant's data.  We defined $\epsilon = 0.001$,
+ensuring that the lowest-weighted participant had relatively low (but
+non-zero) influence.
 
@@
 from the free recall, naturalistic recall, and foreign language
-flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$,
-bootstrap corrected).  This suggests that, within each of these tasks,
+flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$).  This suggests that, within each of these tasks,
 similar processes or constraints may influence both short term and
@@
 between participants' (immediate and delayed) performance on the free
-recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$,
-bootstrap corrected).
+recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$).
 
@@
 example, body mass index (BMI) and weight were correlated
-($r = 0.91, p < 0.0001$, bootstrap corrected).  Resting heart rate over
+($r = 0.91, p < 0.0001$).  Resting heart rate over
 the prior week was negatively correlated with recent
 low-to-moderate-intensity (``fat burn'') cardiovascular
-activity levels ($r = 0.70, p = 0.0004$, bootstrap corrected).
+activity levels ($r = 0.70, p = 0.0004$).
 Participants' peak heart rate (averaged over the prior week) were also
@@
 and so on), we also observed a negative correlation between reported
-stress and alertness ($r = -0.44, p < 0.0001$, bootstrap corrected), and
+stress and alertness ($r = -0.44, p < 0.0001$), and
 positive correlations between the reported clarity of the instructions for all
-tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.02$, bootstrap corrected).
+tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.02$).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.8\textwidth]{figs/corr_MH}
+\caption{\textbf{Memory performance differs according to mental health
+    measures.}  The reported values in the table reflect correlations
+  between each behavioral measure and mental health measure.
+  Only statistically reliable correlations ($p < 0.05$, corrected) are displayed. 
+  We used participants' mean recall accuracy to characterize
+  performance on the free recall and
+  foreign language flashcards tasks, and mean precision to
+  characterize performance on the naturalistic recall tasks.  We
+  characterized performance on the spatial learning task using the
+  (inverted and normalized)
+  intercepts and slopes of linear regressions on mean estimation
+  errors as a function of the number of studied shapes (also see
+  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},
+  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  Typical
+  and current stress levels were measured by self report.  Mental
+  health information was inferred using each participants' list of
+  self-reported medications.}
+\label{fig:mh_corr}
+\end{figure}
 
@@
 in high-intensity activity (prior 7 days versus preceding 30 days; $r
-= 0.41, p = 0.01$).
+= 0.41, p = 0.01$).  Mental health indicators, such as self-reported
+stress levels and medications were also associated with differences in
+memory (Figs.~\ref{fig:mh_corr}, \allCorr).  For example, self-reported stress levels at the time of test
+were negatively correlated with performance on the delayed memory test
+for the foreign language flashcards task ($r = -0.29, p = 0.038$),
+whereas participants who were medicated for anxiety and depression
+tended to perform slightly (but reliably) \textit{better} on the immediate memory test for the
+foreign language flashcards task ($r = 0.11, p < 0.0001$).
 
-\begin{itemize}
-% \item characterizing behaviors (color by quartile and continue the
-%   color scheme in later figures-- hue reflects task, shading reflects
-%   performance.  white outline means immediate, black outline means delayed)
-%   \begin{itemize}
-%   \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
-%     recall performance).  
-%     Figure~\ref{fig:fr_behavioral}.
-%     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
-%       movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
-%     \item Foreign language flashcards (immediate + delayed):
-%       p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
-%       \item Spatial learning: mean error by number of shapes (color:
-%         intercept and slope of line fit to errors as a function of the number of
-%         shapes).  Figure~\ref{fig:spatial_behavioral}.
-%       \end{itemize}
-%     \item Fitness info (break down by task performance, potentially
-%       separately for each task); also separate out recent (raw) and
-%       recent versus baseline -- color using same color scheme as
-%       behavior figure
-%       \begin{itemize}
-%       \item activity (steps, zone minutes, floors/elevation)
-%       \item resting heart rate
-%         \item sleep
-%         \end{itemize}
-  % \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
-  %         tasks.  Diagonal: histogram of performance metric for that
-  %         task.  Above-diagonal entries: compare performance across
-  %         tasks (by subject).  Below-diagonal entries: empty?
-  %         density/2d histograms?
-  %   \begin{itemize}
-  %   \item Memory-memory
-  %   \item fitness-fitness
-  %   \item survey-survey
-  %   \item (fitness + survey)-memory
-  %   \end{itemize}
-  \item predictive analysis (regressions)
-    \begin{itemize}
-    \item Predict memory performance on held-out task from other tasks
-    \item Predict memory performance on each task using fitness data
-      \item Predict memory performance on each task using survey data
-      \end{itemize}
-    \item Reverse correlations: look at recent changes versus baseline
-      trends (color using same scheme as behavior figures).  Possibly 
-      \begin{itemize}
-      \item Fitness profile that predicts performance on each task (barplots + timelines)
-      \item Fitness profile for each survey demographic (barplots + timelines)
-        \begin{itemize}
-          \item Select out mental health demographics (based on meds, stress levels)
-          \end{itemize}
-        \end{itemize}
-  \end{itemize}
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/weighted_timecourse_summary}
+\caption{\textbf{Dynamics of physical activity varies with memory
+    performance and mental health measures.}  \textbf{a. Daily step counts.}  Each
+  timecourse is weighted by either performance on immediate recall tests
+  (left panel) or on delayed recall tests (right panel).  The black
+  (baseline) timecourses display the (unweighted) average across all
+  participants.  \textbf{b. Daily duration (in minutes) of low-intensity physical
+    activity.}  Timecourses are displayed in the same format and color
+scheme as those in Panel A.  \textbf{c. Timecourses of physical
+  activity, weighted by mental health measures.}  The timecourses in
+each panel display the average daily step counts (top panel) or
+duration of low-intensity activity (bottom panel).  Each color denotes
+the average timecourse for all participants with the indicated
+mental health conditions.  The baseline curves (black) display the
+average across all participants (re-plotted in Panel C to illustrate
+scale differences across panels).  Error ribbons in all panels denote
+the standard error of the mean.  Horizontal lines below each panel's
+timecourses denote intervals over which each weighted measure (color) differs
+from the unweighted baseline.}
+\label{fig:dynamics}
+\end{figure}
+
+The above analyses indicate that recent differences in fitness-related
+activity are associated with differences in memory performance and
+mental health measures.  Although the analyses treated these measures
+on average or in aggregate, many of the measures we collected are
+dynamic. For example, the amount or intensity of physical exercise
+people engage in can vary over time, and so on.  We wondered whether
+the dynamics of fitness-related measures might related to memory
+performance and mental health measures.  To this end, we carried out a
+series of reverse correlation analyses (see \textit{Reverse
+  correlation analyses}) to examine whether participants with
+different cognitive or mental health profiles also tended to display
+differences in fitness-related measures over time.  In particular, we
+examined fitness data collected from participants' Fitbit devices over
+the year prior to their test day in our study.  Several example findings are summarized in
+Figure~\ref{fig:dynamics}.  We found that participants who performed
+well on the immediate and delayed free recall memory tests and on the
+naturalistic recall tests tended to be more active than participants
+who performed poorly on those tests (Figs.~\ref{fig:dynamics}a, b;
+\activityTimecourse).  Conversely, participants who performed well on
+the immediate and delayed foreign language flashcards tasks tended to
+be \textit{less} active.  These differences were present even a full
+year before the testing day.  We also found substantial variability
+across people with different (self-reported) mental health profiles
+(Figs.~\ref{fig:dynamics}c, \activityTimecourseMH).  Due to small sample
+sizes of individuals exhibiting several mental health dimensions, it
+is difficult to distinguish generalizable trends from individual
+differences that one or two individuals happened to exhibit.  However,
+several large-sample-size trends emerged.  For example, participants
+who reported higher levels of stress also tended to be slightly more
+physically active than participants who reported lower stress levels.
+We found analogous differences in other activity-related measures
+(Figs.~\activityTimecourse~and \activityTimecourseMH), cardiovascular
+measures (Figs.~\cardioTimecourse~and \cardioTimecourseMH), and
+sleep-related measures (Figs.~\sleepTimecourse~and
+\sleepTimecourseMH).  Taken together, the analyses suggest that
+cogntive and mental health differences are also associated with differences
+in the dynamics of physical health measures.
 
 \section*{Discussion}
+
   \begin{itemize}

### 2021-10-20 paper/supplement.tex
finished draft of results section, added timecourse figs to supplement

@@
     behavioral measures and fitness or demographic measures.}}
-\label{fig:survey_corrs}
+\label{fig:fitness_survey_corrs}
 \end{sidewaysfigure}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity}
+\caption{\textbf{History of fitness activity levels weighted by
+    behavioral performance.}}
+\label{fig:activity_timecourse}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figs/weighted_timecourse_HR}
+\caption{\textbf{History of cardiovascular activity weighted by
+    behavioral performance.}}
+\label{fig:HR_timecourse}
+  \end{figure}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep}
+\caption{\textbf{History of sleep efficiency and duration weighted by
+    behavioral performance.}}
+\label{fig:sleep_timecourse}
+\end{figure}
+
+\begin{sidewaysfigure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
+\caption{\textbf{History of fitness activity levels weighted by
+    mental health factors.}}
+\label{fig:activity_timecourse_MH}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}[p]
+  \centering
+  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
+\caption{\textbf{History of cardiovascular activity weighted by
+    mental health factors.}}
+\label{fig:HR_timecourse_MH}
+  \end{sidewaysfigure}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
+\caption{\textbf{History of sleep efficiency and duration weighted by
+    mental health factors.}}
+\label{fig:sleep_timecourse_MH}
+  \end{figure}
 

### 2021-10-20 paper/main.tex
working on supplement figure captions

@@
 only an immediate test. Participants in all four tasks exhibited
-general trends and tendancies that have been previously reported in
+general trends and tendencies that have been previously reported in
 prior work.  We were also interested in characterizing the variability
@@
 negatively correlated with recent increases in step counts and daily
-elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, boostrap
+elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, bootstrap
 corrected), where recent changes were defined as the average values
@@
 \sleepTimecourseMH).  Taken together, the analyses suggest that
-cogntive and mental health differences are also associated with differences
+cognitive and mental health differences are also associated with differences
 in the dynamics of physical health measures.
@@
 \section*{Discussion}
+After collecting a year's worth of fitness-tracking data from 113
+participants, we ran each participant in a battery of memory tasks and
+had them fill out a series of demographic and mental health-related
+questions.  We found that the associations between fitness-related
+activities, memory performance, and mental health are heterogeneous.
+Our results suggest that engagement in particular physical
+activities (e.g., differing in time relative to the
+test day, intensity, duration, etc.) is also reflected in participants'
+memory performance patterns across tasks and in participants' mental
+health attributes.
 
-  \begin{itemize}
-  \item summarize key findings
-  \item correlation versus causation
-         \item what can vs.
-can't we know?
-we can identify correlations, but not causal direction-- e.g.
-we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.
-that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
-  \item related work (exercise/memory, exercise/mental health), what this study adds
-    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
-    \end{itemize}
+One important limitation of our study is that we cannot distinguish
+correlations between different measures from potential causal
+effects.  For example, we cannot know (from our study) whether
+engaging in particular forms of exercise \textit{causes} changes in
+memory performance or mental health, or whether (alternatively) people
+who tend to engage in similar forms of exercise also happen to
+exhibit similar memory and/or mental health profiles.  In other words,
+an overlapping set of processes or person-specific attributes may lead
+someone to both form particular habits around exercise and display high or low performance on a
+given memory test.  We do not know whether memory performance or
+aspects of mental health might be manipulated or influenced by
+changing the patterns of physical activity someone engages in.  For
+this reason, we have been careful to frame our findings as
+correlations and associations, rather than to imply knowledge about a causal direction
+of our findings.
+
+Although the present study cannot reveal causal effects, a large prior
+literature provided some insight into potential causal effects by examining the neural and cognitive effects of a variety
+of exercise interventions~\citep{ChanEtal15, VidoEtal15, KamiEtal07,
+  ImboEtal19, SuwaEtal17, SinhEtal21, Tomp03}.  A limitation of that
+prior work is that most of these studies examine how relatively
+short-term changes in exercise (e.g., on timescales of hours to days
+or, rarely, weeks to months) affect a cognitive performance on single
+task or aspect of mental health.  The present study examines
+longer-term exercise (over a full year), and relates long-term
+exercise history to performance on a variety of tasks and to a variety
+of mental health dimensions.
+
+To the extent that exercise \textit{does} provide a non-invasive means
+of manipulating cognitive performance and mental health, our work may
+have exciting implications for cognitive enhancement.  For example,
+one might imagine building a recommendation system that suggests a
+particular exercise regimen tailored to improve a specific aspect of
+an individual's cognitive performance (e.g., the efficacy of a student's study session for an
+upcoming exam) or mental health (e.g., reducing symptoms of anxiety
+before an important meeting).  Just as strength training may be
+customized to target a specific muscle group, or to improve
+performance on a specific physical task, similar principles might also
+be applied to target specific improvements in cognitive fitness
+and mental health.
 

### 2021-10-20 paper/supplement.tex
working on supplement figure captions

@@
 
+\newcommand{\task}{1}
+\newcommand{\immediateBehavior}{2}
+\newcommand{\delayedBehavior}{3}
+\newcommand{\fitness}{4}
+\newcommand{\MHcorr}{5}
+\newcommand{\dynamics}{6}
+
 \begin{document}
@@
 \includegraphics[width=1\textwidth]{figs/free_recall_behavior}
-\caption{\textbf{Free recall behavioral results.}}
+\caption{\textbf{Free recall behavioral results.  a--e. Immediate free
+  recall.}  \textbf{a. Probability of first recall.}  Probability of
+recalling each studied word first, as a function of its presentation
+position.  \textbf{b. Lag Conditional Response Probability.}
+Probability of recalling the word presented at position $i +
+\mathrm{Lag}$ following the recall of the word presented at position
+$i$.  \textbf{c. Clustering scores.}  Each score denotes participants'
+tendancies to successively recall (cluster) words according to the
+given feature dimension~\citep{PolyEtal09}: word length, starting letter, (semantic)
+category, size (large or small), or presentation position (temporal).
+\textbf{d. Serial position curve.}  Probability of recalling each word
+as a function of its presentation position.  \textbf{e. Recall
+  accuracy.}  Distribution of the average proportions of recalled
+words, across all lists studied by each participant.  \textbf{f--j.
+  Delayed free recall.}  These panels are in the same formats as
+Panels a -- e, but they reflect performance on the delayed free recall
+memory tests.  All panels: error bars and error ribbons denote bootstrap-estimated
+95\% confidence intervals.  Shading (saturation) denotes results for
+different subsets of participants, according to the average
+proporition of words they remembered (group boundaries are indicated
+by the colored lines in Panels e and j).}
 \label{fig:fr_behavioral}
@@
 \includegraphics[width=1\textwidth]{figs/naturalistic_recall_behavior}
-\caption{\textbf{Naturalistic recall behavioral results.}}
+\caption{\textbf{Naturalistic recall behavioral results.}
+  \textbf{a. Identified topics.}  Applying a topic model to a series
+  of sliding windows of the video's transcript~\citep{HeusEtal21}
+  revealed a set of 13 unique (non-trivial) topics.  The Panel
+  displays the 5 top-weighted words from each topic.  \textbf{b. Topic
+  timecourse of the video.}  Each row displays the topic weights for a
+single moment of the video.  \textbf{c. Topic correlation matrix.}  The
+correlations between the topic vectors for each pair of moments from
+the video reveals an event-like block diagonal structure.
+\textbf{d. Video topic trajectory.}  The topic video's topic
+timecourse (Panel b) has been projected onto 2-dimensions using
+Uniform Manifold Approximation and
+Projection~\citep[UMAP;][]{McInEtal18}.  Each colored dot reflects an
+event, identified by applying a Hidden Markov Model to the video's
+topic timecourse~\citep{BaldEtal17, HeusEtal21}.  Red dots denote
+earlier timepoints in the video and blue dots denote later
+timepoints.  \textbf{e. Immediate recall trajectory.}  The black curve
+displays the average
+topic timecourse (projected into 2D using UMAP), obtained by applying the topic model shown in Panel A
+to the participants' written transcripts from the immediate recall
+test.  The arrows denote agreement across participants in the
+directions of their topic trajectories, for participants whose
+trajectories intersected the corresponding region of topic space.
+Blue arrows denote reliable agreement across participants ($p < 0.05$, corrected).
+\textbf{f. Delayed recall trajectory.} This panel is in the same
+format as Panel e, but displays the trajectory for participants'
+delayed recall of the video.  \textbf{g. Immediate recall precision.}  Distribution of
+average recall \textit{precision}, across all of the events each
+participant recalled during the immediate recall test.  Precision is
+defined as the correlation between the topic vector for a given
+recalled event and the best-matching (most highly correlated) video
+event's topic
+vector~\citep{HeusEtal21}.  \textbf{h. Delayed recall precision.}
+This panel is in the same format as Panel g, but displays the average
+precision values for the delayed memory test.}
 \label{fig:nat_behavioral}
@@
 \includegraphics[width=0.6\textwidth]{figs/vocab_learning_behavior}
-\caption{\textbf{Foreign language vocabulary learning behavioral results.}}
+\caption{\textbf{Foreign language vocabulary learning behavioral
+    results.}  \textbf{a. Immediate recall....}}
 \label{fig:vocab_behavioral}
@@
 
+  \clearpage
+  \newpage
 \bibliographystyle{apa}

### 2021-10-20 paper/supplement.tex
working on supplement figure captions (backing up progress)

@@
 \caption{\textbf{Foreign language vocabulary learning behavioral
-    results.}  \textbf{a. Immediate recall....}}
+    results.}  \textbf{a. Immediate recall.}  Average proportions of
+  correctly identified Gaelic-English word pairs from \textit{early} (first 3) and
+\textit{late} (last 3) study positions, or aggregated over
+\textit{all} study positions.  \textbf{b. Distribution of proportion
+  of correctly recalled pairs on the immediate memory test.}  The colored
+lines indicate quartile boundaries, and correspond to the coloring in
+Panel a.  Note that the right-most edge of the third quartile overlaps
+with the top quartile, since over 25\% of the participants correctly recalled
+90\% of the word pairs correctly, but no participant achieved 100\%
+accuracy.  \textbf{c--d. Delayed recall.}  These panels are in the
+same formats as Panels a and b, but reflect performance on the delayed
+recall test.  The error bars in Panels a and c denote
+bootstrap-estimated 95\% confidence intervals.}
 \label{fig:vocab_behavioral}

### 2021-10-20 paper/supplement.tex
(still) working on supplement figure captions

@@
 \includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
-\caption{\textbf{Spatial learning behavioral results.}}
+\caption{\textbf{Spatial learning behavioral results.}
+  \textbf{a--b. Estimation error.}  Estimation
+  error is defined as the Euclidean distance between each shape's
+  studied and recalled positions.  The bars show the average
+  estimation error (across all shapes for each memory test) versus the
+  number of memorized shapes.  \textbf{a. Slope.} Estimation errors
+  are broken down by the slopes of regresion lines fit to each
+  participant's estimation errors as a function of the number of
+  memorized shapes.  Shallower slopes (i.e., smaller decreases in
+  performance associated with memorizing more shapes) are reflected by
+  more saturated coloring.  Error bars denote bootstrap-estimated 95\%
+  confidence intervals.  \textbf{b. Intercept.}  Bars are in the same
+  format as Panel a, but here estimation errors are
+  broken down by the intercepts of the same regressions used in Panel
+  a.  Smaller intercepts (i.e., smaller baseline errors) are reflected
+  by more saturated coloring.  \textbf{c. Distribution of slopes.}
+  Across-participant distribution of regression slopes.  The lines
+  denote quartile boundaries (colors are matched to Panel a).  The
+  slopes are multiplied by -1 and normalized to be within the [0, 1]
+  interval such that (adjusted) slopes closer to 1 reflect better
+  performance and slopes closer to 0 reflect worse performance.
+  \textbf{b. Distribution of intercepts.}  Across-participant
+  distribution of regression intercept terms.  The lines denote
+  quartile boundaries (colors are matched to Panel b).  The intercepts
+  are multiplied by -1 and normalized to be within the [0, 1] interval
+  such that (adjusted) intercepts closer to 1 reflect better
+  performance and intercepts closer to 0 reflect worse performance.}
 \label{fig:spatial_behavioral}

### 2021-10-21 paper/supplement.tex
finished drafts of all supplement captions, added supplement table

@@
 \renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 
@@
 $i$.  \textbf{c. Clustering scores.}  Each score denotes participants'
-tendancies to successively recall (cluster) words according to the
+tendencies to successively recall (cluster) words according to the
 given feature dimension~\citep{PolyEtal09}: word length, starting letter, (semantic)
@@
 different subsets of participants, according to the average
-proporition of words they remembered (group boundaries are indicated
+proportion of words they remembered (group boundaries are indicated
 by the colored lines in Panels e and j).}
@@
   number of memorized shapes.  \textbf{a. Slope.} Estimation errors
-  are broken down by the slopes of regresion lines fit to each
+  are broken down by the slopes of regression lines fit to each
   participant's estimation errors as a function of the number of
@@
 
+\clearpage
+\begin{table}[]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{p{1.5in}p{4in}p{1.5in}}
+\textbf{Abbreviation}   & \textbf{Description}
+  & \textbf{Units}                           \\
+  \hline
+Resting HR              & Average daily resting heart rate                                                                                                                                                     & beats per minute (BPM)                   \\
+  \hline
+HR variability          & Heart rate variability (average daily variation between heartbeats)                                                                                                                  & milliseconds (ms)                        \\
+  \hline
+Steps                   & Number of steps taken each day                                                                                                                                                       & steps (count)                            \\
+  \hline
+Distance                & Estimated distance traveled each day                                                                                                                                                 & kilometers (km)                          \\
+  \hline
+Elevation               & Estimated daily elevation gain                                                                                                                                                       & feet (ft)                                \\
+  \hline
+Floors climbed          & Estimated number of daily floors climbed                                                                                                                                             & floors (count)                           \\
+  \hline
+Light activity          & Number of estimated daily minutes spent doing low-intensity activity                                                                                                                 & minutes (min)                            \\
+  \hline
+Fair activity           & Number of estimated daily minutes spent doing moderate-intensity activity                                                                                                            & minutes (min)                            \\
+  \hline
+High intensity activity & Number of estimated daily minutes spent doing high-intensity activity                                                                                                                & minutes (min)                            \\
+  \hline
+Excess calories         & Number of estimated daily calories burned minus estimated calorie intake                                                                                                             & calories (cal)                           \\
+  \hline
+Out-of-range HR         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\
+  \hline
+Fat burn HR             & Number of daily minutes spent with a heart rate between 50\% and 69\% of the maximum heart rate                                                                                      & minutes (min)                            \\
+  \hline
+Cardio HR               & Number of daily minutes spent with a heart rate between 70\% and 84\% of the maximum heart rate                                                                                      & minutes (min)                            \\
+  \hline
+Peak HR                 & Number of daily minutes spent with a heart rate between 85\% and 100\% of the maximum heart rate                                                                                     & minutes (min)                            \\
+  \hline
+Sleep duration          & Estimated number of hours slept during the prior 24 hour period                                                                                                                      & hours (hr)                               \\
+  \hline
+BMI                     & Body mass index, calculated as the
+                          individual's weight (in kg) divided by their
+                          height (in m) squared
+  & kilograms per meter squared (kg/m\textsuperscript{2}) \\
+  \hline
+Body fat                & Estimated percentage of body fat (as a proportion of the individual's total weight)                                                                                                  & percentage (\%)                          \\
+  \hline
+Weight                  & Logged or measured weight                                                                                                                                                            & kilograms (kg)                           \\
+  \hline
+Water intake            & Self-reported water intake                                                                                                                                                           & 8 ounce cups (count)                     \\
+  \hline
+Coffee intake           & Self-reported coffee intake                                                                                                                                                          & 8 ounce cups (count)
+\end{tabular}%
+}
+\caption{\textbf{Abbreviations of fitness-related measures.}  The
+  abbreviations and descriptions provided in the table apply to the
+  main text and supplement.}
+\label{tab:abbreviations}
+\end{table}
+
 \begin{sidewaysfigure}[p]
@@
 \includegraphics[width=\textwidth]{figs/fitness_distributions}
-\caption{\textbf{Distributions of fitness measures.}}
+\caption{\textbf{Distributions of fitness measures.}  All
+  abbreviations and measures are described in
+  Table~\ref{tab:abbreviations}.  \textbf{a. Recent measures.}
+  Daily values of each measure, averaged over the week prior to each
+  participant's test day.  \textbf{b. Baselined measures.}  Daily
+  values of each measure, averaged over the week prior to each
+  participant's test day and divided by the average taken over the
+  preceding 30 days.  \textbf{c. Static measures.} For each measure,
+  only the most recently logged values are considered.  All panels:
+  note that not all measures were captured for all participants.  Only
+participants whose Fitbit records logged each given measure are
+included in the distribution(s) for that measure.}
 \label{fig:fitness_dists}
@@
 \caption{\textbf{Distributions of fitness measures, broken down
-    by immediate task performance.}}
+    by immediate task performance.}  The distributions of recent
+  (Panel a), baselined (Panel b), and static (Panel c) fitness
+  measures (Tab.~\ref{tab:abbreviations}) are broken down by
+  participants' performance on each immediate recall test
+  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral},
+  \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
 \label{fig:fitness_dists_immediate}
@@
 \caption{\textbf{Scatterplots of fitness measures versus
-    immediate task performance measures.}}
+    immediate task performance measures.}  The scatterplots of recent
+  (Panel a), baselined (Panel b), and static (Panel c) fitness
+  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
+  participants' performance on each immediate recall test
+  (Figs.~\immediateBehavior, \ref{fig:fr_behavioral}, \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and \ref{fig:spatial_behavioral})}
 \label{fig:fitness_scatters_immediate}
@@
 \caption{\textbf{Distributions of fitness measures, broken down
-    by delayed task performance.}}
+    by delayed task performance.} The distributions of recent
+  (Panel a), baselined (Panel b), and static (Panel c) fitness
+  measures (Tab.~\ref{tab:abbreviations}) are broken down by
+  participants' performance on each delayed recall test
+  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
+  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
 \label{fig:fitness_dists_delayed}
@@
 \caption{\textbf{Scatterplots of fitness measures versus
-    delayed task performance measures.}}
+    delayed task performance measures.} The scatterplots of recent
+  (Panel a), baselined (Panel b), and static (Panel c) fitness
+  measures (Tab.~\ref{tab:abbreviations}) are plotted against 
+  participants' performance on each delayed recall test
+  (Figs.~\delayedBehavior, \ref{fig:fr_behavioral},
+  \ref{fig:nat_behavioral}, and \ref{fig:vocab_behavioral})}
 \label{fig:fitness_scatters_delayed}
@@
 \caption{\textbf{Bootstrap-estimated reliable correlations between
-    behavioral measures.}}
+    behavioral measures.}  The measures are described and summarized in the
+  distributions shown in Figures~\ref{fig:fr_behavioral},
+  \ref{fig:nat_behavioral}, \ref{fig:vocab_behavioral}, and
+  \ref{fig:spatial_behavioral}.
+The reported values denote the correlation coefficient between the
+given row and column.  Only statistically reliable correlations are
+displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
+  analysis}, main text).}
 \label{fig:behavioral_corrs}
@@
 \caption{\textbf{Bootstrap-estimated reliable correlations between
-    fitness measures.}}
+    fitness measures.}  Fitness measures are described in summarized
+  in Table~\ref{tab:abbreviations}.  The reported values denote the correlation coefficient between the
+given row and column.  Only statistically reliable correlations are
+displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
+  analysis}, main text).}
 \label{fig:fitness_corrs}
@@
 \caption{\textbf{Bootstrap-estimated reliable correlations between
-    demographic measures.}}
+    demographic measures.}  Demographic measures are described in the
+  main text (\textit{Participants}).  The reported values denote the correlation coefficient between the
+given row and column.  Only statistically reliable correlations are
+displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
+  analysis}, main text).}
 \label{fig:survey_corrs}
@@
 \caption{\textbf{Bootstrap-estimated reliable correlations between
-    behavioral measures and fitness or demographic measures.}}
+    behavioral measures and fitness or demographic measures.}  All
+  measures and abbreviations in this figure use the same notations as
+  Figures~\ref{fig:behavioral_corrs}, \ref{fig:fitness_corrs}, and
+  \ref{fig:survey_corrs}.  Only statistically reliable correlations are
+displayed ($p < 0.05$, corrected; see \textit{Exploratory correlation
+  analysis}, main text).}
 \label{fig:fitness_survey_corrs}
@@
 \caption{\textbf{History of fitness activity levels weighted by
-    behavioral performance.}}
+    behavioral performance.}  This figure is in the same format as
+  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:activity_timecourse}
@@
 \caption{\textbf{History of cardiovascular activity weighted by
-    behavioral performance.}}
+    behavioral performance.}  This figure is in the same format as
+  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:HR_timecourse}
@@
 \caption{\textbf{History of sleep efficiency and duration weighted by
-    behavioral performance.}}
+    behavioral performance.}  This figure is in the same format as
+  Figure~\dynamics a and b, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:sleep_timecourse}
@@
 \caption{\textbf{History of fitness activity levels weighted by
-    mental health factors.}}
+    mental health factors.}  This figure is in the same format as
+  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:activity_timecourse_MH}
@@
 \caption{\textbf{History of cardiovascular activity weighted by
-    mental health factors.}}
+    mental health factors.} This figure is in the same format as
+  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:HR_timecourse_MH}
@@
 \caption{\textbf{History of sleep efficiency and duration weighted by
-    mental health factors.}}
+    mental health factors.} This figure is in the same format as
+  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:sleep_timecourse_MH}

### 2021-10-21 paper/main.tex
several minor typo fixes

@@
   exercise might related to different aspects of memory and mental
-  health.  To test our hypothesis, we collected nearly a century's
+  health.  To test our hypothesis, we collected roughly a century's
   worth of fitness data (in aggregate).  We then asked participants to
@@
 synaptic inputs from entorhinal cortex to the hippocampus, albeit in
-rodents;]{PalaEtal21}.  Given the central role of these medial
+rodents;][]{PalaEtal21}.  Given the central role that these medial
 temporal lobe structures play in memory, changes in acetylcholine
@@
 they were fluent in English and regularly used a Fitbit fitness
-tracker device.  A total of 160 workers accepted our
-HIT in order to participate in our experiment.  Of these, we excluded all
-participants who failed to log into their Fitbit account (giving us
-access to their anonymized fitness tracking data), encountered
-technical issues (e.g., by accessing the HIT using an incompatible browser, device, or
+tracker device.  A total of 160 workers accepted our HIT in order to
+participate in our experiment.  Of these, we excluded all participants
+who failed to log into their Fitbit account (giving us access to their
+anonymized fitness tracking data), encountered technical issues (e.g.,
+by accessing the HIT using an incompatible browser, device, or
 operating system), or who ended their participation prematurely,
-before completing the full study.  In all, 113 participants remained
-that contributed usable data to the study.
+before completing the full study.  In all, 113 participants
+contributed usable data to the study.
 
@@
 blood pressure (1 participant), bipolar (1 participant),
-hypothyroidism (1 participant), and other unspecified medications (1
+hypothyroidism (1 participant), and other unspecified conditions or medications (1
 participant).  Participants reported their current and typical stress
@@
 \paragraph{Reported water and coffee intake.}
-Participants reported the number of cups of water and coffee they had
+Participants reported the number of 8~oz cups of water and coffee they had
 consumed prior to accepting the HIT.  Water consumption ranged from
@@
 \subsubsection*{Tasks}
-Upon accepting the HIT posted on Mechanical Turk, the worker was
+Upon accepting the HIT posted on Mechanical Turk, each worker was
 directed to read and fill out a screening and consent form, and to
 share access to their anonymized Fitbit data via their Fitbit account.
-After consenting to participant and successfully sharing their Fitbit
+After consenting to participate in our stidy and successfully sharing their Fitbit
 data, participants filled out a survey and then engaged in a series of
@@
 The word lists participants studied were drawn from the categorized
-lists reported in \cite{ZimaEtal18}.  Each participant was assigned
+lists reported by \cite{ZimaEtal18}.  Each participant was assigned
 four unique randomly chosen lists (in a randomized order), selected
@@
 for iteration $n$, $\tanh$ is the hyperbolic tangent, and $\tanh^{-1}$
-is the inverse hyperbolic tangent.
+is the inverse hyperbolic tangent.  We estimated the corresponding $p$-values
+for these correlations as one minus the proportion of bootstrapped
+correlations with the same sign, multiplied by two.
 
@@
 negatively correlated with recent increases in step counts and daily
-elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, bootstrap
-corrected), where recent changes were defined as the average values
+elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$), where recent changes were defined as the average values
 over the seven days leading up to the test day divided by the average

### 2021-10-22 paper/main.tex
addressed all coauthor comments, additional round of JRM edits, updated figs

@@
   Different forms of exercise (i.e., aerobic versus anaerobic; running
-  versus walking versus swimming versus yoga; high-intensity interval
-  training versus endurance workouts; etc.) impact physical fitness
-  in different ways.  For example, running may substantially impact
-  leg and heart strength but only moderately impact arm strength. We
+  versus walking, swimming, or yoga; high-intensity interval training
+  versus endurance workouts; etc.) impact physical fitness in
+  different ways.  For example, running may substantially impact leg
+  and heart strength but only moderately impact arm strength. We
   hypothesized that the mental benefits of exercise might be similarly
@@
   exercise might related to different aspects of memory and mental
-  health.  To test our hypothesis, we collected roughly a century's
-  worth of fitness data (in aggregate).  We then asked participants to
+  health.  To test our hypothesis, we collected (in aggregate) roughly
+  a century's worth of fitness data.  We then asked participants to
   fill out surveys asking them to self-report on different aspects of
@@
   battery of memory tasks that tested their short and long term
-  episodic, semantic, and spatial memory.  We found that participants
-  with similar exercise habits and fitness profiles tended to also
-  exhibit similar mental health and task performance profiles.
+  episodic, semantic, and spatial memory performance.  We found that
+  participants with similar exercise habits and fitness profiles
+  tended to also exhibit similar mental health and task performance
+  profiles.  These effects were task-specific in that different
+  exercise patterns or fitness characteristics varied with different
+  aspects of memory, on different tasks.
 \end{abstract}
@@
 \section*{Introduction}
-Engaging in physical activity (exercise) can improve our physical
-fitness by increasing muscle strength~\citep{RogeEvan93, Lind79,
-  CranEtal13, Knut07}, increasing bone density~\citep{ChilEtal12,
-  BassRams94, LaynNels99}, increasing cardiovascular
-performance~\citep{MaioEtal00, PollEtal00}, increasing lung
-capacity~\citep{LazoEtal16}~\citep[although see][]{RomaEtal16},
-increasing endurance~\citep{WilmKnut03}, and more.  Exercise can also
+Engaging in physical activity (exercise) can improve physical
+fitness by increasing muscle strength \citep{RogeEvan93, Lind79,
+  CranEtal13, Knut07}, bone density~\citep{ChilEtal12,
+  BassRams94, LaynNels99}, cardiovascular
+performance~\citep{MaioEtal00, PollEtal00}, lung
+capacity~\citep[][although see \cite{RomaEtal16}]{LazoEtal16},
+endurance~\citep{WilmKnut03}, and more.  Exercise can also
 improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
@@
 data from each of 113 participants.  We then asked each participant to
-fill out a brief survey in which they self-evaluated several aspects
+fill out a brief survey in which they self-evaluated and self-reported
+several aspects
 of their mental health.  Finally, we ran each participant through a
 battery of memory tasks, which we used to evaluate their memory
-performance along several dimensions.  We examined the data for
+performance along several dimensions.  We searched the data for
 potential associations between memory, mental health, and exercise.
@@
 
-    We ran an online experiment using the Amazon Mechanical Turk
-    platform.  We collected data about each participant's fitness and
+    We ran an online experiment using the Amazon Mechanical Turk (MTurk)
+    platform~\citep{GureEtal16}.  We collected data about each participant's fitness and
     exercise habits, a variety of self-reported measures concerning their
     mental health, and about their performance on a battery of memory
-    tasks.  We mined the dataset for potential associations between
-    memory, mental health, and exercise.
+    tasks.
 
@@
 We recruited experimental participants by posting our experiment as a
-Human Intelligence Task (HIT) on the Amazon Mechanical Turk platform.
-We limited participation to Mechanical Turk Workers who had been
-assigned a ``Masters'' designation on the platform, given to workers
+Human Intelligence Task (HIT) on the MTurk platform.
+We limited participation to MTurk Workers who had been
+assigned a ``master worker'' designation on the platform, given to workers
 who score highly across several metrics on a large number of HITs,
-according to a proprietary algorithm managed by Amazon.  We further
+according to a proprietary algorithm managed by Amazon.  One criteria
+embedded into the algorithm is a requirement that master
+workers must maintain a HIT acceptance rate of at least 95\%.  We further
 limited our participant pool to participants who self-reported that
@@
 depression (4 participants), recent head injury (2 participants), high
-blood pressure (1 participant), bipolar (1 participant),
+blood pressure (1 participant), bipolar disorder (1 participant),
 hypothyroidism (1 participant), and other unspecified conditions or medications (1
@@
 \subsubsection*{Tasks}
-Upon accepting the HIT posted on Mechanical Turk, each worker was
+Upon accepting the HIT posted on MTurk, each worker was
 directed to read and fill out a screening and consent form, and to
 share access to their anonymized Fitbit data via their Fitbit account.
-After consenting to participate in our stidy and successfully sharing their Fitbit
+After consenting to participate in our study and successfully sharing their Fitbit
 data, participants filled out a survey and then engaged in a series of
 memory tasks (Fig.~\ref{fig:tasks}).  All stimuli and code for running
-the full Mechanical Turk experiment may be found
+the full MTurk experiment may be found
 \href{https://github.com/ContextLab/brainfit-task}{\underline{here}}.
@@
 shuffled before presenting the words to the participants.
-
 Participants also performed a final delayed memory test where they
@@
 The narrator (Ronald) discusses growing up living in an apartment over
-Washington Heights branch of the New York Public Library, where his
+the Washington Heights branch of the New York Public Library, where his
 father worked as a custodian during the 1940s.
@@
 their previous responses.  Participants were given up to 10~minutes to
-enter their responses.  After 4~minutes participants were given the
+enter their responses.  After 4~minutes, participants were given the
 option of ending the response period early, e.g., if they felt they
@@
 responses by combining the sentences into a single document and
-removing extraneous whitespace characters.
-
-Following this 4--10 minute free response period, participants were
-given a series of 10 multiple choice questions about the conceptual
-content of the story.  All participants received the same questions,
-in the same order.
-
+removing extraneous whitespace characters.  Following this 4--10
+minute free response period, participants were given a series of 10
+multiple choice questions about the conceptual content of the story.
+All participants received the same questions, in the same order.
 Participants also performed a final delayed memory test, where they
@@
 relatively small number of native speakers and for its dissimilarity
-to other commonly spoken languages amongst Mechanical Turk Workers.
+to other commonly spoken languages amongst MTurk workers.
 We verified (via self report) that all of our participants were fluent
@@
 accounts varied in scope and duration according to which device the
-participant owned (Fig.~\devices), how often the participant
-wore (and/or synced) their tracking device, and how long they had
-owned their device.  For example, while all participants' devices
-supported basic activity metrics such as daily step counts, only a
-subset of the devices with heart rate monitoring capabilities provided
-information about workout intensity, resting heart rate, and other
-related measures.
-
-Across all devices, we collected the following information: heart rate
-data, sleep tracking data, logged bodyweight measurements, logged
-nutrition measurements, Fitbit account and device settings, and
+participant owned (Fig.~\devices), how often the participant wore
+(and/or synced) their tracking device, and how long they had owned
+their device.  For example, while all participants' devices supported
+basic activity metrics such as daily step counts, only a subset of the
+devices with heart rate monitoring capabilities provided information
+about workout intensity, resting heart rate, and other related
+measures.  Across all devices, we collected the following information:
+heart rate data, sleep tracking data, logged bodyweight measurements,
+logged nutrition measurements, Fitbit account and device settings, and
 activity metrics.
@@
 log of the specific foods they had eaten (and logged) over the past
-year, and the amount of water consumed each day.
+year, and the amount of water consumed (and logged) each day.
 
@@
 participant accepted the HIT, and $m(10)$ represents the value of $m$
-9 days prior to accepting the HIT.  Unless otherwise noted, we set
-$R = 7$ and $B = 30$.  In other words, to estimate recent changes in
-any metric $m$, we divided the average value of $m$ taken over the
-prior week by the average value of $m$ taken over the 30 days before
-that.
+9 days prior to accepting the HIT.  We set $R = 7$ and $B = 30$.  In
+other words, to estimate recent changes in any metric $m$, we divided
+the average value of $m$ taken over the prior week by the average
+value of $m$ taken over the 30 days before that.
 
@@
 between each pair of columns.  This yielded, for each pair of columns,
-a distribution of $N$ bootstrapped correlation coefficients.  If fewer
-than $97.5\%$ of the coefficients for a given pair of columns had the
+a distribution of $N$ bootstrapped correlation coefficients.  If
+$97.5\%$ or fewer of the coefficients for a given pair of columns had the
 same sign, we excluded the pair from further analysis and considered
 the expected correlation between those columns to be undefined.  If
-$\geq 97.5\%$ of the coefficients for a given pair of columns had the
+$> 97.5\%$ of the coefficients for a given pair of columns had the
 same sign (corresponding to a bootstrap-estimated two-tailed $p$
@@
 \subsubsection*{Reverse correlation analyses}
-We sought to characterize potential associations between the history
+We sought to characterize potential associations between the \textit{dynamics}
 of participants' fitness-related activities leading up to the time
@@
 ensuring that the lowest-weighted participant had relatively low (but
-non-zero) influence.
-
-We computed the weighted standard error of the mean as:
+non-zero) influence.  We computed the weighted standard error of the
+mean as:
 \[
@@
 \]
-
 When a given row of $F$ was missing data from one or more
@@
 remaining participants) were re-normalized to sum to 1.  The above
-procedure yielded, for each memory variable, a timeseries of average
-(and standard error of the mean) fitness tracking values leading up to
-the day of the experiment.
+procedure yielded, for each memory variable, a timeseries of weighted
+average (and weighted standard error of the mean) fitness tracking
+values leading up to the day of the experiment.
 
 \section*{Results}
-Before testing our main hypothesis we examined the behavioral data
+Before testing our main hypotheses, we examined the behavioral data
 from each of four memory tasks: a random word list learning ``free
-recall'' task; a naturalistic recall task whereby participants watched
+recall'' task (Fig.~\ref{fig:tasks}); a naturalistic recall task whereby participants watched
 a short video and then recounted the narrative; a foreign language
@@
 3), or all (i.e., all 10) study positions.  See
-Figure~\vocabDetail~for additional details.\textbf{d. Spatial
+Figure~\vocabDetail~for additional details.  \textbf{d. Spatial
   learning.}  Average estimation error in shape locations as a
@@
 (Fig.~\ref{fig:fitness_summary}a), baselined measurements (average
-over the prior week, divided by the average over the preceding 30 day;
+over the prior week, divided by the average over the preceding 30 days;
 Fig.~\ref{fig:fitness_summary}b), along with more gradually varying
@@
 activity levels ($r = 0.70, p = 0.0004$).
-Participants' peak heart rate (averaged over the prior week) were also
+Participants' peak heart rates (averaged over the prior week) were also
 negatively correlated with recent increases in step counts and daily
@@
 over the seven days leading up to the test day divided by the average
-values over the preceding 30 days.  Although several demographic
+values over the preceding 30 days.  Several demographic
 attributes (Fig.~\demDemCorr) displayed trivial correlations (e.g.,
 participants identifying as male never reported identifying as female,
-and so on), we also observed a negative correlation between reported
+and so on).  We also observed a negative correlation between reported
 stress and alertness ($r = -0.44, p < 0.0001$), and
@@
 correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
-0.38, p = 0.029$) recall on the naturalistic
+0.38, p = 0.029$) recall performance on the naturalistic
 memory task.  Recent increases in moderate-intensity (``cardio'')
 activity over the prior 7 days (relative to the preceding 30 days) was
-also positively correlated with immediate naturalistic recall ($r =
-0.48, p = 0.003$) and immediate recall on the foreign language
+also positively correlated with immediate naturalistic recall
+performance ($r =
+0.48, p = 0.003$) and immediate recall performance on the foreign language
 flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
@@
     activity.}  Timecourses are displayed in the same format and color
-scheme as those in Panel A.  \textbf{c. Timecourses of physical
+scheme as those in Panel A.  Analogous timecourses for additional
+fitness-related measures may be found in Figures~\activityTimecourse,
+\cardioTimecourse, and \sleepTimecourse.  \textbf{c. Timecourses of physical
   activity, weighted by mental health measures.}  The timecourses in
 each panel display the average daily step counts (top panel) or
-duration of low-intensity activity (bottom panel).  Each color denotes
-the average timecourse for all participants with the indicated
-mental health conditions.  The baseline curves (black) display the
+duration of low-intensity activity (bottom panel).  The colored lines
+show average activity dynamics weighted by self-reported stress levels
+at the start of the experiment (purple) and self-reported ``typical''
+stress levels (pink).  The baseline curves (black) display the
 average across all participants (re-plotted in Panel C to illustrate
-scale differences across panels).  Error ribbons in all panels denote
+scale differences across panels).  Timecourses for additional mental
+health-related and fitness-related measures may be found in
+Figures~\activityTimecourseMH, \cardioTimecourseMH, and \sleepTimecourseMH. Error ribbons in all panels denote
 the standard error of the mean.  Horizontal lines below each panel's
 timecourses denote intervals over which each weighted measure (color) differs
-from the unweighted baseline.}
+from the unweighted baseline (via a paired sample two-sided $t$-test
+of the weighted mean values for each measure within a 30 day window around each timepoint; horizontal lines denote $p <
+0.05$, corrected.}
 \label{fig:dynamics}
@@
 people engage in can vary over time, and so on.  We wondered whether
-the dynamics of fitness-related measures might related to memory
-performance and mental health measures.  To this end, we carried out a
+the dynamics of fitness-related measures might relate to memory
+performance and/or mental health measures.  To this end, we carried out a
 series of reverse correlation analyses (see \textit{Reverse
@@
 \section*{Discussion}
-After collecting a year's worth of fitness-tracking data from 113
+After collecting a year's worth of fitness-tracking data from each of 113
 participants, we ran each participant in a battery of memory tasks and
@@
 questions.  We found that the associations between fitness-related
-activities, memory performance, and mental health are heterogeneous.
+activities, memory performance, and mental health were heterogeneous.
 Our results suggest that engagement in particular physical
@@
 Although the present study cannot reveal causal effects, a large prior
-literature provided some insight into potential causal effects by examining the neural and cognitive effects of a variety
+literature provides some insight into potential causal effects by examining the neural and cognitive effects of a variety
 of exercise interventions~\citep{ChanEtal15, VidoEtal15, KamiEtal07,
@@
 Concept: J.R.M.  Experiment implementation and data collection: G.M.N.
-Analyses: G.M.N., E.C., P.C.F., and J.R.M.  Writing: J.R.M.
+Analyses: G.M.N., E.C., P.C.F., and J.R.M.  Writing: J.R.M. with input
+from all authors.
 

### 2021-10-22 paper/supplement.tex
addressed all coauthor comments, additional round of JRM edits, updated figs

@@
   ``Unknown''  denotes participants whose device information was not
-  available from their available Fitbit data.}
+  specified in their Fitbit data.}
 \label{fig:devices}
@@
   \hline
-Out-of-range HR         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\
+Out-of-range HR, OOR mins         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\
   \hline
@@
     mental health factors.}  This figure is in the same format as
-  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
+  Figure~\dynamics c, but shows additional fitness-related and mental
+  health-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:activity_timecourse_MH}
@@
     mental health factors.} This figure is in the same format as
-  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
+  Figure~\dynamics c, but shows additional fitness-related and mental
+  health-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:HR_timecourse_MH}
@@
     mental health factors.} This figure is in the same format as
-  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
+  Figure~\dynamics c, but shows additional fitness-related and mental
+  health-related measures (Tab.~\ref{tab:abbreviations}).}
 \label{fig:sleep_timecourse_MH}

### 2021-10-22 code/fitness.py
data and code release

@@ -1,0 +1,19 @@
+def format_text(s, width=20):
+    if ':' in s:
+        return format_text(s[:s.find(':')], width=width)
+
+    words = [x.strip() for x in s.strip().replace('hr', 'HR').replace('Hr', 'HR').replace('heart rate', 'HR').split()]
+    words[0] = ''.join([w if i > 0 else w.upper() for i, w in enumerate(words[0])])
+
+    idx = 0
+    formatted = ''
+    line = ''
+    while idx < len(words):
+        if len(line) + len(words[idx]) > width:
+            formatted += line + '\n'
+            line = words[idx]
+        else:
+            line += ' ' + words[idx]
+        idx += 1
+    formatted += line
+    return formatted.strip()

### 2021-10-22 code/free_recall.py

@@ -1,0 +1,186 @@
+# noinspection PyPackageRequirements
+import datawrangler as dw
+import numpy as np
+import seaborn as sns
+from matplotlib import pyplot as plt
+import quail
+
+import warnings
+
+
+def get_bounds(data, bounds):
+    data = [d for d in data.values.ravel() if not np.isnan(d)]
+    return [np.percentile(data, p) for p in bounds]
+
+
+def distplot(data, bounds, cmap, x='Performance', y='Number of participants', bins=15):
+    bound_vals = get_bounds(data, bounds)
+    data = [d for d in data.values.ravel() if not np.isnan(d)]
+
+    sns.histplot(data, kde=True, color='k', bins=bins, edgecolor='w')
+    plt.xlabel(x, fontsize=14)
+    plt.ylabel(y, fontsize=14)
+    ylim = plt.ylim()
+
+    for i, p in enumerate(bound_vals):
+        plt.plot([p, p], ylim, color=cmap[i], linewidth=4)
+
+    plt.ylim(ylim);
+    plt.xlim([0, 1]);
+
+def create_fr_plots(fr, bounds, task_cmaps, prefix='', max_lag=8, save=False):
+    # noinspection PyShadowingNames
+    def get_fname(n, prefix):
+        if len(prefix) == 0:
+            return n + '.pdf'
+        else:
+            return f'{prefix}_{n}.pdf'
+
+    # noinspection PyShadowingNames
+    def group(vals, bounds):
+        edges = np.percentile(vals, bounds)
+        edges[-1] += 1
+        return np.digitize(vals, edges).ravel() - 1
+
+    # noinspection PyTypeChecker
+    def plot_grouped_dists(data, groups, cmap, core_color='k', alpha1=0.25, alpha2=0.3, x='Feature',
+                           y='Clustering score'):
+        # noinspection PyShadowingNames
+        def violin(x, color, alpha1=1, alpha2=0.5, linewidth=1):
+            for i, c in enumerate(x.columns):
+                parts = plt.violinplot([v for v in x[c].values if not np.isnan(v)], positions=[i])
+                for p in parts['bodies']:
+                    p.set_facecolor(color)
+                    p.set_edgecolor(None)
+                    p.set_alpha(alpha1 * alpha2)
+
+                for j in ['cmeans', 'cmins', 'cmaxes', 'cbars', 'cmedians', 'cquantiles']:
+                    if j not in parts.keys():
+                        continue
+                    parts[j].set_color(color)
[…]

### 2021-10-22 code/loader.py

@@ -1,0 +1,1488 @@
+# noinspection PyPackageRequirements
+import datawrangler as dw
+import os
+import sys
+import numpy as np
+import pandas as pd
+import ast
+import json
+import datetime
+import quail
+import nltk
+import warnings
+import pickle
+import datetime as dt
+
+# noinspection PyPackageRequirements
+from spellchecker import SpellChecker
+from glob import glob as lsdir
+from nltk.stem import WordNetLemmatizer
+from nltk.corpus import wordnet
+from scipy.spatial.distance import cdist, pdist
+from scipy.stats import wasserstein_distance, pearsonr, zscore
+from sklearn.linear_model import LinearRegression
+from flair.models import TextClassifier
+from flair.data import Sentence
+
+import brainiak.eventseg.event as event
+
+BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
+DATA_DIR = os.path.join(BASE_DIR, 'data')
+
+
+def load_raw():
+    datadir = os.path.join(DATA_DIR, 'raw_formatted')
+    files = lsdir(os.path.join(datadir, '*.csv'))
+    skip = ['data_descriptors.csv', 'event_descriptors.csv', 'id_filename_key.csv']
+    # noinspection PyShadowingNames
+    files = [f for f in files if os.path.split(f)[-1] not in skip]
+
+    # noinspection PyShadowingNames
+    raw_data = [pd.read_csv(f) for f in files]
+
+    loaded = []
+    subjects = []
+    for i, x in enumerate(raw_data):
+        # noinspection PyBroadException
+        try:
+            y = x.pivot_table(index=['datetime'], columns='variable', aggfunc=lambda a: a)
+            y.columns = [c[1] for c in y.columns]
+            loaded.append(y)
+            subjects.append(f'P{i}')
+        except:
+            print(f'error loading data: {files[i]}')
+            pass
+    return loaded, subjects
+
+
+def parse_data(d):
+    datadir = os.path.join(DATA_DIR, 'raw_formatted')
+    non_exp_descriptors = pd.read_csv(os.path.join(datadir, 'data_descriptors.csv'))
+    exp_descriptors = pd.read_csv(os.path.join(datadir, 'event_descriptors.csv'))
+
+    def variable_type(v):
+        def helper(descriptors):
+            if 'variable name' in descriptors.columns:
+                field = 'variable name'
+            else:
+                field = 'exp_event'
+            # noinspection PyShadowingNames
[…]

### 2021-10-22 code/naturalistic_recall.py

@@ -1,0 +1,515 @@
+# noinspection PyPackageRequirements
+import datawrangler as dw
+
+import math
+
+import numpy as np
+import pandas as pd
+from pycircstat.tests import rayleigh
+from statsmodels.stats.multitest import multipletests
+from tqdm.auto import tqdm
+from scipy.spatial.distance import cdist, pdist
+from scipy.stats import pearsonr
+
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import seaborn as sns
+import hypertools as hyp
+
+import os
+import pickle
+import warnings
+
+from loader import DATA_DIR, get_video_and_recall_trajectories, get_formatted_data, sliding_windows
+
+STEP = 0.9
+XGRID_SCALE = [-10, 25]
+YGRID_SCALE = [-17.5, 19.5]
+
+
+# noinspection PyShadowingNames
+def add_arrows(axes, x, y, *, aspace=None, head_width=None, **kwargs):
+    # spacing of arrows
+    if aspace is None:
+        aspace = .05 * np.max(np.abs([*XGRID_SCALE, *YGRID_SCALE]))
+    if head_width is None:
+        head_width = aspace / 3
+    # distance spanned between pairs of points
+    r = [0]
+    for i in range(1, len(x)):
+        dx = x[i] - x[i - 1]
+        dy = y[i] - y[i - 1]
+        r.append(np.sqrt(dx * dx + dy * dy))
+
+    r = np.array(r)
+    # cumulative sum of r, used to save time
+    rtot = []
+    for i in range(len(r)):
+        rtot.append(r[0:i].sum())
+    rtot.append(r.sum())
+    # will hold tuple(x, y, theta) for each arrow
+    arrow_data = []
+    # current point on walk along data
+    arrow_pos = 0
+    rcount = 1
+    while arrow_pos < r.sum():
+        x1, x2 = x[rcount - 1], x[rcount]
+        y1, y2 = y[rcount - 1], y[rcount]
+        da = arrow_pos - rtot[rcount]
+        theta = np.arctan2((x2 - x1), (y2 - y1))
+        ax = np.sin(theta) * da + x1
+        ay = np.cos(theta) * da + y1
+        arrow_data.append((ax, ay, theta))
+        arrow_pos += aspace
+        while arrow_pos > rtot[rcount + 1]:
+            rcount += 1
+            if arrow_pos > rtot[-1]:
+                break
+
+    for ax, ay, theta in arrow_data:
[…]

### 2021-10-22 docker-setup/jupyter_notebook_config.py

@@ -1,0 +1,14 @@
+"""
+Config file read by the notebook server with some options that presets
+running notebooks inside a container easier
+"""
+from os import getenv
+
+
+c.NotebookApp.ip = getenv("NOTEBOOK_IP")
+c.NotebookApp.port = int(getenv("NOTEBOOK_PORT"))
+c.NotebookApp.notebook_dir = getenv("NOTEBOOK_DIR")
+c.NotebookApp.open_browser = False
+c.NotebookApp.allow_root = True
+# https://github.com/jupyter/notebook/issues/3130
+c.FileContentsManager.delete_to_trash = False

### 2021-10-22 docker-setup/pin_conda_package_version.sh

@@ -1,0 +1,77 @@
+# shellcheck disable=SC2155,SC2207
+​
+# pins the currently installed version of a conda package and its related
+# packages (e.g., numpy, numpy-base), overwriting the existing pinned versions
+# if they exist
+pin_package() {
+    if [[ "$2" == "major" ]]; then
+        local fields=1
+    elif [[ "$2" == "minor" ]]; then
+        local fields=1,2
+    elif [[ "$2" == "exact" ]] || [ -z "$2" ]; then
+        local fields="1-"
+    else
+        echo "bad sub-version \"${2}\"; may be one of [\"major\"|\"minor\"|\"exact\"]"
+        return 1
+    fi
+​
+    if [[ "$3" == "min" ]]; then
+        local v_spec=">="
+    elif [[ "$3" == "max" ]]; then
+        local v_spec="<="
+    elif [[ "$3" == "equal" ]] || [ -z "$3" ]; then
+        local v_spec="="
+    else
+      echo "bad specification \"${3}\"; may be one of [\"min\"|\"max\"|\"equal\"] (default: \"equal\")"
+      return 1
+    fi
+​
+    local pkgs_to_pin=($(conda list "$1" \
+        | grep "^$1" \
+        | tr -s ' ' \
+        | cut -d ' ' -f 1,2 \
+        | cut -d '.' -f $fields \
+        | sed "s/$/.*/g; s/ /$v_spec/g"))
+​
+    if [ "${#pkgs_to_pin[@]}" -eq 0 ]; then
+      echo "no installed packages matching \"$1\""
+      return 1
+    fi
+​
+    for pkg_spec in "${pkgs_to_pin[@]}"; do
+        local search_str="$(echo "$pkg_spec" | cut -d "${v_spec:0:1}" -f 1)[<>=]"
+        local curr_pinned_version=$(conda config --show pinned_packages \
+            | grep "^  - $search_str" \
+            | sed 's/  - //')
+​
+        if [ -n "$curr_pinned_version" ]; then
+            if [[ "$curr_pinned_version" == "$pkg_spec" ]]; then
+                echo "$curr_pinned_version already pinned"
+                continue
+            fi
+​
+            conda config --remove pinned_packages "$curr_pinned_version"
+            echo "unpinned $curr_pinned_version"
+        fi
+        conda config --add pinned_packages "$pkg_spec"
+        echo "pinned $pkg_spec"
+    done
+}
+​
+​
[…]

### 2021-10-23 paper/main.tex
updated author affiliations
typo fixes

@@
 \author[1, $\star$]{Jeremy R. Manning}
-\author[1,2]{Gina M. Notaro}
+\author[1]{Gina M. Notaro}
 \author[1]{Esme Chen}
@@
 \affil[1]{Dartmouth College, Hanover, NH}
-\affil[2]{Lockheed Martin, Bethesda, MD}
 \affil[$\star$]{Address correspondence to
@@
   differentiated.  We focused specifically on how different forms of
-  exercise might related to different aspects of memory and mental
+  exercise might relate to different aspects of memory and mental
   health.  To test our hypothesis, we collected (in aggregate) roughly
@@
 of the weighted mean values for each measure within a 30 day window around each timepoint; horizontal lines denote $p <
-0.05$, corrected.}
+0.05$, corrected).}
 \label{fig:dynamics}

### 2021-11-05 paper/admin/elife_cover_letter.tex
incorporated GMN edits

\title{cover letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{hyperref, pxfonts, geometry}

  \setlength{\voffset}{0in}

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{\vspace{-0.3in}Jeremy R. Manning}
\addrfrom{
	Dartmouth College\\
    %Department of Psychological \& Brain Sciences\\
    %HB 6207 Moore Hall\\
	Hanover, NH  03755}

\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{eLife}:}

\closeline{Sincerely,}
%\usepackage{setspace}
%\linespread{0.85}
% How will your work make others in the field think differently and move the field forward?
% How does your work relate to the current literature on the topic?
% Who do you consider to be the most relevant audience for this work?
% Have you made clear in the letter what the work has and has not achieved?

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Fitness tracking
  reveals task-specific associations between memory, mental health,
  and exercise} to be considered for publication as a
\textit{Research Article}.  The manuscript reports new evidence that, just as different
forms of exercise affect \textit{physical} health in different ways,
different forms of exercise also affect cognitive performance and
mental health differently.

In our study, we collected a year of fitness tracking data from each
of 113 participants.  We also had the participants fill out surveys
asking them to self-report on different aspects of their mental
health, and to engage in a battery of memory tasks that assessed their
short and long term episodic, semantic, and spatial memory
performance.  We found that participants with similar exercise habits
and fitness profiles tended to also exhibit similar mental health and
memory performance profiles.  We view the study as laying a foundation
for future exercise interventions that target specific aspects of
cognitive performance and mental health.

We expect that this article will be of interest to researchers in a
broad range of areas, including fitness, memory, and mental health.

Thank you for considering our manuscript, and we hope you will find it suitable for publication in \textit{eLife}.

\end{newlfm}
\end{document}

### 2021-11-05 paper/main.tex
incorporated GMN edits

@@
 
+\newpage
 \begin{abstract}
   Physical exercise can benefit both physical and mental well-being.
-  Different forms of exercise (i.e., aerobic versus anaerobic; running
+  Different forms of exercise (e.g., aerobic versus anaerobic; running
   versus walking, swimming, or yoga; high-intensity interval training
@@
   exercise patterns or fitness characteristics varied with different
-  aspects of memory, on different tasks.
+  aspects of memory, on different tasks.  Taken together, these
+  findings provide foundational work for designing exercise
+  interventions that target specific components of cognitive performance
+  and mental health by leveraging low-cost fitness tracking devices.
 \end{abstract}
@@
 \section*{Introduction}
-Engaging in physical activity (exercise) can improve physical
-fitness by increasing muscle strength \citep{RogeEvan93, Lind79,
-  CranEtal13, Knut07}, bone density~\citep{ChilEtal12,
-  BassRams94, LaynNels99}, cardiovascular
-performance~\citep{MaioEtal00, PollEtal00}, lung
-capacity~\citep[][although see \cite{RomaEtal16}]{LazoEtal16},
-endurance~\citep{WilmKnut03}, and more.  Exercise can also
-improve mental health~\citep{Ragl90, MikkEtal17, TaylEtal85,
-  DeslEtal09, Call04, PaluSchw00, BassSuzu17} and cognitive performance~\citep{ChanEtal12b,
-  BrisEtal02, EtniEtal06, BassSuzu17}.
+Engaging in physical activity (exercise) can improve physical fitness
+by increasing muscle strength \citep{RogeEvan93, Lind79, CranEtal13,
+  Knut07}, bone density~\citep{ChilEtal12, BassRams94, LaynNels99},
+cardiovascular performance~\citep{MaioEtal00, PollEtal00}, lung
+capacity~\citep[][although see \cite{RomaEtal16}]{LazoEtal16}, and
+endurance~\citep{WilmKnut03}.  Exercise can also improve mental
+health~\citep{Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
+  PaluSchw00, BassSuzu17} and cognitive
+performance~\citep{ChanEtal12b, BrisEtal02, EtniEtal06, BassSuzu17}.
 
@@
 can in turn affect their growth or atrophy~\citep{SchiEtal13}.  By
-comparison, the benefits of exercise on mental health are less direct.  For
-example, one hypothesis is that exercise leads to specific
+comparison, the benefits of exercise on mental health are less direct.
+For example, one hypothesis is that exercise leads to specific
 physiological changes, such as increased aminergic synaptic
 transmission and endorphin release, which in turn act on
-neurotransmitters in the brain~\citep{PaluSchw00}.
-
-Speculatively, if different exercise regimens lead to different
-neurophysiological responses, one might be able to map out a spectrum
-of signalling and transduction pathways that are impacted by a given
-type, duration, and intensity of exercise in each brain region.  For
-example, prior work has shown that exercise increases acetylcholine
-levels, starting in the vicinity of the exercised
-muscles~\citep{ShoeEtal97}.  Acetylcholine is thought to play an
-important role in memory formation~\citep[e.g., by modulating specific
-synaptic inputs from entorhinal cortex to the hippocampus, albeit in
+neurotransmitters in the brain~\citep{PaluSchw00}.  Speculatively, if
+different exercise regimens lead to different neurophysiological
+responses, one might be able to map out a spectrum of signalling and
+transduction pathways that are impacted by a given type, duration, and
+intensity of exercise in each brain region.  For example, prior work
+has shown that exercise increases acetylcholine levels, starting in
+the vicinity of the exercised muscles~\citep{ShoeEtal97}.
+Acetylcholine is thought to play an important role in memory
+formation~\citep[e.g., by modulating specific synaptic inputs from
+entorhinal cortex to the hippocampus, albeit in
 rodents;][]{PalaEtal21}.  Given the central role that these medial
@@
 
-In the present study, we hypothesize that (a) different exercise regimens will
-have different, quantifiable impacts on cognitive performance and
-mental health, and that (b) these impacts will be consistant across
-individuals.  To this end, we collected a year of fitness tracking
-data from each of 113 participants.  We then asked each participant to
-fill out a brief survey in which they self-evaluated and self-reported
-several aspects
-of their mental health.  Finally, we ran each participant through a
-battery of memory tasks, which we used to evaluate their memory
-performance along several dimensions.  We searched the data for
-potential associations between memory, mental health, and exercise.
+In the present study, we hypothesize that (a) different exercise
+regimens will have different, quantifiable impacts on cognitive
+performance and mental health, and that (b) these impacts will be
+consistant across individuals.  To this end, we collected a year of
+real-world fitness tracking data from each of 113 participants.  We
+then asked each participant to fill out a brief survey in which they
+self-evaluated and self-reported several aspects of their mental
+health.  Finally, we ran each participant through a battery of memory
+tasks, which we used to evaluate their memory performance along
+several dimensions.  We searched the data for potential associations
+between memory, mental health, and exercise.
 
@@
 \section*{Author contributions}
-Concept: J.R.M.  Experiment implementation and data collection: G.M.N.
-Analyses: G.M.N., E.C., P.C.F., and J.R.M.  Writing: J.R.M. with input
+Concept: J.R.M. and G.M.N.  Experiment implementation and data collection: G.M.N.
+Analyses: J.R.M., G.M.N., E.C., and P.C.F.  Writing: J.R.M. with input
 from all authors.

### 2022-03-13 paper/admin/nhb_cover_letter.tex
updated cover letters and formatting

--- 2021-11-05 paper/admin/elife_cover_letter.tex
@@
 
-\greetto{To the editors of \textit{eLife}:}
+\greetto{To the editors of \textit{Nature Human Behavior}:}
 
@@
   reveals task-specific associations between memory, mental health,
-  and exercise} to be considered for publication as a
-\textit{Research Article}.  The manuscript reports new evidence that, just as different
+  and exercise} to be considered for publication as an
+\textit{Article}.  The manuscript reports new evidence that, just as different
 forms of exercise affect \textit{physical} health in different ways,
@@
 
-Thank you for considering our manuscript, and we hope you will find it suitable for publication in \textit{eLife}.
+Thank you for considering our manuscript, and we hope you will find it
+suitable for publication in \textit{Nature Human Behavior}.
 

### 2022-03-13 paper/admin/science_advances_cover_letter.tex
updated cover letters and formatting

--- 2022-03-13 paper/admin/nhb_cover_letter.tex
@@
 
-\greetto{To the editors of \textit{Nature Human Behavior}:}
+\greetto{To the editors of \textit{Science Advances}:}
 
@@
   and exercise} to be considered for publication as an
-\textit{Article}.  The manuscript reports new evidence that, just as different
+\textit{Research Article}.  The manuscript reports new evidence that, just as different
 forms of exercise affect \textit{physical} health in different ways,
@@
 Thank you for considering our manuscript, and we hope you will find it
-suitable for publication in \textit{Nature Human Behavior}.
+suitable for publication in \textit{Science Advances}.
 

### 2022-03-13 paper/admin/scientific_reports_cover_letter.tex
updated cover letters and formatting

--- 2021-11-05 paper/admin/elife_cover_letter.tex
@@
 
-\greetto{To the editors of \textit{eLife}:}
+\greetto{To the editors of \textit{Scientific Reports}:}
 
@@
   reveals task-specific associations between memory, mental health,
-  and exercise} to be considered for publication as a
-\textit{Research Article}.  The manuscript reports new evidence that, just as different
+  and exercise} to be considered for publication in \textit{Scientific
+  Reports}.  The manuscript reports new evidence that, just as different
 forms of exercise affect \textit{physical} health in different ways,
@@
 
-Thank you for considering our manuscript, and we hope you will find it suitable for publication in \textit{eLife}.
+Thank you for considering our manuscript, and we hope you will find it
+suitable for publication in \textit{Scientific Reports}.
 

### 2022-03-13 paper/main.tex
updated cover letters and formatting

@@
 \usepackage{geometry}
-\usepackage[sort]{natbib}
+\usepackage[sort, numbers]{natbib}
 \usepackage{pxfonts}
@@
 
-For their participation, workers received a base payment of \$5 per hour (computed in 15
-minute increments, rounded up to the nearest 15 minutes), plus an
-additional performance-based bonus of up to \$5.  Our recruitment
-procedure and study protocol
-were approved by Dartmouth's Committee for the Protection of Human Subjects.
+For their participation, workers received a base payment of \$5 per
+hour (computed in 15 minute increments, rounded up to the nearest 15
+minutes), plus an additional performance-based bonus of up to \$5.
+Our recruitment procedure and study protocol were approved by
+Dartmouth's Committee for the Protection of Human Subjects.  We
+obtained informed consent using an online form administered to all
+prospective participants prior to enrolling them in our study.  All
+methods were performed in accordance with the relevant guidelines and
+regulations.
 
@@
 particular way also tended to perform better on a given memory task,
-this could suggest that either (a) some property intrinsic to participants who
-exercised in a particular way might also affect their memory
-performance on the given task, and/or (b) particular exercise behaviors
-could have a causal impact on memory performance.  We carried out an
-exploratory analysis whereby we used a bootstrap-based approach (see
-\textit{Exploratory correlation analyses}) to
-identify reliable correlations between different aspects of memory
-performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
-attributes (Fig.~\demDemCorr), and correlations between memory
-performance, fitness information, and demographic attributes
-(Fig.~\allCorr).  Several patterns emerged.  First, we found that
+this could suggest that either (a) some property intrinsic to
+participants who exercised in a particular way might also affect their
+memory performance on the given task, and/or (b) particular exercise
+behaviors could have a causal impact on memory performance.  We
+carried out an exploratory analysis whereby we used a bootstrap-based
+approach to identify reliable correlations between different aspects
+of memory performance (Fig.~\behBehCorr), different aspects of fitness
+(Fig.~\fitFitCorr), different demographic attributes
+(Fig.~\demDemCorr), and correlations between memory performance,
+fitness information, and demographic attributes (Fig.~\allCorr).
+Specifically, we sought to identify correlations that were present in
+the same direction (i.e., positive or negative) across different
+subsets of participants.  For each test, we report the average correlation (taken
+across 10,000 subsets of participants, chosen with replacement) and
+an associated two-tailed $p$-value, estimated as
+\[
+p = 2 \times (1 - q),
+\]
+where $q$ is the proportion of those
+10,000 subsets that exhibited correlations in the same direction  (see
+\textit{Exploratory correlation analyses}).  When all 10,000 randomly
+chosen subsets of participants exhibited correlations in the same
+direction (i.e., all positive correlations or all negative
+correlations), we report the $p$-value as $p < 0.0001$.
+
+Several patterns emerged from these analyses.  First, we found that
 participants' performance on the (within-task) immediate versus delayed memory tests
@@
 Ziman.  Our work was supported in part by the Dartmouth Young Minds
-and Brains initiative.  The content is solely the responsibility of
-the authors and does not necessarily represent the official views of
-our supporting organizations.  This paper is dedicated to the memory
-of David Bucci, who helped to inspire the theoretical foundations of
-this work.  Dave served as a mentor and colleague on the project prior
-to his passing.
+and Brains initiative, and by NSF grant number 2145172 to J.R.M.  The
+content is solely the responsibility of the authors and does not
+necessarily represent the official views of our supporting
+organizations.  This paper is dedicated to the memory of David Bucci,
+who helped to inspire the theoretical foundations of this work.  Dave
+served as a mentor and colleague on the project prior to his passing.
 

### 2022-07-13 paper/main.tex
working on addressing r1 comments

@@
 \title{Fitness tracking reveals task-specific associations between
-  memory, mental health, and exercise}
+  memory, mental health, and physical activity}
 \author[1, $\star$]{Jeremy R. Manning}
@@
 \begin{abstract}
-  Physical exercise can benefit both physical and mental well-being.
+  Physical activity can benefit both physical and mental well-being.
   Different forms of exercise (e.g., aerobic versus anaerobic; running
@@
   and heart strength but only moderately impact arm strength. We
-  hypothesized that the mental benefits of exercise might be similarly
-  differentiated.  We focused specifically on how different forms of
-  exercise might relate to different aspects of memory and mental
+  hypothesized that the mental benefits of physical activity might be similarly
+  differentiated.  We focused specifically on how different intensities of
+  physical activity might relate to different aspects of memory and mental
   health.  To test our hypothesis, we collected (in aggregate) roughly
@@
   episodic, semantic, and spatial memory performance.  We found that
-  participants with similar exercise habits and fitness profiles
+  participants with similar physical activity habits and fitness profiles
   tended to also exhibit similar mental health and task performance
   profiles.  These effects were task-specific in that different
-  exercise patterns or fitness characteristics varied with different
+  physical activity patterns or fitness characteristics varied with different
   aspects of memory, on different tasks.  Taken together, these
-  findings provide foundational work for designing exercise
+  findings provide foundational work for designing physical activity
   interventions that target specific components of cognitive performance
@@
 capacity~\citep[][although see \cite{RomaEtal16}]{LazoEtal16}, and
-endurance~\citep{WilmKnut03}.  Exercise can also improve mental
+endurance~\citep{WilmKnut03}.  Physical activity can also improve mental
 health~\citep{Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
@@
 can in turn affect their growth or atrophy~\citep{SchiEtal13}.  By
-comparison, the benefits of exercise on mental health are less direct.
-For example, one hypothesis is that exercise leads to specific
+comparison, the benefits of physical activity on mental health are less direct.
+For example, one hypothesis is that physical activity leads to specific
 physiological changes, such as increased aminergic synaptic
@@
 neurotransmitters in the brain~\citep{PaluSchw00}.  Speculatively, if
-different exercise regimens lead to different neurophysiological
+different physical activity regimens lead to different neurophysiological
 responses, one might be able to map out a spectrum of signalling and
 transduction pathways that are impacted by a given type, duration, and
-intensity of exercise in each brain region.  For example, prior work
-has shown that exercise increases acetylcholine levels, starting in
+intensity of physical activity in each brain region.  For example, prior work
+has shown that physical activity increases acetylcholine levels, starting in
 the vicinity of the exercised muscles~\citep{ShoeEtal97}.
@@
 several dimensions.  We searched the data for potential associations
-between memory, mental health, and exercise.
+between memory, mental health, and physical activity.
 
@@
     platform~\citep{GureEtal16}.  We collected data about each participant's fitness and
-    exercise habits, a variety of self-reported measures concerning their
+    physical activity habits, a variety of self-reported measures concerning their
     mental health, and about their performance on a battery of memory
@@
 and water consumption, location of their residence, activity typically
-required for their job, and exercise habits.
+required for their job, and physical activity habits.
 
@@
 given task, we would be unable to identify how memory performance on
-that task varied with mental health or exercise.
+that task varied with mental health or physical activity.
 
@@
 participants who exercised in a particular way might also affect their
-memory performance on the given task, and/or (b) particular exercise
+memory performance on the given task, and/or (b) particular physical activity
 behaviors could have a causal impact on memory performance.  We
@@
 on average or in aggregate, many of the measures we collected are
-dynamic. For example, the amount or intensity of physical exercise
+dynamic. For example, the amount or intensity of physical activity
 people engage in can vary over time, and so on.  We wondered whether
@@
 effects.  For example, we cannot know (from our study) whether
-engaging in particular forms of exercise \textit{causes} changes in
+engaging in particular forms of physical activity \textit{causes} changes in
 memory performance or mental health, or whether (alternatively) people
-who tend to engage in similar forms of exercise also happen to
+who tend to engage in similar forms of physical activity also happen to
 exhibit similar memory and/or mental health profiles.  In other words,
 an overlapping set of processes or person-specific attributes may lead
-someone to both form particular habits around exercise and display high or low performance on a
+someone to both form particular habits around physical activity and display high or low performance on a
 given memory test.  We do not know whether memory performance or
@@
 prior work is that most of these studies examine how relatively
-short-term changes in exercise (e.g., on timescales of hours to days
+short-term changes in physical activity (e.g., on timescales of hours to days
 or, rarely, weeks to months) affect a cognitive performance on single
 task or aspect of mental health.  The present study examines
-longer-term exercise (over a full year), and relates long-term
-exercise history to performance on a variety of tasks and to a variety
+longer-term physical activity (over a full year), and relates long-term
+physical activity history to performance on a variety of tasks and to a variety
 of mental health dimensions.
 
-To the extent that exercise \textit{does} provide a non-invasive means
+To the extent that physical activity \textit{does} provide a non-invasive means
 of manipulating cognitive performance and mental health, our work may
@@
 one might imagine building a recommendation system that suggests a
-particular exercise regimen tailored to improve a specific aspect of
+particular physical activity regimen tailored to improve a specific aspect of
 an individual's cognitive performance (e.g., the efficacy of a student's study session for an
@@
 \bibliographystyle{apa}
-\bibliography{/Users/jmanning/CDL-bibliography/cdl}
+\bibliography{/home/jeremy/CDL-bibliography/cdl.bib}
 \end{document}

### 2022-07-14 paper/main.tex
updating paper

@@
 health~\citep{Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
-  PaluSchw00, BassSuzu17} and cognitive
+  PaluSchw00, BassSuzu17, MorrEtal18, GordEtal17, MorrEtal22, HerrEtal10} and cognitive
 performance~\citep{ChanEtal12b, BrisEtal02, EtniEtal06, BassSuzu17}.
@@
 
-In the present study, we hypothesize that (a) different exercise
-regimens will have different, quantifiable impacts on cognitive
+In the present study, we hypothesize that (a) different intensities of physical activity will have different, quantifiable impacts on cognitive
 performance and mental health, and that (b) these impacts will be
@@
 We wondered about potential links between the different aspects of
-participants' data.  For example, if people who exercised in a
-particular way also tended to perform better on a given memory task,
+participants' data.  For example, if people who engaged in particular intensities of physical activity also tended to perform better on a given memory task,
 this could suggest that either (a) some property intrinsic to
@@
 questions.  We found that the associations between fitness-related
-activities, memory performance, and mental health were heterogeneous.
-Our results suggest that engagement in particular physical
-activities (e.g., differing in time relative to the
-test day, intensity, duration, etc.) is also reflected in participants'
-memory performance patterns across tasks and in participants' mental
-health attributes.
+activities, memory performance, and mental health are complex.  For example,
+participants who tended to engage in a particular intensity of physical activity
+also tended to perform better on some memory tasks but worse on others.  This
+suggests that engaging in one form or intensity of physical activity
+will not necessarily affect all aspects of cognitive or mental health equally
+(or in the same direction).
+
+A number of prior studies have shown that engaging in exercise can improve cognitive
+and mental health~\citep{ChanEtal12b, BrisEtal02, EtniEtal06, BassSuzu17, Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
+PaluSchw00, MorrEtal18, GordEtal17, MorrEtal22, HerrEtal10}.  The majority of these studies
+ask participants in an ``exercise intervention'' condition (where participants engage in
+a designated physical activity or training regimen) or a ``control'' condition (where participants 
+do not engage in the designated activity or training) to perform cognitive tasks or undergo
+mental health screening.  In other words, most primary studies treat ``physical activity'' as a binary
+variable that either is or is not present for each participant.  Most prior studies also 
+track or manipulate exercise over relatively short durations (typically on the order of days or weeks).  Our current work indicates
+that the true relations between physical activity, cognitive performance, and mental health
+may be non-monotonic and heterogeneous across activities, tasks, and mental health measures.  These
+relations can also unfold over much longer timescales than have been previously identified (on the order of months; Fig.~\ref{fig:dynamics}).
+However, despite the complexities of the structures of these associations, we also found that 
+they were often remarkably consistent across people.  For example, as displayed in Figure~\allCorr,
+many of the associations between fitness, behavioral, and mental health
+measures were consistent across over 95\% of 10,000 randomly chosen subsets
+of participants.
 

### 2022-07-14 code/loader.py

@@ -29,6 +29,7 @@ import brainiak.eventseg.event as event
 BASE_DIR = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))
 DATA_DIR = os.path.join(BASE_DIR, 'data')
 
+nltk.download('omw-1.4')
 
 def load_raw():
     datadir = os.path.join(DATA_DIR, 'raw_formatted')

### 2022-07-16 paper/main.tex
addressing r2 comments in main text

@@
 \includegraphics[width=0.8\textwidth]{figs/corr_MH}
-\caption{\textbf{Memory performance differs according to mental health
-    measures.}  The reported values in the table reflect correlations
+\caption{\textbf{Summaries of correlations between behavioral, fitness, and mental
+ health measures.}  The reported values in the tables reflect correlations
   between each behavioral measure and mental health measure.
   Only statistically reliable correlations ($p < 0.05$, corrected) are displayed.
-  We used participants' mean recall accuracy to characterize
+  \textbf{a. Correlations between behavioral and mental health measures.}
+  We adjusted each task's behavioral measure(s) such that more positive values reflect
+  better performance on the given task.  We used participants' mean recall accuracy to characterize
   performance on the free recall and
@@
   Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},
-  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  Typical
+  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  For each mental health
+  measure, more positive values denote greater severity of the given measure.  Typical
   and current stress levels were measured by self report.  Mental
   health information was inferred using each participants' list of
-  self-reported medications.}
-\label{fig:mh_corr}
+  self-reported medications (see \textit{Methods}).  Positive correlations indicate that
+  better performance on a given behavioral task is associated with more severe 
+  mental health phenotypes.  \textbf{b. Correlations between fitness
+  and mental health measures.}  For each fitness measure, more positive
+  values denote higher observed scores (i.e., higher resting heart rate,
+  more minutes of activity or time spent in each heart rate zone, or greater heart rate variability).
+  The mental health measures in this panel were treated as in Panel a.
+  \textbf{c. Correlations between fitness and behavioral measures.}
+  Each measure reflected in this panel was treated as in Panels a and b.}
+\label{fig:corr_summaries}
 \end{figure}
@@
 stress levels and medications were also associated with differences in
-memory (Figs.~\ref{fig:mh_corr}, \allCorr).  For example, self-reported stress levels at the time of test
+memory (Figs.~\ref{fig:corr_summaries}, \allCorr).  For example, self-reported stress levels at the time of test
 were negatively correlated with performance on the delayed memory test
@@
 many of the associations between fitness, behavioral, and mental health
-measures were consistent across over 95\% of 10,000 randomly chosen subsets
+measures were consistent across over 97.5\% of 10,000 randomly chosen subsets
 of participants.

### 2022-07-16 paper/main.tex
generated diff file

@@
 \centering
-\includegraphics[width=0.8\textwidth]{figs/corr_MH}
+\includegraphics[width=\textwidth]{figs/combined_correlations_main}
 \caption{\textbf{Summaries of correlations between behavioral, fitness, and mental
@@
 However, despite the complexities of the structures of these associations, we also found that 
-they were often remarkably consistent across people.  For example, as displayed in Figure~\allCorr,
+they were often remarkably consistent across people.  For example, as displayed in Figures~\ref{fig:corr_summaries} and~\allCorr,
 many of the associations between fitness, behavioral, and mental health

### 2022-07-16 paper/main.tex
spelling and grammar edits

@@
 performance and mental health, and that (b) these impacts will be
-consistant across individuals.  To this end, we collected a year of
+consistent across individuals.  To this end, we collected a year of
 real-world fitness tracking data from each of 113 participants.  We
@@
 who score highly across several metrics on a large number of HITs,
-according to a proprietary algorithm managed by Amazon.  One criteria
+according to a proprietary algorithm managed by Amazon.  One criterion
 embedded into the algorithm is a requirement that master
@@
 male, and 1 chose not to report their gender.  Participants ranged in
-age from 19--68 years old (25\textsuperscript{th} percentile: 28.25
+age from 19 to 68 years old (25\textsuperscript{th} percentile: 28.25
 years; 50\textsuperscript{th} percentile: 32 years;
@@
 Participants reported the number of 8~oz cups of water and coffee they had
-consumed prior to accepting the HIT.  Water consumption ranged from
-0--6 cups (25\textsuperscript{th} percentile: 1;
+consumed prior to accepting the HIT.  Water consumption ranged from 0 to 6 cups (25\textsuperscript{th} percentile: 1;
 50\textsuperscript{th} percentile: 3; 75\textsuperscript{th}
-percentile: 4).  Coffee consumption ranged from 0--4 cups (25\textsuperscript{th} percentile: 0;
+percentile: 4).  Coffee consumption ranged from 0 to 4 cups (25\textsuperscript{th} percentile: 0;
 50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
@@
 \paragraph*{Naturalistic recall (Fig.~\ref{fig:tasks}b).}
-Participants watched a 2.5~minute video clip entitled ``The Temple of
+Participants watched a 2.5-minute video clip entitled ``The Temple of
 Knowledge.''  The video comprises an animated story told to StoryCorps
@@
 option of ending the response period early, e.g., if they felt they
-had finished entering all of the information they remembered.  Each
+had finished entering all the information they remembered.  Each
 participant's transcript was constructed from their submitted
 responses by combining the sentences into a single document and
-removing extraneous whitespace characters.  Following this 4--10
-minute free response period, participants were given a series of 10
+removing extraneous whitespace characters.  Following this 4--10-minute free response period, participants were given a series of 10
 multiple choice questions about the conceptual content of the story.
@@
 participant accepted the HIT, and $m(10)$ represents the value of $m$
-9 days prior to accepting the HIT.  We set $R = 7$ and $B = 30$.  In
+9 days prior to accepting the HIT).  We set $R = 7$ and $B = 30$.  In
 other words, to estimate recent changes in any metric $m$, we divided
@@
 value'' for each day with the average values of that measure (when
-available) over the 7 day interval ending on the given day.
+available) over the 7-day interval ending on the given day.
 
@@
 Figure~\frDetail~for additional details.
-\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5~min video
+\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5-min video
 clip; each dot reflects a narrative event (red denotes early events
@@
   errors as a function of the number of studied shapes (also see
-  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},
-  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  For each mental health
+  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},~\frDetail,~\natDetail,~\vocabDetail, and~\spatialDetail).  For each mental health
   measure, more positive values denote greater severity of the given measure.  Typical
@@
 from the unweighted baseline (via a paired sample two-sided $t$-test
-of the weighted mean values for each measure within a 30 day window around each timepoint; horizontal lines denote $p <
+of the weighted mean values for each measure within a 30-day window around each timepoint; horizontal lines denote $p <
 0.05$, corrected).}

### 2022-07-17 paper/main.tex
finished complete pass through edits of main text, supplement, and response letter

@@
 \includegraphics[width=\textwidth]{figs/combined_correlations_main}
-\caption{\textbf{Summaries of correlations between behavioral, fitness, and mental
- health measures.}  The reported values in the tables reflect correlations
-  between each behavioral measure and mental health measure.
-  Only statistically reliable correlations ($p < 0.05$, corrected) are displayed.
-  \textbf{a. Correlations between behavioral and mental health measures.}
-  We adjusted each task's behavioral measure(s) such that more positive values reflect
-  better performance on the given task.  We used participants' mean recall accuracy to characterize
-  performance on the free recall and
+\caption{\textbf{Summaries of correlations between behavioral,
+    fitness, and mental health measures.}  The reported values in the
+  tables reflect correlations between each behavioral measure and
+  mental health measure.  Only statistically reliable correlations
+  ($p < 0.05$, corrected) are displayed.  \textbf{a. Correlations
+    between behavioral and mental health measures.}  We adjusted each
+  task's behavioral measure(s) such that more positive values reflect
+  better performance on the given task.  We used participants' mean
+  recall accuracy to characterize performance on the free recall and
   foreign language flashcards tasks, and mean precision to
@@
   characterized performance on the spatial learning task using the
-  (inverted and normalized)
-  intercepts and slopes of linear regressions on mean estimation
-  errors as a function of the number of studied shapes (also see
-  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},~\frDetail,~\natDetail,~\vocabDetail, and~\spatialDetail).  For each mental health
-  measure, more positive values denote greater severity of the given measure.  Typical
-  and current stress levels were measured by self report.  Mental
-  health information was inferred using each participants' list of
-  self-reported medications (see \textit{Methods}).  Positive correlations indicate that
-  better performance on a given behavioral task is associated with more severe 
-  mental health phenotypes.  \textbf{b. Correlations between fitness
-  and mental health measures.}  For each fitness measure, more positive
-  values denote higher observed scores (i.e., higher resting heart rate,
-  more minutes of activity or time spent in each heart rate zone, or greater heart rate variability).
-  The mental health measures in this panel were treated as in Panel a.
-  \textbf{c. Correlations between fitness and behavioral measures.}
-  Each measure reflected in this panel was treated as in Panels a and b.}
+  (inverted and normalized) intercepts and slopes of linear
+  regressions on mean estimation errors as a function of the number of
+  studied shapes (also see Figs.~\ref{fig:immediate_behavior},
+  \ref{fig:delayed_behavior},~\frDetail,~\natDetail,~\vocabDetail,
+  and~\spatialDetail).  For each mental health measure, more positive
+  values denote greater severity of the given measure.  Typical and
+  current stress levels were measured by self report.  Mental health
+  information was inferred using each participants' list of
+  self-reported medications (see \textit{Methods}).  Positive
+  correlations indicate that better performance on a given behavioral
+  task is associated with more severe mental health phenotypes.
+  \textbf{b. Correlations between fitness and mental health measures.}
+  For each fitness measure, more positive values denote higher
+  observed scores (i.e., higher resting heart rate, more minutes of
+  activity or time spent in each heart rate zone, or greater heart
+  rate variability).  The mental health measures in this panel were
+  treated as in Panel a.  \textbf{c. Correlations between fitness and
+    behavioral measures.}  Each measure reflected in this panel was
+  treated as in Panels a and b.}
 \label{fig:corr_summaries}
@@
 demographic measures and their behaviors in different tasks
-(for a complete report, see Fig.~\allCorr).  For example, recent
-low-to-moderate-intensity (``fat burn'') 
-cardiovascular activity was positively
-correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
-0.38, p = 0.029$) recall performance on the naturalistic
-memory task.  Recent increases in moderate-intensity (``cardio'')
-activity over the prior 7 days (relative to the preceding 30 days) was
-also positively correlated with immediate naturalistic recall
-performance ($r =
-0.48, p = 0.003$) and immediate recall performance on the foreign language
-flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
-(``peak'') activity was positively correlated with performance on the
-spatial learning task ($r = 0.34, p < 0.0001$), as were recent increases
-in high-intensity activity (prior 7 days versus preceding 30 days; $r
-= 0.41, p = 0.01$).  Mental health indicators, such as self-reported
-stress levels and medications were also associated with differences in
-memory (Figs.~\ref{fig:corr_summaries}, \allCorr).  For example, self-reported stress levels at the time of test
-were negatively correlated with performance on the delayed memory test
-for the foreign language flashcards task ($r = -0.29, p = 0.038$),
-whereas participants who were medicated for anxiety and depression
-tended to perform slightly (but reliably) \textit{better} on the immediate memory test for the
-foreign language flashcards task ($r = 0.11, p < 0.0001$).
+(Fig.~\ref{fig:corr_summaries}; for a complete report, see Fig.~\allCorr).
+For example, recent low-to-moderate-intensity (``fat burn'')
+cardiovascular activity was positively correlated with immediate
+($r = 0.44, p = 0.001$) and delayed ($r = 0.38, p = 0.031$) recall
+performance on the naturalistic memory task.  Recent sedentary
+(``out-of-range'') cariovascular activity was negatively correlated
+with performance on the spatial learning task
+($r = -0.31, p = 0.042$), whereas recent high intensity (``peak'')
+activity was positively correlated with performance on the spatial
+learning task ($r = 0.34, p = 0.0002$).  Mental health indicators,
+such as self-reported stress levels and medications were also
+associated with differences in memory
+(Figs.~\ref{fig:corr_summaries}a, \allCorr).  For example,
+self-reported stress levels at the time of test were negatively
+correlated with performance on the delayed memory test for the foreign
+language flashcards task ($r = -0.29, p = 0.038$), whereas
+participants who were medicated for anxiety and depression tended to
+perform slightly (but reliably) \textit{better} on the immediate
+memory test for the foreign language flashcards task
+($r = 0.11, p < 0.0001$).  Mental health indicators were also
+correlated with several fitness measures
+(Fig.~\ref{fig:corr_summaries}c).  For example, participants with
+higher resting heart rates were less likely to be hypothyroid ($r =
+-0.33, p < 0.0001$).  Participants who engaged in more low-intensity
+(``light'') activity tended to be less anxious and depressed ($r =
+-0.12, p = 0.03$), whereas participants who engaged in more
+high-intensity activity tended to report higher levels of current ($r
+= 0.15, p = 0.027$) and typical ($r = 0.21, p = 0.012$) stress.
 

### 2022-07-18 paper/main.tex
use mac-style bib path
final round of edits, recompiled diffs

@@
 \paragraph{Languages.}
-All participants reported that they were fluent in either 1 and 2
+All participants reported that they were fluent in either 1 or 2
 languages (25\textsuperscript{th} percentile: 1;
@@
 with the given picture.  The 3 incorrect options were selected at
-random (with replacement across trials), and the order in which the
+random (with replacement across trials), and the orders in which the
 choices appeared to the participant were also randomized.  Each of the
-10 words they had learned were tested exactly once.
+10 words they had learned was tested exactly once.
 
@@
 Before testing our main hypotheses, we examined the behavioral data
-from each of four memory tasks: a random word list learning ``free
-recall'' task (Fig.~\ref{fig:tasks}); a naturalistic recall task whereby participants watched
+from each of four memory tasks (Fig.~\ref{fig:tasks}): a random word list learning ``free
+recall'' task; a naturalistic recall task whereby participants watched
 a short video and then recounted the narrative; a foreign language
@@
     fitness, and mental health measures.}  The reported values in the
-  tables reflect correlations between each behavioral measure and
-  mental health measure.  Only statistically reliable correlations
+  tables reflect correlations between each pair of measures.  Only statistically reliable correlations
   ($p < 0.05$, corrected) are displayed.  \textbf{a. Correlations
@@
   better performance on the given task.  We used participants' mean
-  recall accuracy to characterize performance on the free recall and
-  foreign language flashcards tasks, and mean precision to
+  recall accuracies to characterize performance on the free recall and
+  foreign language flashcards tasks, and mean precisions to
   characterize performance on the naturalistic recall tasks.  We
@@
   (inverted and normalized) intercepts and slopes of linear
-  regressions on mean estimation errors as a function of the number of
+  regressions on mean estimation errors as a function of the numbers of
   studied shapes (also see Figs.~\ref{fig:immediate_behavior},
@@
 performance on the naturalistic memory task.  Recent sedentary
-(``out-of-range'') cariovascular activity was negatively correlated
+(``out-of-range'') cardiovascular activity was negatively correlated
 with performance on the spatial learning task
@@
 \includegraphics[width=\textwidth]{figs/weighted_timecourse_summary}
-\caption{\textbf{Dynamics of physical activity varies with memory
+\caption{\textbf{Dynamics of physical activity vary with memory
     performance and mental health measures.}  \textbf{a. Daily step counts.}  Each
@@
 this reason, we have been careful to frame our findings as
-correlations and associations, rather than to imply knowledge about a causal direction
+correlations and associations, rather than to imply knowledge about causal directions
 of our findings.

### 2022-07-18 paper/old.tex

--- 2022-07-16 paper/main.tex
@@
 \title{Fitness tracking reveals task-specific associations between
-  memory, mental health, and physical activity}
+  memory, mental health, and exercise}
 \author[1, $\star$]{Jeremy R. Manning}
@@
 \begin{abstract}
-  Physical activity can benefit both physical and mental well-being.
+  Physical exercise can benefit both physical and mental well-being.
   Different forms of exercise (e.g., aerobic versus anaerobic; running
@@
   and heart strength but only moderately impact arm strength. We
-  hypothesized that the mental benefits of physical activity might be similarly
-  differentiated.  We focused specifically on how different intensities of
-  physical activity might relate to different aspects of memory and mental
+  hypothesized that the mental benefits of exercise might be similarly
+  differentiated.  We focused specifically on how different forms of
+  exercise might relate to different aspects of memory and mental
   health.  To test our hypothesis, we collected (in aggregate) roughly
@@
   episodic, semantic, and spatial memory performance.  We found that
-  participants with similar physical activity habits and fitness profiles
+  participants with similar exercise habits and fitness profiles
   tended to also exhibit similar mental health and task performance
   profiles.  These effects were task-specific in that different
-  physical activity patterns or fitness characteristics varied with different
+  exercise patterns or fitness characteristics varied with different
   aspects of memory, on different tasks.  Taken together, these
-  findings provide foundational work for designing physical activity
+  findings provide foundational work for designing exercise
   interventions that target specific components of cognitive performance
@@
 capacity~\citep[][although see \cite{RomaEtal16}]{LazoEtal16}, and
-endurance~\citep{WilmKnut03}.  Physical activity can also improve mental
+endurance~\citep{WilmKnut03}.  Exercise can also improve mental
 health~\citep{Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
-  PaluSchw00, BassSuzu17, MorrEtal18, GordEtal17, MorrEtal22, HerrEtal10} and cognitive
+  PaluSchw00, BassSuzu17} and cognitive
 performance~\citep{ChanEtal12b, BrisEtal02, EtniEtal06, BassSuzu17}.
@@
 can in turn affect their growth or atrophy~\citep{SchiEtal13}.  By
-comparison, the benefits of physical activity on mental health are less direct.
-For example, one hypothesis is that physical activity leads to specific
+comparison, the benefits of exercise on mental health are less direct.
+For example, one hypothesis is that exercise leads to specific
 physiological changes, such as increased aminergic synaptic
@@
 neurotransmitters in the brain~\citep{PaluSchw00}.  Speculatively, if
-different physical activity regimens lead to different neurophysiological
+different exercise regimens lead to different neurophysiological
 responses, one might be able to map out a spectrum of signalling and
 transduction pathways that are impacted by a given type, duration, and
-intensity of physical activity in each brain region.  For example, prior work
-has shown that physical activity increases acetylcholine levels, starting in
+intensity of exercise in each brain region.  For example, prior work
+has shown that exercise increases acetylcholine levels, starting in
 the vicinity of the exercised muscles~\citep{ShoeEtal97}.
@@
 
-In the present study, we hypothesize that (a) different intensities of physical activity will have different, quantifiable impacts on cognitive
+In the present study, we hypothesize that (a) different exercise
+regimens will have different, quantifiable impacts on cognitive
 performance and mental health, and that (b) these impacts will be
-consistent across individuals.  To this end, we collected a year of
+consistant across individuals.  To this end, we collected a year of
 real-world fitness tracking data from each of 113 participants.  We
@@
 several dimensions.  We searched the data for potential associations
-between memory, mental health, and physical activity.
+between memory, mental health, and exercise.
 
@@
     platform~\citep{GureEtal16}.  We collected data about each participant's fitness and
-    physical activity habits, a variety of self-reported measures concerning their
+    exercise habits, a variety of self-reported measures concerning their
     mental health, and about their performance on a battery of memory
@@
 who score highly across several metrics on a large number of HITs,
-according to a proprietary algorithm managed by Amazon.  One criterion
+according to a proprietary algorithm managed by Amazon.  One criteria
 embedded into the algorithm is a requirement that master
@@
 male, and 1 chose not to report their gender.  Participants ranged in
-age from 19 to 68 years old (25\textsuperscript{th} percentile: 28.25
+age from 19--68 years old (25\textsuperscript{th} percentile: 28.25
 years; 50\textsuperscript{th} percentile: 32 years;
@@
 Participants reported the number of 8~oz cups of water and coffee they had
-consumed prior to accepting the HIT.  Water consumption ranged from 0 to 6 cups (25\textsuperscript{th} percentile: 1;
+consumed prior to accepting the HIT.  Water consumption ranged from
+0--6 cups (25\textsuperscript{th} percentile: 1;
 50\textsuperscript{th} percentile: 3; 75\textsuperscript{th}
-percentile: 4).  Coffee consumption ranged from 0 to 4 cups (25\textsuperscript{th} percentile: 0;
+percentile: 4).  Coffee consumption ranged from 0--4 cups (25\textsuperscript{th} percentile: 0;
 50\textsuperscript{th} percentile: 1; 75\textsuperscript{th}
@@
 and water consumption, location of their residence, activity typically
-required for their job, and physical activity habits.
+required for their job, and exercise habits.
 
@@
 \paragraph*{Naturalistic recall (Fig.~\ref{fig:tasks}b).}
-Participants watched a 2.5-minute video clip entitled ``The Temple of
+Participants watched a 2.5~minute video clip entitled ``The Temple of
 Knowledge.''  The video comprises an animated story told to StoryCorps
@@
 option of ending the response period early, e.g., if they felt they
-had finished entering all the information they remembered.  Each
+had finished entering all of the information they remembered.  Each
 participant's transcript was constructed from their submitted
 responses by combining the sentences into a single document and
-removing extraneous whitespace characters.  Following this 4--10-minute free response period, participants were given a series of 10
+removing extraneous whitespace characters.  Following this 4--10
+minute free response period, participants were given a series of 10
 multiple choice questions about the conceptual content of the story.
@@
 participant accepted the HIT, and $m(10)$ represents the value of $m$
-9 days prior to accepting the HIT).  We set $R = 7$ and $B = 30$.  In
+9 days prior to accepting the HIT.  We set $R = 7$ and $B = 30$.  In
 other words, to estimate recent changes in any metric $m$, we divided
@@
 value'' for each day with the average values of that measure (when
-available) over the 7-day interval ending on the given day.
+available) over the 7 day interval ending on the given day.
 
@@
 given task, we would be unable to identify how memory performance on
-that task varied with mental health or physical activity.
+that task varied with mental health or exercise.
 
@@
 Figure~\frDetail~for additional details.
-\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5-min video
+\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5~min video
 clip; each dot reflects a narrative event (red denotes early events
@@
 We wondered about potential links between the different aspects of
-participants' data.  For example, if people who engaged in particular intensities of physical activity also tended to perform better on a given memory task,
+participants' data.  For example, if people who exercised in a
+particular way also tended to perform better on a given memory task,
 this could suggest that either (a) some property intrinsic to
 participants who exercised in a particular way might also affect their
-memory performance on the given task, and/or (b) particular physical activity
+memory performance on the given task, and/or (b) particular exercise
 behaviors could have a causal impact on memory performance.  We
@@
 \centering
-\includegraphics[width=\textwidth]{figs/combined_correlations_main}
-\caption{\textbf{Summaries of correlations between behavioral, fitness, and mental
- health measures.}  The reported values in the tables reflect correlations
+\includegraphics[width=0.8\textwidth]{figs/corr_MH}
+\caption{\textbf{Memory performance differs according to mental health
+    measures.}  The reported values in the table reflect correlations
   between each behavioral measure and mental health measure.
   Only statistically reliable correlations ($p < 0.05$, corrected) are displayed. 
-  \textbf{a. Correlations between behavioral and mental health measures.}
-  We adjusted each task's behavioral measure(s) such that more positive values reflect
-  better performance on the given task.  We used participants' mean recall accuracy to characterize
+  We used participants' mean recall accuracy to characterize
   performance on the free recall and
@@
   errors as a function of the number of studied shapes (also see
-  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},~\frDetail,~\natDetail,~\vocabDetail, and~\spatialDetail).  For each mental health
-  measure, more positive values denote greater severity of the given measure.  Typical
+  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},
+  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  Typical
   and current stress levels were measured by self report.  Mental
   health information was inferred using each participants' list of
-  self-reported medications (see \textit{Methods}).  Positive correlations indicate that
-  better performance on a given behavioral task is associated with more severe 
-  mental health phenotypes.  \textbf{b. Correlations between fitness
-  and mental health measures.}  For each fitness measure, more positive
-  values denote higher observed scores (i.e., higher resting heart rate,
-  more minutes of activity or time spent in each heart rate zone, or greater heart rate variability).
-  The mental health measures in this panel were treated as in Panel a.
-  \textbf{c. Correlations between fitness and behavioral measures.}
-  Each measure reflected in this panel was treated as in Panels a and b.}
-\label{fig:corr_summaries}
+  self-reported medications.}
+\label{fig:mh_corr}
 \end{figure}
@@
 stress levels and medications were also associated with differences in
-memory (Figs.~\ref{fig:corr_summaries}, \allCorr).  For example, self-reported stress levels at the time of test
+memory (Figs.~\ref{fig:mh_corr}, \allCorr).  For example, self-reported stress levels at the time of test
 were negatively correlated with performance on the delayed memory test
@@
 from the unweighted baseline (via a paired sample two-sided $t$-test
-of the weighted mean values for each measure within a 30-day window around each timepoint; horizontal lines denote $p <
+of the weighted mean values for each measure within a 30 day window around each timepoint; horizontal lines denote $p <
 0.05$, corrected).}
@@
 on average or in aggregate, many of the measures we collected are
-dynamic. For example, the amount or intensity of physical activity
+dynamic. For example, the amount or intensity of physical exercise
 people engage in can vary over time, and so on.  We wondered whether
@@
 questions.  We found that the associations between fitness-related
-activities, memory performance, and mental health are complex.  For example,
-participants who tended to engage in a particular intensity of physical activity
-also tended to perform better on some memory tasks but worse on others.  This
-suggests that engaging in one form or intensity of physical activity
-will not necessarily affect all aspects of cognitive or mental health equally
-(or in the same direction).
-
-A number of prior studies have shown that engaging in exercise can improve cognitive
-and mental health~\citep{ChanEtal12b, BrisEtal02, EtniEtal06, BassSuzu17, Ragl90, MikkEtal17, TaylEtal85, DeslEtal09, Call04,
-PaluSchw00, MorrEtal18, GordEtal17, MorrEtal22, HerrEtal10}.  The majority of these studies
-ask participants in an ``exercise intervention'' condition (where participants engage in
-a designated physical activity or training regimen) or a ``control'' condition (where participants 
-do not engage in the designated activity or training) to perform cognitive tasks or undergo
-mental health screening.  In other words, most primary studies treat ``physical activity'' as a binary
-variable that either is or is not present for each participant.  Most prior studies also 
-track or manipulate exercise over relatively short durations (typically on the order of days or weeks).  Our current work indicates
-that the true relations between physical activity, cognitive performance, and mental health
-may be non-monotonic and heterogeneous across activities, tasks, and mental health measures.  These
-relations can also unfold over much longer timescales than have been previously identified (on the order of months; Fig.~\ref{fig:dynamics}).
-However, despite the complexities of the structures of these associations, we also found that 
-they were often remarkably consistent across people.  For example, as displayed in Figures~\ref{fig:corr_summaries} and~\allCorr,
-many of the associations between fitness, behavioral, and mental health
-measures were consistent across over 97.5\% of 10,000 randomly chosen subsets
-of participants.
+activities, memory performance, and mental health were heterogeneous.
+Our results suggest that engagement in particular physical
+activities (e.g., differing in time relative to the
+test day, intensity, duration, etc.) is also reflected in participants'
+memory performance patterns across tasks and in participants' mental
+health attributes.
 
@@
 effects.  For example, we cannot know (from our study) whether
-engaging in particular forms of physical activity \textit{causes} changes in
+engaging in particular forms of exercise \textit{causes} changes in
 memory performance or mental health, or whether (alternatively) people
-who tend to engage in similar forms of physical activity also happen to
+who tend to engage in similar forms of exercise also happen to
 exhibit similar memory and/or mental health profiles.  In other words,
 an overlapping set of processes or person-specific attributes may lead
-someone to both form particular habits around physical activity and display high or low performance on a
+someone to both form particular habits around exercise and display high or low performance on a
 given memory test.  We do not know whether memory performance or
@@
 prior work is that most of these studies examine how relatively
-short-term changes in physical activity (e.g., on timescales of hours to days
+short-term changes in exercise (e.g., on timescales of hours to days
 or, rarely, weeks to months) affect a cognitive performance on single
 task or aspect of mental health.  The present study examines
-longer-term physical activity (over a full year), and relates long-term
-physical activity history to performance on a variety of tasks and to a variety
+longer-term exercise (over a full year), and relates long-term
+exercise history to performance on a variety of tasks and to a variety
 of mental health dimensions.
 
-To the extent that physical activity \textit{does} provide a non-invasive means
+To the extent that exercise \textit{does} provide a non-invasive means
 of manipulating cognitive performance and mental health, our work may
@@
 one might imagine building a recommendation system that suggests a
-particular physical activity regimen tailored to improve a specific aspect of
+particular exercise regimen tailored to improve a specific aspect of
 an individual's cognitive performance (e.g., the efficacy of a student's study session for an
@@
 \bibliographystyle{apa}
-\bibliography{/home/jeremy/CDL-bibliography/cdl.bib}
+\bibliography{/home/jeremy/CDL-bibliography/cdl}
 \end{document}

### 2022-07-18 paper/supplement.tex
updated author affiliations

@@
 \affil[1]{Dartmouth College, Hanover, NH}
-\affil[2]{Lockheed Martin, Bethesda, MD}
 \affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}
@@
 delayed recall of the video.  \textbf{g. Immediate recall precision.}  Distribution of
-average recall \textit{precision}, across all of the events each
+average recall \textit{precision}, across all the events each
 participant recalled during the immediate recall test.  Precision is
@@
   \hline
-Sleep duration          & Estimated number of hours slept during the prior 24 hour period                                                                                                                      & hours (hr)                               \\
+Sleep duration          & Estimated number of hours slept during the prior 24-hour period                                                                                                                      & hours (hr)                               \\
   \hline
@@
 \includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
-\caption{\textbf{Scatterplots of fitness measures versus
-    immediate task performance measures.}  The scatterplots of recent
+\caption{\textbf{Scatter plots of fitness measures versus
+    immediate task performance measures.}  The scatter plots of recent
   (Panel a), baselined (Panel b), and static (Panel c) fitness
@@
 \includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
-\caption{\textbf{Scatterplots of fitness measures versus
-    delayed task performance measures.} The scatterplots of recent
+\caption{\textbf{Scatter plots of fitness measures versus
+    delayed task performance measures.} The scatter plots of recent
   (Panel a), baselined (Panel b), and static (Panel c) fitness
@@
 \bibliographystyle{apa}
-\bibliography{/Users/jmanning/CDL-bibliography/cdl}
+\bibliography{/home/jeremy/CDL-bibliography/cdl}
 \end{document}
